---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script calculates euclidian distances and analyses them. 
From YOUNG and OLD datasets of THE SAME SPECIES.

Replace the file path to load objects from different species.

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(ComplexUpset)
library(cowplot)
library(ggpubr)
library(ggbeeswarm)
library(bluster)
library(dendextend)
library(pheatmap)
library(RColorBrewer)
library(viridis)
library(ggplotify)


#library(scran)
#library(ggpubr)
#library(scater)
#library(data.table)

ctpints_list[[9]][[2]][[210]]

cpi_list[[9]]$Conditions

```

## Load

### Code

```{r load_code, message = FALSE}

setwd("/home/l012t/Interspecies_BM")

source(file = "code/filepath.R")
source(file = "code/colors.R")
source(file = "interactome/functions/cpi_functions_analysis.R")

```

### Objects

Adjust the file paths to load objects from different species. 
After this, nothing needs to be changed.

```{r}

# merged and pre-processed SCE objects
sce_yng <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_m"))
sce_old <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_m"))

# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

name_yng <- "mmus_yng"
name_old <- "mmus_old"
species <- "mmus"

max_ctpints <- 400
max_ctints <- 600
max_nrcells <- 10000
max_nrlrs <- 220

```

Merge overview dfs for direct comparion between age groups.

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctints_both <- rbind(ctints_yng[[1]], ctints_old[[1]])
ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))
ctints_both$celltypes <- factor(ctints_both$celltypes, 
                                levels = names(col_cts_red))
```

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))
```

# Analysis

Calculate euclidian distances first.

```{r}

#scaling (and rename for convenience)
cpi_both_scaled <- scale(t(cpi_merged_pca$Score))

#euclidian distances
cpi_both_dist <- dist(cpi_both_scaled, method = 'euclidean')

# make a df for convenience
cpi_both_dist_mat <- as.matrix(cpi_both_dist)
cpi_both_dist_df <- as.data.frame(cpi_both_dist_mat)

```

## Direct Measurement between young and old ctps

Get the direct euclidian distances between ctps from young and ctps from old.

```{r}

dist_oy <- cpi_both_dist_df[grep("yng", rownames(cpi_both_dist_df)), 
                         grep("old", colnames(cpi_both_dist_df))]

dist_oy <- rownames_to_column(dist_oy, var = "ct_pair_yng")

dist_oy_direct <- dist_oy %>%
  pivot_longer(cols = c(2:ncol(dist_oy)),
               names_to = "ct_pair_old",
               names_ptypes = list("ct_pair_old" = character()),
               values_to = "distance",
               values_ptypes = list("euclidian_distance" = numeric())
  )

dist_oy_direct$ct_pair_yng <- gsub(paste0("_", species, "_", "yng"), "", dist_oy_direct$ct_pair_yng)
dist_oy_direct$ct_pair_old <- gsub(paste0("_", species, "_", "old"), "", dist_oy_direct$ct_pair_old)


dist_oy_direct$emitter_old <- gsub("[&][[:print:]]+", "", dist_oy_direct$ct_pair_old)
dist_oy_direct$receiver_old <- gsub("[[:print:]]+[&]", "", dist_oy_direct$ct_pair_old)

dist_oy_direct$emitter_yng <- gsub("[&][[:print:]]+", "", dist_oy_direct$ct_pair_yng)
dist_oy_direct$receiver_yng <- gsub("[[:print:]]+[&]", "", dist_oy_direct$ct_pair_yng)

dist_oy_direct$emitter_old <- factor(dist_oy_direct$emitter_old,
                                levels = names(col_emi_red))
dist_oy_direct$emitter_yng <- factor(dist_oy_direct$emitter_yng,
                                levels = names(col_emi_red))

dist_oy_direct$receiver_old <- factor(dist_oy_direct$receiver_old,
                                levels = names(col_rec_red))
dist_oy_direct$receiver_yng <- factor(dist_oy_direct$receiver_yng,
                                levels = names(col_rec_red))

dist_oy_direct_direct <- dist_oy_direct[dist_oy_direct$ct_pair_yng == dist_oy_direct$ct_pair_old,]


```

```{r}

plot_direct_emi <- ggplot(dist_oy_direct_direct, 
                  aes(x = emitter_old, y = distance, color = emitter_old))+
  geom_quasirandom()
  

plot_direct_rec <- ggplot(dist_oy_direct_direct,
                  aes(x = receiver_old, y = distance, color = receiver_old))+
  geom_quasirandom()

plot_direct_emi
plot_direct_rec

```

## Distances within age groups

Euclidian distances within age groups.

Get all distances within young, then all distances within old. 
Then substract complete yng from complete old.

```{r}

cpi_both_dist_df_old <- cpi_both_dist_df[
  grep("old", colnames(cpi_both_dist_df)),
  grep("old", rownames(cpi_both_dist_df))]

cpi_both_dist_df_old <- cpi_both_dist_df_old[
  order(rownames(cpi_both_dist_df_old)),order(colnames(cpi_both_dist_df_old))]

cpi_both_dist_df_yng <- cpi_both_dist_df[
  grep("yng", colnames(cpi_both_dist_df)),
  grep("yng", rownames(cpi_both_dist_df))]

cpi_both_dist_df_yng <- cpi_both_dist_df_yng[
  order(rownames(cpi_both_dist_df_yng)),order(colnames(cpi_both_dist_df_yng))]

dist_df <- cpi_both_dist_df_old - cpi_both_dist_df_yng
dist_df <- dist_df[order(rownames(dist_df)),order(colnames(dist_df))]

```


```{r}

# change rownames and colnames to actual cell type names


rownames(dist_df) <- gsub(paste0("_", species, "_", "old"), "", rownames(dist_df))
colnames(dist_df) <- gsub(paste0("_", species, "_", "old"), "", colnames(dist_df))


dist_df <- rownames_to_column(dist_df, var = "ct_pair1")

dist_df_long <- dist_df %>%
  pivot_longer(cols = c(2:ncol(dist_df)),
               names_to = "ct_pair2",
               names_ptypes = list("ct_pair2" = character()),
               values_to = "distance",
               values_ptypes = list("euclidian_distance" = numeric())
  )


dist_df_long$emitter1 <- gsub("[&][[:print:]]+", "", dist_df_long$ct_pair1)
dist_df_long$receiver1 <- gsub("[[:print:]]+[&]", "", dist_df_long$ct_pair1)

dist_df_long$emitter2 <- gsub("[&][[:print:]]+", "", dist_df_long$ct_pair2)
dist_df_long$receiver2 <- gsub("[[:print:]]+[&]", "", dist_df_long$ct_pair2)

dist_df_long$emitter1 <- factor(dist_df_long$emitter1,
                                levels = names(col_emi_red))
dist_df_long$emitter2 <- factor(dist_df_long$emitter2,
                                levels = names(col_emi_red))

dist_df_long$receiver1 <- factor(dist_df_long$receiver1,
                                levels = names(col_rec_red))
dist_df_long$receiver2 <- factor(dist_df_long$receiver2,
                                levels = names(col_rec_red))
```


```{r}

median_emi1 <- dist_df_long %>%
  group_by(emitter1) %>%
  summarise(median_val = median(distance))

plot_within_emi <- ggplot(dist_df_long,
                  aes(x = emitter1, y = distance, color = emitter1))+
  geom_quasirandom(size = 0.2)+
  geom_point(median_emi1, mapping = aes(y = median_val), color = "black", 
             fill = "white",  shape = 22, size = 3, stroke = 1)

median_rec1 <- dist_df_long %>%
  group_by(receiver1) %>%
  summarise(median_val = median(distance))
  

plot_within_rec <- ggplot(dist_df_long, 
                  aes(x = receiver1, y = distance, color = receiver1))+
  geom_quasirandom(size = 0.2)+
  geom_point(median_rec1, mapping = aes(y = median_val), color = "black",
             fill = "white",  shape = 22, size = 3, stroke = 1)

  
plot_within_emi
plot_within_rec

```

## Clustering

Try different types of clustering.

```{r}

# ward d2 for type
cpi_both_ward <- hclust(cpi_both_dist, method = "ward.D2")
plot(cpi_both_ward, labels = FALSE, main = "ward.D2")

# others for spectrum
cpi_both_comp <- hclust(cpi_both_dist, method = "complete")
plot(cpi_both_comp, labels = FALSE, main = "complete")

cpi_both_avrg <- hclust(cpi_both_dist, method = "average")
plot(cpi_both_avrg, labels = FALSE, main = "average")

cpi_both_spct <- hclust(cpi_both_dist, method = "single")
plot(cpi_both_spct, labels = FALSE, main = "single")

```

Cut the tree at different places.
This should be decided after looking at the different methods and their 
branches.

```{r}

# cut the three into k clusters according to ward d2 method
cpi_both_ward_k4 <- cutree(cpi_both_ward, k = 4)
cpi_both_ward_k5 <- cutree(cpi_both_ward, k = 5)
cpi_both_ward_k6 <- cutree(cpi_both_ward, k = 6)

# add to cpi object
cpi_both$Celltypes$cluster <- cpi_both_ward_k6

```



### Visualise


Clustering

```{r}

# ward d2 for type
cpi_both_ward <- hclust(cpi_both_dist, method = "ward.D2")

# cut the three into k clusters according to ward d2 method
cpi_both_ward_k6 <- cutree(cpi_both_ward, k = 6)

# add to cpi object
cpi_both$Celltypes$cluster <- cpi_both_ward_k6

cpi_both$Celltypes$cluster_anno <- cpi_both$Celltypes$cluster

# name the clusters according to the cell type pairs they contain
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "1"] <- "mixed young"
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "2"] <- "mixed LMPPs"
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "3"] <- "mixed ECs"
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "4"] <- "mixed old"
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "5"] <- "old Mono/Dendr. prog."
cpi_both$Celltypes$cluster_anno[cpi_both$Celltypes$cluster == "6"] <- "old LT-HSCs"

cpi_both$Celltypes$cluster_anno <- factor(cpi_both$Celltypes$cluster_anno,
                                          levels = c("mixed young",
                                                     "mixed old",
                                                     "mixed ECs",
                                                     "old LT-HSCs",
                                                     "old Mono/Dendr. prog.",
                                                     "mixed LMPPs"))


```

Get HVGs

```{r}

var <- modelGeneVar(cpi_both$Score)

top_hvg <- getTopHVGs(var, var.field = "bio", n = 30)

top_hvg

```

Own color palette because most scores are 0 and there is nothing between 0 and 0.5


Annotations and annotation colours, one for each plot


```{r}

cpi_both_hvg <- cpi_both
cpi_both_hvg$Score <- cpi_both$Score[rownames(cpi_both$Score) %in% top_hvg,]
cpi_both_hvg$Interactions <- cpi_both$Interactions[rownames(cpi_both$Score) %in% top_hvg,]

anno_row_hvg <- data.frame(
  row.names = rownames(cpi_both_hvg$Score),
  Interactiontype = cpi_both_hvg$Interactions$interaction_type
)
order2_hvg <- order(anno_row_hvg$Interactiontype)

anno_col_hvg <- data.frame(
  row.names = colnames(cpi_both_hvg$Score),
  Cluster = as.character(cpi_both_hvg$Celltypes$cluster_anno)
)
# as already correctly ordered

# colours
heatmap_col_all <- list(
  Cluster = col_cls_man_anno,
  Interactiontype = col_itp
  )

pheatmap(cpi_both_hvg$Score[order2,],
         show_colnames = FALSE,
         show_rownames = FALSE,
         cluster_cols = cpi_both_ward,
         cluster_rows =  FALSE,
         annotation_col = anno_col_hvg,
         annotation_row = anno_row_hvg,
         annotation_colors = heatmap_col_all,
         main = c("Clustering of Young and Old Interaction Pairs"),
         color = mypalette
         )

```

```{r}

anno_row <- data.frame(
  row.names = rownames(cpi_both$Score),
  Interactiontype = cpi_both$Interactions$interaction_type
)
order2 <- order(anno_row$Interactiontype)

anno_col <- data.frame(
  row.names = colnames(cpi_both$Score),
  Cluster = as.character(cpi_both$Celltypes$cluster_anno)
)
# as already correctly ordered

# colours
heatmap_col_all <- list(
  Cluster = col_cls_man_anno,
  Interactiontype = col_itp
  )

pheatmap(cpi_both$Score[order2,],
         show_colnames = FALSE,
         show_rownames = FALSE,
         cluster_cols = cpi_both_ward,
         cluster_rows =  FALSE,
         annotation_col = anno_col,
         annotation_row = anno_row,
         annotation_colors = heatmap_col_all,
         main = c("Clustering of Young and Old Interaction Pairs"),
         color = mypalette
         )


```

