---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script analyses interactions at different levels for two cpi objects from 
YOUNG and OLD datasets of THE SAME SPECIES.

Replace the file path to load objects from different species.

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(ComplexUpset)
library(cowplot)
library(ggpubr)
library(ggbeeswarm)
library(pheatmap)
library(RColorBrewer)
library(viridis)
library(ggplotify)

library(scran)
library(ggpubr)
#library(scater)
#library(data.table)

```

## Load

### Code

```{r load_code, message = FALSE}

setwd("/home/l012t/Interspecies_BM")

source(file = "code/filepath.R")
source(file = "code/colors.R")
source(file = "interactome/functions/cpi_functions_analysis.R")

```

### Objects

Adjust the file paths to load objects from different species. 
After this, nothing needs to be changed.

```{r}

# merged and pre-processed SCE objects
sce_yng <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_ds_ctrm"))
sce_old <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_ds_ctrm"))

# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

cpi_both <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))

# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))
score_df_yng <-readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_ctpints_score_df"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))
score_df_old <-readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_ctpints_score_df"))

name_yng <- "mmus_yng"
name_old <- "mmus_old"
species <- "mmus"

max_ctpints <- 400
max_ctints <- 600
max_nrcells <- 10000
max_nrlrs <- 220

```

Merge overview dfs for direct comparion between age groups.

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctints_both <- rbind(ctints_yng[[1]], ctints_old[[1]])
ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))
ctints_both$celltypes <- factor(ctints_both$celltypes, 
                                levels = names(col_cts_red))
```

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))
```

```{r}

score_df_yng$age <- "young"
score_df_old$age <- "old"

score_df_both <- rbind(score_df_yng, score_df_old)
score_df_both$age <- factor(score_df_both$age, levels = c("young", "old"))
score_df_both$emitter <- factor(score_df_both$emitter, 
                               levels = names(col_emi_red))
score_df_both$receiver <- factor(score_df_both$receiver, 
                               levels = names(col_rec_red))

```


# Analysis

## Ligand/Receptor cell type level (sigmols)

Calculate the ctlrs object first.


```{r}

ctints_list <- list(ctints_yng, ctints_old)

ctlrs_list <- lapply(ctints_list, function(ctints){
  ctlrs <- lapply(ctints[[2]], extract_lrs_info)
  return(ctlrs)
})

ctlrs_yng <- ctlrs_list[[1]]
ctlrs_old <- ctlrs_list[[2]]

```

### Overlap between age groups

```{r}

sigmols_age_list <- list()
sigmols_age_vec <- vector()
for(i in names(ctlrs_yng)){

  shared_sigmols <- intersect(ctlrs_old[[i]]$sigmols, ctlrs_yng[[i]]$sigmols)

  unique_yng_sigmols <- ctlrs_yng[[i]]$sigmols[-which(ctlrs_yng[[i]]$sigmols %in% shared_sigmols)]
  unique_old_sigmols <- ctlrs_old[[i]]$sigmols[-which(ctlrs_old[[i]]$sigmols %in% shared_sigmols)]
  
  
  return_list <- list(
    shared_sigmols = shared_sigmols,
    unique_yng_sigmols = unique_yng_sigmols,
    unique_old_sigmols = unique_old_sigmols
  
  )
  
  sigmols_age_list[[i]] <- return_list
  sigmols_age_vec[i] <- length(shared_sigmols)
  
}

names(sigmols_age_list) <- names(ctlrs_yng)
names(sigmols_age_vec) <- names(ctlrs_yng)

```

```{r}

sigmols_shared_age <- data.frame(
  celltypes = names(col_cts_red),
  annotation = c(rep("emitter", 11), rep("receiver", 11))
)

sigmols_shared_age$shared <- vector(length = nrow(sigmols_shared_age))
sigmols_shared_age$old <- vector(length = nrow(sigmols_shared_age))
sigmols_shared_age$young <- vector(length = nrow(sigmols_shared_age))


for(i in unique(sigmols_shared_age$celltype)){
  
  siglist <- sigmols_age_list[[i]]
  
  sigmols_shared_age$shared[
    sigmols_shared_age$celltypes == i] <- length(siglist$shared_sigmols)
  sigmols_shared_age$old[
    sigmols_shared_age$celltypes == i] <- length(siglist$unique_old_sigmols)
  sigmols_shared_age$young[
    sigmols_shared_age$celltypes == i] <- length(siglist$unique_yng_sigmols)

}

sigmols_shared_age$old_total <- sigmols_shared_age$old + sigmols_shared_age$shared
sigmols_shared_age$yng_total <- sigmols_shared_age$young + sigmols_shared_age$shared
sigmols_shared_age$order <- sigmols_shared_age$shared

sigmols_shared_young <- pivot_longer(sigmols_shared_age,
                                     cols = c(3,5), names_to = "sample")

sigmols_shared_old <- pivot_longer(sigmols_shared_age,
                                     cols = c(3,4), names_to = "sample")

sigmols_shared_young$sample[sigmols_shared_young$sample == "young"] <- "exclusively young"
sigmols_shared_old$sample[sigmols_shared_old$sample == "old"] <- "exclusively old"

sigmols_shared_young$sample <- factor(sigmols_shared_young$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))
sigmols_shared_old$sample <- factor(sigmols_shared_old$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))

```

```{r}

legend_plot <- ggplot(sigmols_shared_young, 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))

legend_ctp_age <- get_legend(legend_plot)

plot_lrs_age_emi <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.35, 0.4),

  ggplot(sigmols_shared_young[sigmols_shared_young$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_nrlrs, 0),
                       breaks = c(-max_nrlrs, (-max_nrlrs* 0.5), 0),
                       labels = c(max_nrlrs, (max_nrlrs* 0.5), 0))+
    ylab("")+
    xlab("Number of ligands/cell type")+
    ggtitle(paste(species, "young"))+
    theme(legend.position = "none"),
 
  
   ggplot(sigmols_shared_old[sigmols_shared_old$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_text(size = 9, hjust = 0.5),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_nrlrs),
                       breaks = c(0, (max_nrlrs*0.5), max_nrlrs),
                       labels = c(0, (max_nrlrs*0.5), max_nrlrs))+
    ylab("Cell type pairs")+
    xlab("Number of ligands/cell type")+
    ggtitle(paste(species, "old"))+
    theme(legend.position = "none"),
  legend_ctp_age

    
)

plot_lrs_age_rec <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.5, 0.4),

  ggplot(sigmols_shared_young[sigmols_shared_young$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_nrlrs, 0),
                       breaks = c(-max_nrlrs, (-max_nrlrs* 0.5), 0),
                       labels = c(max_nrlrs, (max_nrlrs* 0.5), 0))+
    ylab("")+
    xlab("Number of receptors/cell type")+
    ggtitle(paste(species, "young"))+
    theme(legend.position = "none"),
 
  
   ggplot(sigmols_shared_old[sigmols_shared_old$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_text(size = 9, hjust = 0.5),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_nrlrs),
                       breaks = c(0, (max_nrlrs*0.5), max_nrlrs),
                       labels = c(0, (max_nrlrs*0.5), max_nrlrs))+
    ylab("Cell type pairs")+
    xlab("Number of receptors/cell type")+
    ggtitle(paste(species, "old"))+
    theme(legend.position = "none"),
  legend_ctp_age

    
)

plot_lrs_age_emi
plot_lrs_age_rec

```

```{r}

sigmols_shared_age$perc_unique_old <- sigmols_shared_age$old/sigmols_shared_age$old_total*100
sigmols_shared_age$perc_unique_yng <- sigmols_shared_age$young/sigmols_shared_age$yng_total*100

sigmols_shared_age_long <- sigmols_shared_age %>%
  pivot_longer(cols = c(9, 10), names_to = "age", values_to = "unique_percent")

sigmols_shared_age_long$annotation[sigmols_shared_age_long$annotation == "emitter"] <- "Emitters"
sigmols_shared_age_long$annotation[sigmols_shared_age_long$annotation == "receiver"] <- "Receivers"
 
sigmols_shared_age_long$age <- gsub("perc_unique_", "", sigmols_shared_age_long$age)
sigmols_shared_age_long$age[sigmols_shared_age_long$age == "yng"] <- "young"
sigmols_shared_age_long$age <- factor(sigmols_shared_age_long$age, levels = c("young", "old"))

plot_emirec_unique <- ggplot(sigmols_shared_age_long, 
                             aes(x = annotation, y = unique_percent, 
                                 color = age))+
  geom_boxplot()

plot_emirec_unique

```


Get the genes exclusively detected in old or young.

```{r}

shared_sigmols_all <- vector()
yng_sigmols_all <- vector()
old_sigmols_all <- vector()

for(i in 1:length(sigmols_age_list)){
  
  shared_sigmols_all <- c(shared_sigmols_all, sigmols_age_list[[i]][[1]])
  yng_sigmols_all <- c(yng_sigmols_all, sigmols_age_list[[i]][[2]])
  old_sigmols_all <- c(old_sigmols_all, sigmols_age_list[[i]][[3]])
}

# remove all duplicates
shared_sigmols_all <- unique(shared_sigmols_all)
yng_sigmols_all <- unique(yng_sigmols_all)
old_sigmols_all <- unique(old_sigmols_all)

# it is possible that one ligand exclusively expressedin CT1 old is expressed in CT2 young
table(is.na(match(shared_sigmols_all, yng_sigmols_all)))
table(is.na(match(shared_sigmols_all, old_sigmols_all)))
table(is.na(match(yng_sigmols_all, old_sigmols_all)))
# there is significant overlap

yng_sigmols_all <- yng_sigmols_all[is.na(match(yng_sigmols_all, old_sigmols_all))]
yng_sigmols_all <- yng_sigmols_all[is.na(match(yng_sigmols_all, shared_sigmols_all))]

old_sigmols_all <- old_sigmols_all[is.na(match(old_sigmols_all, yng_sigmols_all))]
old_sigmols_all <- old_sigmols_all[is.na(match(old_sigmols_all, shared_sigmols_all))]

old_genes <- old_sigmols_all
yng_genes <- yng_sigmols_all

old_genes
yng_genes

```

With these genes I want to perform GO term enrichment analysis.

```{r}

old_genes <- factor(old_genes, levels = old_genes)
levels(old_genes)

all_genes <- unique(c(cpi_both$Interactions$ligand_symbol, cpi_both$Interactions$receptor_symbol))
all_genes <- factor(all_genes, levels = all_genes)

all_genes_df <- data.frame(
  genes = all_genes,
  filler = rep("1", length(all_genes))
)

write_csv(all_genes_df, file = "../../data/all_genes_df.csv")

old_genes_df <- data.frame(
  genes = old_genes,
  filler = rep("1", length(old_genes))
)

write_csv(old_genes_df, file = "../../data/old_genes_df.csv")


```


### Ligand/Receptor overlap between cell types

percentage of overlap

```{r}

ctlrs_binary_yng <- data.frame(
  row.names = unique(c(cpi_yng$Interactions$ligand_symbol,
                     cpi_yng$Interactions$receptor_symbol)))

for(i in 1:length(names(ctlrs_yng))){
  ctlrs_binary_yng[,i] <- vector(length = nrow(ctlrs_binary_yng))

}

colnames(ctlrs_binary_yng) <- names(ctlrs_yng)

for(j in 1:length(names(ctlrs_yng))){
  for(i in 1:nrow(ctlrs_binary_yng)){
    if(rownames(ctlrs_binary_yng)[i] %in% ctlrs_yng[[j]]$sigmols){
      ctlrs_binary_yng[i,j] <- 1
    }else{
      ctlrs_binary_yng[i,j] <- 0
    }
  }
}

ctlrs_binary_yng_emi <- ctlrs_binary_yng[,1:11]
ctlrs_binary_yng_rec <- ctlrs_binary_yng[,12:22]

ctlrs_binary_yng_emi <- ctlrs_binary_yng_emi[rowMeans(ctlrs_binary_yng_emi[,1:11]) > 0,]
ctlrs_binary_yng_rec <- ctlrs_binary_yng_rec[rowMeans(ctlrs_binary_yng_rec[,1:11]) > 0,]
ctlrs_binary_yng <- ctlrs_binary_yng[rowMeans(ctlrs_binary_yng[,1:22]) > 0,]


ctlrs_binary_old <- data.frame(
  row.names = unique(c(cpi_old$Interactions$ligand_symbol,
                     cpi_old$Interactions$receptor_symbol)))

for(i in 1:length(names(ctlrs_old))){
  ctlrs_binary_old[,i] <- vector(length = nrow(ctlrs_binary_old))

}

colnames(ctlrs_binary_old) <- names(ctlrs_old)

for(j in 1:length(names(ctlrs_old))){
  for(i in 1:nrow(ctlrs_binary_old)){
    if(rownames(ctlrs_binary_old)[i] %in% ctlrs_old[[j]]$sigmols){
      ctlrs_binary_old[i,j] <- 1
    }else{
      ctlrs_binary_old[i,j] <- 0
    }
  }
}

ctlrs_binary_old_emi <- ctlrs_binary_old[,1:11]
ctlrs_binary_old_rec <- ctlrs_binary_old[,12:22]

ctlrs_binary_old_emi <- ctlrs_binary_old_emi[rowMeans(ctlrs_binary_old_emi[,1:11]) > 0,]
ctlrs_binary_old_rec <- ctlrs_binary_old_rec[rowMeans(ctlrs_binary_old_rec[,1:11]) > 0,]
ctlrs_binary_old <- ctlrs_binary_old[rowMeans(ctlrs_binary_old[,1:22]) > 0,]

```


```{r fig.width = 6}

ctlrs_binary_yng$shared <- vector(length = nrow(ctlrs_binary_yng))
ctlrs_binary_yng_emi$shared_emi <- vector(length = nrow(ctlrs_binary_yng_emi))
ctlrs_binary_yng_rec$shared_rec <- vector(length = nrow(ctlrs_binary_yng_rec))


ctlrs_binary_yng$shared[rowMeans(ctlrs_binary_yng[1:22]) == 1] <- TRUE
ctlrs_binary_yng_emi$shared_emi[rowMeans(ctlrs_binary_yng_emi[1:11]) == 1] <- TRUE
ctlrs_binary_yng_rec$shared_rec[rowMeans(ctlrs_binary_yng_rec[1:11]) == 1] <- TRUE


ctlrs_yng_emi_plot <- upset(ctlrs_binary_yng_emi,
      intersect = colnames(ctlrs_binary_yng_emi[,1:11]),
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_emi),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 55))+
              ggtitle(paste(species, "young", "emitters", sep = " "))
        )
    )
)


ctlrs_yng_rec_plot <-upset(ctlrs_binary_yng_rec,
      intersect = colnames(ctlrs_binary_yng_rec[,1:11]),
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_rec),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 55))+
              ggtitle(paste(species, "young", "receivers", sep = " "))
        )
    )
)


ctlrs_yng_plot <-upset(ctlrs_binary_yng,
      intersect = colnames(ctlrs_binary_yng[,1:22]),
     sort_intersections_by = c("cardinality", "ratio"),
     height_ratio = 0.8,
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 55))+
              ggtitle(paste(species, "young", "all cell types", sep = " "))
        )
    )
)

ctlrs_yng_emi_plot
ctlrs_yng_rec_plot
ctlrs_yng_plot

```

```{r fig.width = 6}

ctlrs_binary_old$shared <- vector(length = nrow(ctlrs_binary_old))
ctlrs_binary_old_emi$shared_emi <- vector(length = nrow(ctlrs_binary_old_emi))
ctlrs_binary_old_rec$shared_rec <- vector(length = nrow(ctlrs_binary_old_rec))


ctlrs_binary_old$shared[rowMeans(ctlrs_binary_old[1:22]) == 1] <- TRUE
ctlrs_binary_old_emi$shared_emi[rowMeans(ctlrs_binary_old_emi[1:11]) == 1] <- TRUE
ctlrs_binary_old_rec$shared_rec[rowMeans(ctlrs_binary_old_rec[1:11]) == 1] <- TRUE


ctlrs_old_emi_plot <- ctlrs_binary_emi_plot <-upset(ctlrs_binary_old_emi,
      intersect = colnames(ctlrs_binary_old_emi[,1:11]),
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_emi),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 80))+
              ggtitle(paste(species, "old", "emitters", sep = " "))
        )
    )
)


ctlrs_old_rec_plot <- upset(ctlrs_binary_old_rec,
      intersect = colnames(ctlrs_binary_old_rec[,1:11]),
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_rec),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 80))+
              ggtitle(paste(species, "old", "receivers", sep = " "))
        )
    )
)


ctlrs_old_plot <- upset(ctlrs_binary_old,
      intersect = colnames(ctlrs_binary_old[,1:22]),
     sort_intersections_by = c("cardinality", "ratio"),
     height_ratio = 0.8,
      min_size = 5,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
          # base theme
          theme_classic()+
          theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_nrlrs))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE)+
            # base theme
            theme_classic()+
            theme(axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.title = element_text(size = 9, face = "bold"),
            legend.text = element_text(size = 8),
            plot.title = element_text(size = 10, face = "bold"))+
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 80))+
              ggtitle(paste(species, "old", "all cell types", sep = " "))
        )
    )
)

ctlrs_old_emi_plot 
ctlrs_old_rec_plot 
ctlrs_old_plot 
  
```

### Percentage of shared interactions

```{r}

# ligands
perc_lig_yng <- data.frame(
  row.names = colnames(ctlrs_binary_yng_emi)[1:11],
  percent = vector(length = 11),
  age = rep("young", 11),
  annotation = rep("Ligands", 11)
)

for(i in 1:nrow(perc_lig_yng)){
  
  shared <- length(which(ctlrs_binary_yng_emi$shared_emi == TRUE))
  perc_lig_yng$percent[i] <- shared/length(which(ctlrs_binary_yng_emi[i] == 1))*100
}
perc_lig_yng

perc_lig_old <- data.frame(
  row.names = colnames(ctlrs_binary_old_emi)[1:11],
  percent = vector(length = 11),
  age = rep("old", 11),
  annotation = rep("Ligands", 11)
)

for(i in 1:nrow(perc_lig_old)){
  
  shared <- length(which(ctlrs_binary_old_emi$shared_emi == TRUE))
  perc_lig_old$percent[i] <- shared/length(which(ctlrs_binary_old_emi[i] == 1))*100
}
perc_lig_old


# receptors
perc_rec_yng <- data.frame(
  row.names = colnames(ctlrs_binary_yng_rec)[1:11],
  percent = vector(length = 11),
  age = rep("young", 11),
  annotation = rep("Receptors", 11)
)

for(i in 1:nrow(perc_rec_yng)){
  
  shared <- length(which(ctlrs_binary_yng_rec$shared_rec == TRUE))
  perc_rec_yng$percent[i] <- shared/length(which(ctlrs_binary_yng_rec[i] == 1))*100
}
perc_rec_yng

perc_rec_old <- data.frame(
  row.names = colnames(ctlrs_binary_old_rec)[1:11],
  percent = vector(length = 11),
  age = rep("old", 11),
  annotation = rep("Receptors", 11)
)

for(i in 1:nrow(perc_rec_old)){
  
  shared <- length(which(ctlrs_binary_old_rec$shared_rec == TRUE))
  perc_rec_old$percent[i] <- shared/length(which(ctlrs_binary_old_rec[i] == 1))*100
}

perc_rec_old

perc_all_lig <- rbind(perc_lig_yng, perc_lig_old)
perc_all_rec <- rbind(perc_rec_yng, perc_rec_old)

perc_all_lig$age <- factor(perc_all_lig$age, levels = c("young", "old"))
perc_all_rec$age <- factor(perc_all_rec$age, levels = c("young", "old"))

perc_all_lig$percent_unique <- 100 -perc_all_lig$percent
perc_all_rec$percent_unique <- 100 -perc_all_rec$percent

```

```{r}

ggplot(perc_all_lig, aes(x = age, y = percent, color = age))+
  geom_boxplot()+
  ylim(limits = c(0,100))+
  theme_classic()+
  scale_color_manual("Age", values = col_age)+
  ylab("Shared ligands per emitter [%]")

ggplot(perc_all_rec, aes(x = age, y = percent, color = age))+
  geom_boxplot()+
  ylim(limits = c(0,100))+
  theme_classic()+
  scale_color_manual("Age", values = col_age)+
  ylab("Shared receptors per receiver [%]")

median(perc_all_lig$percent[perc_all_lig$age == "old"])
median(perc_all_lig$percent[perc_all_lig$age == "young"])

median(perc_all_rec$percent[perc_all_rec$age == "old"])
median(perc_all_rec$percent[perc_all_rec$age == "young"])


```


### Directly compare ranks

```{r}

# make on df with ints for young
ctints_yng_all <- data.frame(
  interactions = vector(),
  celltype = vector(),
  annotation = vector(),
  rank = vector()
)

for(i in 1:length(ctints_yng[[2]])){
  
  ctints_yng_all <- rbind(ctints_yng_all, ctints_yng[[2]][[i]])
}

# one for old
ctints_old_all <- data.frame(
  interactions = vector(),
  celltype = vector(),
  annotation = vector(),
  rank = vector()
)

for(i in 1:length(ctints_yng[[2]])){
  
  ctints_old_all <- rbind(ctints_old_all, ctints_old[[2]][[i]])
}

# add info on age and separate interactions into ligand, receptors
ctints_yng_all$age <- "young"
ctints_yng_all$celltype <- paste0(ctints_yng_all$celltype, "_yng")

ctints_yng_all$ligand <- gsub("[&][[:print:]]+", "", ctints_yng_all$interactions)
ctints_yng_all$receptor <- gsub("[[:print:]]+[&]", "", ctints_yng_all$interactions)

ctints_old_all$age <- "old"
ctints_old_all$celltype <- paste0(ctints_old_all$celltype, "_old")

ctints_old_all$ligand <- gsub("[&][[:print:]]+", "", ctints_old_all$interactions)
ctints_old_all$receptor <- gsub("[[:print:]]+[&]", "", ctints_old_all$interactions)

# rbind into one df
ctints_all <- rbind(ctints_yng_all, ctints_old_all)

# make a dataframe that fits heatmap
ctints_all_test <- ctints_all %>%
  pivot_wider(names_from = celltype, values_from = rank)

# make one dataframe for ligand ranks
ctints_all_test_lig <- data.frame(
  row.names = unique(ctints_all$ligand)
)
ctints_all_test_lig[,1:44] <- vector(length = nrow(ctints_all_test_lig))
colnames(ctints_all_test_lig) <- colnames(ctints_all_test[,6:49])

for(i in 1:ncol(ctints_all_test_lig)){
  for(j in 1:nrow(ctints_all_test_lig)){
    
    celltype <- colnames(ctints_all_test_lig)[i]
    ligand <- rownames(ctints_all_test_lig)[j]
    
    ctints_all_test_lig[j,i] <- as.numeric(
      ctints_all_test[
        # only the row of the ligand in question
        grep(ligand, ctints_all_test$ligand)[
          # since each interaction is not detected in all ages, choose the first that is not NA
          which(!is.na(ctints_all_test[
            grep(ligand, ctints_all_test$ligand), 
            grep(celltype, colnames(ctints_all_test))]))[1]],
        # only the col of the cell type in question
      grep(celltype, colnames(ctints_all_test))])
  }
}

# make one for receptor ranks

ctints_all_test_rec <- data.frame(
  row.names = unique(ctints_all$receptor)
)
ctints_all_test_rec[,1:44] <- vector(length = nrow(ctints_all_test_rec))
colnames(ctints_all_test_rec) <- colnames(ctints_all_test[,6:49])

for(i in 1:ncol(ctints_all_test_rec)){
  for(j in 1:nrow(ctints_all_test_rec)){
    
    celltype <- colnames(ctints_all_test_rec)[i]
    receptor <- rownames(ctints_all_test_rec)[j]
    
    ctints_all_test_rec[j,i] <- as.numeric(
      ctints_all_test[
        # only the row of the receptor in question
        grep(receptor, ctints_all_test$receptor)[
          # since each interaction is not detected in all ages, choose the first that is not NA
          which(!is.na(ctints_all_test[
            grep(receptor, ctints_all_test$receptor), 
            grep(celltype, colnames(ctints_all_test))]))[1]],
        # only the col of the cell type in question
      grep(celltype, colnames(ctints_all_test))])
  }
}

```

My color scheme for ranks

```{r}

min_rank <- min(ctints_all$rank[ctints_all$rank != 0])

zero_to_min_r = rep(viridis(n = 1, option = "D", begin = 0.3, end = 0.3),
                    min_rank*100)
min_to_1_r = viridis(n = c((min_rank*100:100)), option = "D", begin = 0.3,
                     end = 1)


cols_r = c(zero_to_min_r, min_to_1_r)

mypalette <- colorRampPalette(cols_r)(255)

```

#### Ligands

```{r}

ctints_all_test_lig[is.na(ctints_all_test_lig)] <- 0

ctints_all_test_emi <- ctints_all_test_lig[,c(1:11, 23:33)]
ctints_all_test_emi <- ctints_all_test_emi[which(rowMeans(ctints_all_test_emi) >0),]

match_pos_emi <- match(names(col_emi_red), 
                       gsub("_yng", "", colnames(ctints_all_test_emi)))

match_pos_emi <- c(match_pos_emi, match_pos_emi+11)

ctints_all_test_emi <- ctints_all_test_emi[,match_pos_emi]

anno_col_emi <- data.frame(
  row.names = colnames(ctints_all_test_emi),
  Age = c(rep("young", 11), rep("old", 11)),
  Celltypes = c(names(col_emi_red)[], names(col_emi_red))
)

color_list_emi <- list(
  "Age" = col_age,
  "Celltypes" = col_emi_red
)

plot_ligands <- as.ggplot(pheatmap(ctints_all_test_emi,
         cluster_cols = FALSE, 
         color = mypalette,
         show_rownames = FALSE,
         show_colnames = FALSE,
         annotation_col = anno_col_emi,
         annotation_colors = color_list_emi,
         fontsize = 12))

```

#### Receptors

```{r}

ctints_all_test_rec[is.na(ctints_all_test_rec)] <- 0

ctints_all_test_rece <- ctints_all_test_lig[,c(12:22, 34:44)]
ctints_all_test_rece <- ctints_all_test_rece[which(rowMeans(ctints_all_test_rece) >0),]

match_pos_rec <- match(names(col_rec_red), 
                       gsub("_yng", "", colnames(ctints_all_test_rece)))

match_pos_rec <- c(match_pos_rec, match_pos_rec+11)

ctints_all_test_rece <- ctints_all_test_rece[,match_pos_rec]

anno_col_rec <- data.frame(
  row.names = colnames(ctints_all_test_rece),
  Age = c(rep("young", 11), rep("old", 11)),
  Celltypes = c(names(col_rec_red))
)

color_list_rec <- list(
  "Age" = col_age,
  "Celltypes" = col_rec_red
)

plot_receptors <- as.ggplot(pheatmap(ctints_all_test_rece,
         cluster_cols = FALSE, 
         color = mypalette,
         show_rownames = FALSE,
         show_colnames = FALSE,
         annotation_col = anno_col_rec,
         annotation_colors = color_list_rec,
         fontsize = 12))

```

Ligand variability within age group

```{r}


ctints_all_test_emi_Test <- ctints_all_test_emi
ctints_all_test_emi_Test <- rownames_to_column(ctints_all_test_emi_Test, "ligands")

ctints_all_test_emi_Test <- ctints_all_test_emi_Test %>%
  pivot_longer(cols = c(2:ncol(ctints_all_test_emi_Test)), values_to = "ranks",
               names_to = "celltypes")

ctints_all_test_emi_Test$age <- gsub("[[:print:]]+[_]", "", ctints_all_test_emi_Test$celltypes)
ctints_all_test_emi_Test$age[ctints_all_test_emi_Test$age == "yng"] <- "young"

ctints_all_test_emi_var_yng <- ctints_all_test_emi_Test[ctints_all_test_emi_Test$age == "young",] %>%
  group_by(ligands) %>%
  summarise(yng_emi_var = var(ranks))

ctints_all_test_emi_var_old <- ctints_all_test_emi_Test[ctints_all_test_emi_Test$age == "old",] %>%
  group_by(ligands) %>%
  summarise(old_emi_var = var(ranks))


emi_var <- cbind(ctints_all_test_emi_var_old, ctints_all_test_emi_var_yng)
emi_var <- emi_var %>%
  pivot_longer(cols = c("old_emi_var", "yng_emi_var"), names_to = "age", values_to = "var")
  
emi_var$age[emi_var$age == "old_emi_var"] <- "old"
emi_var$age[emi_var$age == "yng_emi_var"] <- "young"
emi_var$age <- factor(emi_var$age, levels = c("young", "old"))

```

```{r}

median_ligand <- emi_var %>%
  group_by(age) %>%
  summarise(med_lig = median(var))

plot_ligand_var <- ggplot(emi_var, aes(x = age, y = var, color = age))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_ligand, mapping = aes(y = med_lig), color = "black", 
           fill = "orange",  shape = 22, size = 5, stroke = 1)

plot_ligand_var

median_ligand

```

```{r}

ctints_all_test_rec_Test <- ctints_all_test_rec[,c(12:22, 34:44)]
ctints_all_test_rec_Test <- rownames_to_column(ctints_all_test_rec_Test, "receptors")

ctints_all_test_rec_Test <- ctints_all_test_rec_Test %>%
  pivot_longer(cols = c(2:ncol(ctints_all_test_rec_Test)), values_to = "ranks",
               names_to = "celltypes")

ctints_all_test_rec_Test$age <- gsub("[[:print:]]+[_]", "", ctints_all_test_rec_Test$celltypes)
ctints_all_test_rec_Test$age[ctints_all_test_rec_Test$age == "yng"] <- "young"

ctints_all_test_rec_var_yng <- ctints_all_test_rec_Test[ctints_all_test_rec_Test$age == "young",] %>%
  group_by(receptors) %>%
  summarise(yng_rec_var = var(ranks))

ctints_all_test_rec_var_old <- ctints_all_test_rec_Test[ctints_all_test_rec_Test$age == "old",] %>%
  group_by(receptors) %>%
  summarise(old_rec_var = var(ranks))


rec_var <- cbind(ctints_all_test_rec_var_old, ctints_all_test_rec_var_yng)
rec_var <- rec_var %>%
  pivot_longer(cols = c("old_rec_var", "yng_rec_var"), names_to = "age", values_to = "var")
  
rec_var$age[rec_var$age == "old_rec_var"] <- "old"
rec_var$age[rec_var$age == "yng_rec_var"] <- "young"
rec_var$age <- factor(rec_var$age, levels = c("young", "old"))


```

```{r}

median_receptor <- rec_var %>%
  group_by(age) %>%
  summarise(med_rec = median(var))
  
  
plot_receptor_var <- ggplot(rec_var, aes(x = age, y = var, color = age))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_receptor, mapping = aes(y = med_rec), color = "black", 
           fill = "orange",  shape = 22, size = 5, stroke = 1)

plot_receptor_var

median_receptor

```

## Cell type interactions level

### Overlap between age groups

```{r}

ctints_shared_age_list <- list()
ctints_shared_age_vec <- vector()
for(i in names(ctints_yng[[2]])){

  shared_ints <- intersect(ctints_yng[[2]][[i]]$interactions, 
                           ctints_old[[2]][[i]]$interactions)

  unique_yng_ints <- ctints_yng[[2]][[i]]$interactions[
    -which(ctints_yng[[2]][[i]]$interactions %in% shared_ints)]
  unique_old_ints <- ctints_old[[2]][[i]]$interactions[
    -which(ctints_old[[2]][[i]]$interactions %in% shared_ints)]
  
  
  return_list <- list(
    shared_ints = shared_ints,
    unique_yng_ints = unique_yng_ints,
    unique_old_ints = unique_old_ints
  
  )
  
  ctints_shared_age_list[[i]] <- return_list
  ctints_shared_age_vec[i] <- length(shared_ints)
}

names(ctints_shared_age_list) <- names(ctints_yng[[2]])
names(ctints_shared_age_vec) <- names(ctints_yng[[2]])

```

```{r}

ctints_shared_age <- data.frame(
  celltypes = names(col_cts_red),
  annotation = c(rep("emitter", 11), rep("receiver", 11))
)

ctints_shared_age$shared <- vector(length = nrow(ctints_shared_age))
ctints_shared_age$old <- vector(length = nrow(ctints_shared_age))
ctints_shared_age$young <- vector(length = nrow(ctints_shared_age))


for(i in unique(ctints_shared_age$celltype)){
  
  ctints_list <- ctints_shared_age_list[[i]]
  
  ctints_shared_age$shared[
    ctints_shared_age$celltypes == i] <- length(ctints_list$shared_ints)
  ctints_shared_age$old[
    ctints_shared_age$celltypes == i] <- length(ctints_list$unique_old_ints)
  ctints_shared_age$young[
    ctints_shared_age$celltypes == i] <- length(ctints_list$unique_yng_ints)

}

ctints_shared_age$old_total <- ctints_shared_age$old + ctints_shared_age$shared
ctints_shared_age$yng_total <- ctints_shared_age$young + ctints_shared_age$shared
ctints_shared_age$order <- ctints_shared_age$shared

ctints_shared_young <- pivot_longer(ctints_shared_age,
                                     cols = c(3,5), names_to = "sample")

ctints_shared_old <- pivot_longer(ctints_shared_age,
                                     cols = c(3,4), names_to = "sample")

ctints_shared_young$sample[ctints_shared_young$sample == "young"] <- "exclusively young"
ctints_shared_old$sample[ctints_shared_old$sample == "old"] <- "exclusively old"

ctints_shared_young$sample <- factor(ctints_shared_young$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))
ctints_shared_old$sample <- factor(ctints_shared_old$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))

```

```{r}

legend_plot <- ggplot(ctints_shared_young, 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))

legend_ctp_age <- get_legend(legend_plot)

plot_ctints_age_emi <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.35, 0.4),

  ggplot(ctints_shared_young[ctints_shared_young$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_ctints, 0),
                       breaks = c(-max_ctints, (-max_ctints* 0.5), 0),
                       labels = c(max_ctints, (max_ctints* 0.5), 0))+
    ylab("")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "young"))+
    theme(legend.position = "none"),
 
  
   ggplot(ctints_shared_old[ctints_shared_old$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_text(size = 9, hjust = 0.5),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_ctints),
                       breaks = c(0, (max_ctints*0.5), max_ctints),
                       labels = c(0, (max_ctints*0.5), max_ctints))+
    ylab("Cell type pairs")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "old"))+
    theme(legend.position = "none"),
  legend_ctp_age

    
)

plot_ctints_age_rec <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.5, 0.4),

  ggplot(ctints_shared_young[ctints_shared_young$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_ctints, 0),
                       breaks = c(-max_ctints, (-max_ctints* 0.5), 0),
                       labels = c(max_ctints, (max_ctints* 0.5), 0))+
    ylab("")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "young"))+
    theme(legend.position = "none"),
 
  
   ggplot(ctints_shared_old[ctints_shared_old$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_text(size = 9, hjust = 0.5),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_ctints),
                       breaks = c(0, (max_ctints*0.5), max_ctints),
                       labels = c(0, (max_ctints*0.5), max_ctints))+
    ylab("Cell type pairs")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "old"))+
    theme(legend.position = "none"),
  legend_ctp_age

    
)

plot_ctints_age_emi
plot_ctints_age_rec

```

```{r}

ctints_shared_age$unique_percent_old <- ctints_shared_age$old/ctints_shared_age$old_total*100
ctints_shared_age$unique_percent_yng <- ctints_shared_age$young/ctints_shared_age$yng_total*100


ctints_shared_age_long <- ctints_shared_age %>%
  pivot_longer(cols = c(9, 10), names_to = "age", values_to = "unique_percent")


ctints_shared_age_long$annotation[ctints_shared_age_long$annotation == "emitter"] <- "Emitters"
ctints_shared_age_long$annotation[ctints_shared_age_long$annotation == "receiver"] <- "Receivers"


ctints_shared_age_long$age <- gsub("unique_percent_", "", ctints_shared_age_long$age)
ctints_shared_age_long$age[ctints_shared_age_long$age == "yng"] <- "young"
ctints_shared_age_long$age <- factor(ctints_shared_age_long$age, levels = c("young", "old"))


plot_emirec_unique_ints <- ggplot(ctints_shared_age_long, 
                             aes(x = annotation, y = unique_percent, 
                                 color = age))+
  geom_boxplot()

plot_emirec_unique_ints

```



### Interaction overlap between cell types

percentage of overlap

```{r}

ctints_binary_yng <- data.frame(row.names = cpi_yng$Interactions$interaction_pair)

for(i in 1:length(names(ctints_yng[[2]]))){
  ctints_binary_yng[,i] <- vector(length = nrow(ctints_binary_yng))

}

colnames(ctints_binary_yng) <- names(ctints_yng[[2]])

for(j in 1:length(names(ctints_yng[[2]]))){
  for(i in 1:nrow(ctints_binary_yng)){
    if(rownames(ctints_binary_yng)[i] %in% ctints_yng[[2]][[j]]$interactions){
      ctints_binary_yng[i,j] <- 1
    }else{
      ctints_binary_yng[i,j] <- 0
    }
  }
}

ctints_binary_yng$interaction_type <- cpi_yng$Interactions$interaction_type
ctints_binary_yng <- ctints_binary_yng[rowMeans(ctints_binary_yng[,1:22]) > 0,]


ctints_binary_old <- data.frame(row.names = cpi_old$Interactions$interaction_pair)

for(i in 1:length(names(ctints_old[[2]]))){
  ctints_binary_old[,i] <- vector(length = nrow(ctints_binary_old))

}

colnames(ctints_binary_old) <- names(ctints_old[[2]])

for(j in 1:length(ctints_old[[2]])){
  for(i in 1:nrow(ctints_binary_old)){
    if(rownames(ctints_binary_old)[i] %in% ctints_old[[2]][[j]]$interactions){
      ctints_binary_old[i,j] <- 1
    }else{
      ctints_binary_old[i,j] <- 0
    }
  }
}

ctints_binary_old$interaction_type <- cpi_old$Interactions$interaction_type
ctints_binary_old <- ctints_binary_old[rowMeans(ctints_binary_old[,1:22]) > 0,]

```


```{r fig.width = 6}

ctints_binary_yng$shared <- vector(length = nrow(ctints_binary_yng))
ctints_binary_yng$shared_rec <- vector(length = nrow(ctints_binary_yng))
ctints_binary_yng$shared_emi <- vector(length = nrow(ctints_binary_yng))
ctints_binary_yng$shared_emi[rowMeans(ctints_binary_yng[1:11]) == 1] <- TRUE
ctints_binary_yng$shared_rec[rowMeans(ctints_binary_yng[12:22]) == 1] <- TRUE
ctints_binary_yng$shared[rowMeans(ctints_binary_yng[1:22]) == 1] <- TRUE


ctints_yng_emi_plot <- upset(ctints_binary_yng,
      intersect = colnames(ctints_binary_yng)[1:11],
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 15,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_emi),
            width=0.8),
            position='right')+
          # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
           # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "young", "emitters", sep = " "))
        )
    )
)


ctints_yng_rec_plot <- upset(ctints_binary_yng,
      intersect = colnames(ctints_binary_yng)[12:22],
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 15,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_rec),
            width=0.8),
            position='right')+
         # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
            # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "young", "receivers", sep = " "))
        )
    )
)


ctints_yng_plot <- upset(ctints_binary_yng,
      intersect = colnames(ctints_binary_yng[,1:22]),
     sort_intersections_by = c("cardinality", "ratio"),
     height_ratio = 0.8,
      min_size = 15,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
         # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
           # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "young", "all cell types", sep = " "))
        )
    )
)

ctints_yng_emi_plot
ctints_yng_rec_plot 
ctints_yng_plot 

```

```{r fig.width = 6}

ctints_binary_old$shared <- vector(length = nrow(ctints_binary_old))
ctints_binary_old$shared_rec <- vector(length = nrow(ctints_binary_old))
ctints_binary_old$shared_emi <- vector(length = nrow(ctints_binary_old))
ctints_binary_old$shared_emi[rowMeans(ctints_binary_old[1:11]) == 1] <- TRUE
ctints_binary_old$shared_rec[rowMeans(ctints_binary_old[12:22]) == 1] <- TRUE
ctints_binary_old$shared[rowMeans(ctints_binary_old[1:22]) == 1] <- TRUE


ctints_old_emi_plot <- upset(ctints_binary_old,
      intersect = colnames(ctints_binary_old)[1:11],
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 15,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_emi),
            width=0.8),
            position='right')+
         # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[2]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
           # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "old", "emitters", sep = " "))
        )
    )
)


ctints_old_rec_plot <- upset(ctints_binary_old,
      intersect = colnames(ctints_binary_old)[12:22],
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 15,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared_rec),
            width=0.8),
            position='right')+
        # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          # individual
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
           # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "old", "receivers", sep = " "))
        )
    )
)


ctints_old_plot <- upset(ctints_binary_old,
      intersect = colnames(ctints_binary_old[,1:22]),
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 10,
     height_ratio = 0.8,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
          # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[1]]))+
          ylab("Interactions/cell type")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point())+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
            # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0, 220))+
              ggtitle(paste(species, "old", "all cell types", sep = " "))
        )
    )
)

ctints_old_emi_plot
ctints_old_rec_plot 
ctints_old_plot

```


## Cell type pair level

### Overlap between age groups

get a list of shared, exclusively young and exclusively old interactions.

```{r}

ctpints_shared_age_list <- list()
ctpints_shared_age_vec <- vector()
for(i in 1:length(names(ctpints_yng[[2]]))){

  shared_intsctp <- intersect(ctpints_yng[[2]][[i]]$interaction, ctpints_old[[2]][[i]]$interaction)

  unique_yng_intsctp <- ctpints_yng[[2]][[i]]$interaction[-which(ctpints_yng[[2]][[i]]$interaction %in% shared_intsctp)]
  unique_old_intsctp <- ctpints_old[[2]][[i]]$interaction[-which(ctpints_old[[2]][[i]]$interaction %in% shared_intsctp)]
  
  print(i)
  print(grep("Rims2&Abca1",unique_old_intsctp ))
  
  return_list <- list(
    shared_intsctp = shared_intsctp,
    unique_yng_intsctp = unique_yng_intsctp,
    unique_old_intsctp = unique_old_intsctp
  
  )
  
  ctpints_shared_age_list[[i]] <- return_list
  ctpints_shared_age_vec[i] <- length(shared_intsctp)
  
}

names(ctpints_shared_age_list) <- names(ctpints_yng[[2]])
names(ctpints_shared_age_vec) <- names(ctpints_yng[[2]])

which(ctpints_old[[2]][[21]]$interaction == "Rims2&Abca1")
ctpints_yng[[2]][[47]]

grep("Rims2&Abca1", ctpints_old[[2]][[47]]$interaction )

cpi_old$Score[rownames(cpi_old$Score) == "Rims2&Abca1",]
rowMeans(cpi_old$Score[rownames(cpi_old$Score) == "Rims2&Abca1",], na.rm = TRUE)
rowMeans(cpi_old$Score[rownames(cpi_old$Score) == "Rims2&Abca1",], na.rm = TRUE)
rowMeans(cpi_old$Score, na.rm = TRUE)

```

make dataframes for visualisation

```{r}

ctpints_shared_age <- data.frame(
  ct_pair = names(ctpints_yng[[2]])
)

ctpints_shared_age$shared <- vector(length = nrow(ctpints_shared_age))
ctpints_shared_age$old <- vector(length = nrow(ctpints_shared_age))
ctpints_shared_age$young <- vector(length = nrow(ctpints_shared_age))


for(i in unique(ctpints_shared_age$ct_pair)){
  
  ctpints_list <- ctpints_shared_age_list[[i]]
  
  ctpints_shared_age$shared[
    ctpints_shared_age$ct_pair == i] <- length(ctpints_list$shared_intsctp)
  ctpints_shared_age$old[
    ctpints_shared_age$ct_pair == i] <- length(ctpints_list$unique_old_intsctp)
  ctpints_shared_age$young[
    ctpints_shared_age$ct_pair == i] <- length(ctpints_list$unique_yng_intsctp)

}

ctpints_shared_age$old_total <- ctpints_shared_age$old + ctpints_shared_age$shared
ctpints_shared_age$yng_total <- ctpints_shared_age$young + ctpints_shared_age$shared
ctpints_shared_age$order <- ctpints_shared_age$shared

ctpints_shared_age$emitter <- ctpints_yng$overview$emitter[
  match( ctpints_shared_age$ct_pair, ctpints_yng$overview$ct_pairs)]
ctpints_shared_age$receiver <- ctpints_yng$overview$receiver[
  match(ctpints_shared_age$ct_pair, ctpints_yng$overview$ct_pairs)]

ctpints_shared_age$perc_unique_old <- ctpints_shared_age$old / ctpints_shared_age$old_total * 100
ctpints_shared_age$perc_unique_yng <- ctpints_shared_age$young / ctpints_shared_age$yng_total * 100

ctpints_shared_age$perc_shared_old <- ctpints_shared_age$shared / ctpints_shared_age$old_total * 100
ctpints_shared_age$perc_shared_yng <- ctpints_shared_age$shared / ctpints_shared_age$yng_total * 100


ctpints_shared_age$ratio_oy <- ctpints_shared_age$young / ctpints_shared_age$old


ctpints_shared_young <- pivot_longer(ctpints_shared_age,
                                     cols = c(2,4), names_to = "sample")

ctpints_shared_old <- pivot_longer(ctpints_shared_age,
                                     cols = c(2,3), names_to = "sample")

ctpints_shared_young$sample[ctpints_shared_young$sample == "young"] <- "exclusively young"
ctpints_shared_old$sample[ctpints_shared_old$sample == "old"] <- "exclusively old"

ctpints_shared_young$sample <- factor(ctpints_shared_young$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))
ctpints_shared_old$sample <- factor(ctpints_shared_old$sample,
                                      levels = c("exclusively young", "exclusively old", "shared"))

ctpints_shared_age$emitter <- factor(ctpints_shared_age$emitter,
                                     levels = rev(names(col_emi_red)))
ctpints_shared_age$receiver <- factor(ctpints_shared_age$receiver,
                                     levels = rev(names(col_rec_red)))
 
```

visualise all

```{r}

legend_plot <- ggplot(ctpints_shared_young, 
         aes(y = reorder(ct_pair, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))

legend_ctp_age <- get_legend(legend_plot)

plot_ctp_age <- ggarrange(
  
  ncol = 3,

  ggplot(ctpints_shared_young, 
         aes(y = reorder(ct_pair, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_ctpints, 0),
                       breaks = c(-max_ctpints, (-max_ctpints* 0.5), 0),
                       labels = c(max_ctpints, (max_ctpints* 0.5), 0))+
    ylab("")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "young"))+
    theme(legend.position = "none"),
 
  
   ggplot(ctpints_shared_old, 
         aes(y = reorder(ct_pair, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme_classic()+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_ctpints),
                       breaks = c(0, (max_ctpints*0.5), max_ctpints),
                       labels = c(0, (max_ctpints*0.5), max_ctpints))+
    ylab("Cell type pairs")+
    xlab("Number of interactions")+
    ggtitle(paste(species, "old"))+
    theme(legend.position = "none"),
  legend_ctp_age
)

plot_ctp_age

```

percentage of shared interactions of total number of interactions
for each cell type pair.

```{r}

ctpints_shared_age_test <- ctpints_shared_age
ctpints_shared_age_test$emitter <- unfactor(ctpints_shared_age$receiver)

ctpints_shared_age$annotation <- "emitter"
ctpints_shared_age_test$annotation <- "receiver"

ctpints_shared_age_test_rev <- rbind(ctpints_shared_age, ctpints_shared_age_test)

ctpints_shared_age_test_rev$emitter <- factor(ctpints_shared_age_test_rev$emitter,
                                          levels = names(col_cts_red))


ggplot(ctpints_shared_age_test_rev, aes(x = emitter))+
  geom_quasirandom(aes(y = perc_unique_yng), color = col_age[[1]])+
  geom_quasirandom(aes(y = perc_unique_old), color = col_age[[2]])+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Percentage of unique interactions")+
  xlab("Emitters")+
  ylim(limits = c(0, 100))




```

### Interaction overlap within cell type pairs

```{r}

# can easily transform score into binary matrix 
ctp_binary_yng <- cpi_yng$Score
ctp_binary_yng[!is.na(ctp_binary_yng)] <- 1
ctp_binary_yng[is.na(ctp_binary_yng)] <- 0

ctp_binary_old <- cpi_old$Score
ctp_binary_old[!is.na(ctp_binary_old)] <- 1
ctp_binary_old[is.na(ctp_binary_old)] <- 0

ctp_binary_yng$interaction_type <- cpi_yng$Interactions$interaction_type
ctp_binary_old$interaction_type <- cpi_old$Interactions$interaction_type

ctp_binary_yng <- ctp_binary_yng[rowMeans(ctp_binary_yng[,1:121]) > 0,]
ctp_binary_old <- ctp_binary_old[rowMeans(ctp_binary_old[,1:121]) > 0,]

```

#### Total

```{r fig.height = 14, fig.width = 7}

ctp_binary_yng$shared <- vector(length = nrow(ctp_binary_yng))
ctp_binary_yng$shared[rowMeans(ctp_binary_yng[1:121]) == 1] <- TRUE

ctpints_yng_plot <-upset(ctp_binary_yng,
      intersect = colnames(ctp_binary_yng)[1:121],
     sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      height_ratio = 4,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
          # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[2]]))+
          ylab("Interactions/cell type pair")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
        ylim(limits = c(0, max_ctpints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point(size=0.2))+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
           # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0,50))
        )
    )
)


ctp_binary_old$shared <- vector(length = nrow(ctp_binary_old))
ctp_binary_old$shared[rowMeans(ctp_binary_old[1:121]) == 1] <- TRUE

labels <- as.character(c(1:121))

ctpints_old_plot <- upset(ctp_binary_old,
      intersect = colnames(ctp_binary_old)[1:121],
      sort_intersections_by = c("cardinality", "ratio"),
      min_size = 5,
      height_ratio = 4,
      name = NULL,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
            width=0.8),
            position='right')+
         # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[2]]))+
          ylab("Interactions/cell type pair")+
          theme(axis.text.y = element_blank(),
                axis.title.y = element_blank(),
                axis.ticks.y = element_blank(),
                plot.background = element_blank())+
          ylim(c(0, max_ctpints))),
      guides='over',
      matrix=(
         intersection_matrix(
            geom=geom_point(size=0.2))+
           scale_y_discrete(labels = NULL)+
           theme(legend.position = "none")),
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
            # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
            scale_fill_manual("LRI annotation", values = col_itp)+
            theme(axis.text.x = element_blank(),
                  axis.ticks.x = element_blank())+
            ylab("Number of shared interactions")+
              ylim(limits = c(0,50))
      
      )
    )
)

ctpints_yng_plot
ctpints_old_plot

```

#### Cell type pair-wise

```{r fig.width = 6}

ctp_binary_subset_yng <- list()
for(i in names(col_cts_red)){
  
  subset <- ctp_binary_yng[,grep(i, colnames(ctp_binary_yng))]
  subset$interaction_type <- ctp_binary_yng[,122]
  subset <- subset[rowMeans(subset[,1:11]) > 0,]

  ctp_binary_subset_yng[[i]] <- subset
                           
}

ctp_binary_subset_old <- list()
for(i in names(col_cts_red)){
  
  subset <- ctp_binary_old[,grep(i, colnames(ctp_binary_yng)[1:121])]
  subset$interaction_type <- ctp_binary_old[,122]
  subset <- subset[rowMeans(subset[,1:11]) > 0,]

  ctp_binary_subset_old[[i]] <- subset
                           
}

```

```{r, fig.width = 7, fig.height=7}

up_plot_list_yng <- list()
for(i in 1:length(ctp_binary_subset_yng)){
  
  ctp_binary_subset_yng[[i]]$shared <- vector(
    length = nrow(ctp_binary_subset_yng[[i]]))
  ctp_binary_subset_yng[[i]]$shared[
    rowMeans(ctp_binary_subset_yng[[i]][1:11]) == 1] <- TRUE

  up_plot <- upset(ctp_binary_subset_yng[[i]],
      intersect = colnames(ctp_binary_subset_yng[[i]][1:11]),
      sort_intersections_by = c("cardinality", "ratio"),
      min_size = 3,
      height_ratio = 1,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
                width=0.8),
            position='right')+
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[2]]))+
          ylab("Number of interactions per cell type pair")+
          ylim(limits = c(0, max_ctpints))),
      guides='over',
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
                  theme_classic()+
                  scale_fill_manual("LRI annotation", values = col_itp)+
                  theme(axis.text.x = element_blank(),
                        axis.ticks.x = element_blank())+
                  ylab("Number of shared interactions")+
                  ylim(limits = c(0, 160))+
                  ggtitle(paste(species, "young", sep = " "))
      )
    )
  )
  
  up_plot_list_yng[[i]] <- up_plot

}

names(up_plot_list_yng) <- names(col_cts_red)
up_plot_list_yng

```

```{r fig.width = 7, fig.height=7}

up_plot_list_old <- list()
for(i in 1:length(ctp_binary_subset_old)){
  
  ctp_binary_subset_old[[i]]$shared <- vector(
    length = nrow(ctp_binary_subset_old[[i]]))
  ctp_binary_subset_old[[i]]$shared[
    rowMeans(ctp_binary_subset_old[[i]][1:11]) == 1] <- TRUE

  up_plot <- upset(ctp_binary_subset_old[[i]],
      intersect = colnames(ctp_binary_subset_old[[i]][1:11]),
      sort_intersections_by = c("cardinality", "ratio"),
      min_size = 3,
      height_ratio = 1,
      set_sizes=(
        upset_set_size(
          geom=geom_bar(
            aes(fill=shared),
                width=0.8),
            position='right')+
          scale_fill_manual("Shared with all",
                            values = c("TRUE" = "orange", 
                                       "FALSE" = col_age[[2]]))+
          ylab("Number of interactions per cell type pair")+
          ylim(limits = c(0, max_ctpints))),
      guides='over',
      base_annotations = list(
        'Size'=(intersection_size(counts=FALSE,
                                  mapping = aes(fill = interaction_type))+
                  theme_classic()+
                  scale_fill_manual("LRI annotation", values = col_itp)+
                  theme(axis.text.x = element_blank(),
                        axis.ticks.x = element_blank())+
                  ylab("Number of shared interactions")+
                  ylim(limits = c(0, 160))+
                  ggtitle(paste(species, "old", sep = " "))
      )
    )
  )
  
  up_plot_list_old[[i]] <- up_plot

}

names(up_plot_list_old) <- names(col_cts_red)
up_plot_list_old


```

Look at the percentage of shared interactions again, this time for within
cell type pair sharing.

```{r}

ctp_perc_yng <- data.frame(ct_pairs = colnames(cpi_yng$Score))
ctp_perc_yng$emitter <- cpi_yng$Celltypes$emitter
ctp_perc_yng$receiver <- cpi_yng$Celltypes$receiver
ctp_perc_yng$perc_sharedints <- vector(length = nrow(ctp_perc_yng))
ctp_perc_yng$age <- "young"

for(i in 1:length(ctp_binary_subset_yng)){
  
  for(j in colnames(
    ctp_binary_subset_yng[[i]])[1:(ncol(ctp_binary_subset_yng[[i]]) - 2)]){
    
    temp_subset <- ctp_binary_subset_yng[[i]][
      c(which(colnames(ctp_binary_subset_yng[[i]]) == j), 
        which(colnames(ctp_binary_subset_yng[[i]]) == "shared"))]
    
    temp_subset <- temp_subset[which(temp_subset[,1] == 1),]
    
    ctp_perc_yng$perc_sharedints[
      ctp_perc_yng$ct_pairs == j] <- length(which(
        temp_subset$shared == TRUE))/nrow(temp_subset) * 100
  }
}



ctp_perc_old <- data.frame(ct_pairs = colnames(cpi_old$Score))
ctp_perc_old$emitter <- cpi_old$Celltypes$emitter
ctp_perc_old$receiver <- cpi_old$Celltypes$receiver
ctp_perc_old$perc_sharedints <- vector(length = nrow(ctp_perc_old))
ctp_perc_old$age <- "old"

for(i in 1:length(ctp_binary_subset_old)){
  
  for(j in colnames(
    ctp_binary_subset_old[[i]])[1:(ncol(ctp_binary_subset_old[[i]]) - 2)]){
    
    temp_subset <- ctp_binary_subset_old[[i]][
      c(which(colnames(ctp_binary_subset_old[[i]]) == j), 
        which(colnames(ctp_binary_subset_old[[i]]) == "shared"))]
    
    temp_subset <- temp_subset[which(temp_subset[,1] == 1),]
    
    ctp_perc_old$perc_sharedints[
      ctp_perc_old$ct_pairs == j] <- length(which(
        temp_subset$shared == TRUE))/nrow(temp_subset) * 100
  }
}

ctp_perc <- rbind(ctp_perc_yng, ctp_perc_old)
ctp_perc$emitter <- factor(ctp_perc$emitter, 
                           levels = names(col_emi_red))
ctp_perc$receiver <- factor(ctp_perc$receiver, 
                           levels = names(col_rec_red))

```

```{r}

ggplot(ctp_perc, aes(x = emitter, y = perc_sharedints, color = age))+
  geom_quasirandom(size = 0.6)+
  theme_classic()+
  scale_color_manual("Age", values = col_age)+
  ylim(limits = c(0,100))+
  ylab(expression(atop("Nr interactions shared within cell type/",
                       paste("Nr total interactions per cell type pair [%]"))))+
  xlab("Emitter")+
  theme(axis.text.x = element_text(angle = 90))

ggplot(ctp_perc, aes(x = receiver, y = perc_sharedints, color = age))+
  geom_quasirandom(size = 0.6)+
  theme_classic()+
  scale_color_manual("Age", values = col_age)+
  ylim(limits = c(0,100))+
  ylab(expression(atop("Nr interactions shared within cell type/",
                       paste("Nr total interactions per cell type pair [%]"))))+
  xlab("Receiver")+
  theme(axis.text.x = element_text(angle = 90))


```

## Directly compare interesting interactomes

```{r}

min_score <- min(cpi_both$Score[cpi_both$Score != 0])

zero_to_min = rep(viridis(n = 1, option = "D", begin = 0.3, end = 0.3), min_score*100)
min_to_1 = viridis(n = c((min_score*100:100)), option = "D", begin = 0.3, end = 1)


cols = c(zero_to_min, min_to_1)

mypalette <- colorRampPalette(cols)(255)


```

```{r}

cpi_both_perc <- cpi_both
score_df_both_temp <- score_df_both
score_df_both_temp$ct_pair[score_df_both_temp$age == "young"] <- paste0(
  score_df_both_temp$ct_pair[score_df_both_temp$age == "young"], "_yng")
score_df_both_temp$ct_pair[score_df_both_temp$age == "old"] <- paste0(
  score_df_both_temp$ct_pair[score_df_both_temp$age == "old"], "_old")
colnames(cpi_both_perc$Score) <- gsub("mmus_", "", colnames(cpi_both_perc$Score))

for(i in 1:nrow(cpi_both_perc$Score)){
  for(j in 1:ncol(cpi_both_perc$Score)){
    
    if(cpi_both_perc$Score[i, j] != 0){
      cpi_both_perc$Score[i, j] <- score_df_both_temp$score_percentile[
        intersect(which(score_df_both_temp$interaction == rownames(cpi_both_perc$Score)[i]),
                  which(score_df_both_temp$ct_pair == colnames(cpi_both_perc$Score)[j]))]
    }
  }
}


```

```{r}

min_score <- min(cpi_both_perc$Score[cpi_both_perc$Score != 0])

zero_to_min = rep(viridis(n = 1, option = "D", begin = 0.3, end = 0.3), min_score*100)
min_to_1 = viridis(n = c((min_score*100:100)), option = "D", begin = 0.3, end = 1)


cols = c(zero_to_min, min_to_1)

mypalette <- colorRampPalette(cols)(255)

```


```{r}

plot_list_HM_leg <-list()
for(i in names(col_cts_red)){
  
  print(i)
  
  cpi_temp <- cpi_both_perc
  cpi_temp$Score <- cpi_both_perc$Score[,grep(i, colnames(cpi_temp$Score))]
  cpi_temp$Interactions <- cpi_temp$Interactions[-rowMeans(cpi_temp$Score) != 0,]
  cpi_temp$Celltypes <- cpi_temp$Celltypes[grep(i, cpi_temp$Celltypes$ct_pair),]
  cpi_temp$Score <- cpi_temp$Score[-rowMeans(cpi_temp$Score) != 0,]

  if(i %in% names(col_emi_red)){
    partners <- cpi_temp$Celltypes$receiver
    col <- col_rec_red
    col_ct <- col_emi_red[[i]]
    names(col_ct) <- i
  }else if(i %in% names(col_rec_red)){
    partners <- cpi_temp$Celltypes$emitter
    col <- col_emi_red
    col_ct <- col_rec_red[[i]]
    names(col_ct) <- i
  }
  
  anno_col <- data.frame(
    row.names = colnames(cpi_temp$Score),
    Age = cpi_temp$Celltypes$Age,
    "Partner" = partners
    )

  # colours
  heatmap_col <- list(
    Age = col_age,
    "Partner" = col,
    Interactiontype = col_itp
    )

  plot <- as.ggplot(pheatmap(cpi_temp$Score,
         show_colnames = FALSE,
         show_rownames = FALSE,
         cluster_rows =  TRUE,
         treeheight_row = 0,
         treeheight_col = 22,
         annotation_col = anno_col,
         annotation_colors = heatmap_col,
         color =  viridis(n = 100, option = "D", begin = 0, end = 1),
         fontsize = 12
         ))

  plot_list_HM_leg[[i]] <- plot
}

```

```{r}

plot_list_HM <-list()

for(i in names(col_cts_red)){
  
  cpi_temp <- cpi_both_perc
  cpi_temp$Score <- cpi_both_perc$Score[,grep(i, colnames(cpi_temp$Score))]
  cpi_temp$Interactions <- cpi_temp$Interactions[-rowMeans(cpi_temp$Score) != 0,]
  cpi_temp$Celltypes <- cpi_temp$Celltypes[grep(i, cpi_temp$Celltypes$ct_pair),]
  cpi_temp$Score <- cpi_temp$Score[-rowMeans(cpi_temp$Score) != 0,]

  if(i %in% names(col_emi_red)){
    partners <- cpi_temp$Celltypes$receiver
    col <- col_rec_red
    col_ct <- col_emi_red[[i]]
    names(col_ct) <- i
  }else if(i %in% names(col_rec_red)){
    partners <- cpi_temp$Celltypes$emitter
    col <- col_emi_red
    col_ct <- col_rec_red[[i]]
    names(col_ct) <- i
  }
  
  anno_col <- data.frame(
    row.names = colnames(cpi_temp$Score),
    Age = cpi_temp$Celltypes$Age,
    "Partner" = partners
    )

  # colours
  heatmap_col <- list(
    Age = col_age,
    "Partner" = col,
    Interactiontype = col_itp
    )
  
  plot <- as.ggplot(pheatmap(cpi_temp$Score,
         show_colnames = FALSE,
         show_rownames = FALSE,
         cluster_rows =  TRUE,
         treeheight_row = 0,
          treeheight_col = 22,
          annotation_col = anno_col,
         annotation_colors = heatmap_col,
         color = viridis(n = 100, option = "D", begin = 0, end = 1),
         annotation_legend = FALSE,
         fontsize = 12
         ))

  plot_list_HM[[i]] <- plot
}

col_cts_red

```

### Distribution of Scores across cell types

```{r}

median_emi <- score_df_yng %>%
  group_by(emitter) %>%
  summarise(median_val = median(emi_var, na.rm = TRUE))

plot_young_emi_scores <- ggplot(score_df_yng, aes(y = emi_var, 
                                                x = emitter, color = emitter))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_emi, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3)

median_rec <- score_df_yng %>%
  group_by(receiver) %>%
  summarise(median_val = median(rec_var, na.rm = TRUE))

plot_young_rec_scores <- ggplot(score_df_yng, aes(y = rec_var, 
                                                x = receiver, color = receiver))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_rec, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3, stroke = 1)

plot_young_emi_scores
plot_young_rec_scores

```

One example


```{r}

var <- modelGeneVar(cpi_both$Score)
top_hvg30 <- getTopHVGs(var, var.field = "bio", n = 30)

```


```{r}

top_30_pos <- score_df_yng[score_df_yng$interaction %in% top_hvg30,]

fibrchr_pos <- score_df_yng[score_df_yng$emitter == "Fibro/Chondro progs",]

ex_pos_lig <- intersect(top_30_pos, fibrchr_pos)

plot_fibrochondro_percentile <- ggplot(ex_pos_lig, 
       aes(y = interaction, x = score_percentile, color = emitter))+
  geom_boxplot(color = col_cts_all["Fibro/Chondro progs"])


mono_rec <- score_df_yng[score_df_yng$receiver == "Monocyte-primed progs",]

ex_pos_rec <- intersect(top_30_pos, mono_rec)

plot_mono_percentile <- ggplot(ex_pos_rec, 
       aes(y = interaction, x = score_percentile, color = receiver))+
  geom_boxplot(color = col_cts_all["Monocyte-primed progs"])

plot_fibrochondro_percentile
plot_mono_percentile
```

## SCORES

```{r}

median_emi <- score_df_old %>%
  group_by(emitter) %>%
  summarise(median_val = median(emi_var, na.rm = TRUE))

plot_old_emi_scores <- ggplot(score_df_old, aes(y = emi_var,
                                              x = emitter, color = emitter))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_emi, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3)

median_rec <- score_df_old %>%
  group_by(receiver) %>%
  summarise(median_val = median(rec_var, na.rm = TRUE))

plot_old_rec_scores <- ggplot(score_df_old, aes(y = rec_var, x = receiver, color = receiver))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_rec, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3, stroke = 1)

plot_old_emi_scores
plot_old_rec_scores

```


```{r}

score_df_both$age <- factor(score_df_both$age, levels = c("young", "old"))

median_emi_both <- score_df_both %>%
  group_by(age) %>%
  summarise(median_val = median(emi_var, na.rm = TRUE))


plot_both_emi_scores <- ggplot(score_df_both, aes(y = emi_var,
                                                x = age, color = age))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_emi_both, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3, stroke = 1)

median_rec_both <- score_df_both %>%
  group_by(age) %>%
  summarise(median_val = median(rec_var, na.rm = TRUE))


plot_both_rec_scores <- ggplot(score_df_both, aes(y = rec_var,
                                                x = age, color = age))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_rec_both, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3, stroke = 1)

plot_both_emi_scores
plot_both_rec_scores

```

## both at once

```{r}

median_emi_yng <- score_df_yng %>%
  group_by(emitter) %>%
  summarise(median_val = median(emi_var, na.rm = TRUE))

median_emi_yng$age <- "young"

median_emi_old <- score_df_old %>%
  group_by(emitter) %>%
  summarise(median_val = median(emi_var, na.rm = TRUE))

median_emi_old$age <- "old"


median_emi_both <- rbind(median_emi_yng, median_emi_old)
median_emi_both$age <- factor(median_emi_both$age, levels = c("young", "old"))
score_df_both$age <- factor(score_df_both$age, levels = c("young", "old"))

plot_both_emi_scores <- ggplot(score_df_both, aes(y = emi_var,
                                              x = emitter, color = emitter))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_emi_both, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3)+
  facet_grid(cols = vars(age))

plot_both_emi_scores

```

```{r}

median_rec_yng <- score_df_yng %>%
  group_by(receiver) %>%
  summarise(median_val = median(rec_var, na.rm = TRUE))

median_rec_yng$age <- "young"

median_rec_old <- score_df_old %>%
  group_by(receiver) %>%
  summarise(median_val = median(rec_var, na.rm = TRUE))

median_rec_old$age <- "old"


median_rec_both <- rbind(median_rec_yng, median_rec_old)
median_rec_both$age <- factor(median_rec_both$age, levels = c("young", "old"))

plot_both_rec_scores <- ggplot(score_df_both, aes(y = rec_var,
                                              x = receiver, color = receiver))+
  geom_quasirandom(size = 0.3)+
  geom_point(median_rec_both, mapping = aes(y = median_val), color = "black", 
           fill = "white",  shape = 22, size = 3)+
  facet_grid(cols = vars(age))

plot_both_rec_scores

```

