---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script visualises PCA and other reduced dimensions for two cpi objects 
from YOUNG and OLD datasets of THE SAME SPECIES.

Replace the file path to load objects from different species.

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)

#library(scran)
#library(ggpubr)
#library(scater)
#library(data.table)

```

## Load

### Code

```{r load_code, message = FALSE}

setwd("/home/l012t/Interspecies_BM")

source(file = "code/filepath.R")
source(file = "code/colors.R")

```

### Objects

Adjust the file paths to load objects from different species. 
After this, nothing needs to be changed.

```{r}

# merged and pre-processed SCE objects
sce_yng <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE"))
sce_old <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE"))

# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi_pca"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi_pca"))

# merged cpi object

cpi_merged <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))

# corresponging metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

name_yng <- "mmus_yng"
name_old <- "mmus_old"
species <- "mmus"

max_ctpints <- 500
max_ctints <- 1500
max_nrcells <- 10000

```

Merge overview dfs for direct comparion between age groups.
This time, ordering by alphabet BEFORE merging is crucial.

```{r}

ctpints_yng[[1]]$ct_pairs <- paste0(ctpints_yng[[1]]$ct_pairs, "_yng")
ctpints_yng_tm <- ctpints_yng[[1]][order(ctpints_yng[[1]]$ct_pairs),]

ctpints_old[[1]]$ct_pairs <- paste0(ctpints_old[[1]]$ct_pairs, "_old")
ctpints_old_tm <- ctpints_old[[1]][order(ctpints_old[[1]]$ct_pairs),]

ctpints_both <- rbind(ctpints_yng_tm, ctpints_old_tm)

ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))


```

```{r}

ctints_yng[[1]]$celltypes <- paste0(ctints_yng[[1]]$celltypes, "_yng")
ctints_yng_tm <- ctints_yng[[1]][order(ctints_yng[[1]]$celltypes),]

ctints_old[[1]]$celltypes <- paste0(ctints_old[[1]]$celltypes, "_old")
ctints_old_tm <- ctints_old[[1]][order(ctints_old[[1]]$celltypes),]

ctints_both <- rbind(ctints_yng_tm, ctints_old_tm)

ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))

```

```{r}

nrlrs_yng$celltypes <- paste0(nrlrs_yng$celltypes, "_yng")
nrlrs_yng_tm <- nrlrs_yng[order(nrlrs_yng$celltypes),]

nrlrs_old$celltypes <- paste0(nrlrs_old$celltypes, "_old")
nrlrs_old_tm <- nrlrs_old[order(nrlrs_old$celltypes),]

nrlrs_both <- rbind(nrlrs_yng_tm, nrlrs_old_tm)

nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))

```

# Analysis

## Age

### Separate objects

```{r}

age_12_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_yng, "interactome PCA"))

age_13_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_yng, "interactome PCA"))
  
age_23_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_yng, "interactome PCA"))
  
age_12_yng
age_13_yng
age_23_yng

```

```{r}

age_12_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2))+
  geom_point(size = 1.5, color = col_age[2])+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_old, "interactome PCA"))

age_13_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3))+
  geom_point(size = 1.5, color = col_age[2])+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_old, "interactome PCA"))
  
age_23_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3))+
  geom_point(size = 1.5, color = col_age[2])+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  ggtitle(paste(name_old, "interactome PCA"))
  
age_12_old
age_13_old
age_23_old

```

### Merged object

### Visualise Age

```{r}

age_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_merged$Celltypes$Age))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Age", values = col_age)+
  ggtitle(paste(species, "interactome PCA"))

age_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_merged$Celltypes$Age))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Age", values = col_age)+
  ggtitle(paste(species, "interactome PCA"))
  
age_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_merged$Celltypes$Age))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Age", values = col_age)+
  ggtitle(paste(species, "interactome PCA"))
  
age_12
age_13
age_23

```

## Emitters

### Separate objects

```{r}

emi_12_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_yng$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_yng, "interactome PCA"))

emi_13_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_yng$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_yng, "interactome PCA"))
  
emi_23_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_yng$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_yng, "interactome PCA"))
  
emi_12_yng
emi_13_yng
emi_23_yng

```

```{r}

emi_12_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_old$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_old, "interactome PCA"))

emi_13_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_old$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_old, "interactome PCA"))
  
emi_23_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_old$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(name_old, "interactome PCA"))
  
emi_12_old
emi_13_old
emi_23_old

```

### Merged object

```{r}

emi_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_merged$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(species, "interactome PCA"))

emi_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_merged$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(species, "interactome PCA"))
  
emi_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_merged$Celltypes$emitter))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitter", values = col_emi_red)+
  ggtitle(paste(species, "interactome PCA"))
  
emi_12
emi_13
emi_23

```

## Receivers

### Separate objects

```{r}

rec_12_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_yng$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_yng, "interactome PCA"))

rec_13_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_yng$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_yng, "interactome PCA"))
  
rec_23_yng <- ggplot(cpi_yng$PCA[1:(nrow(cpi_yng$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_yng$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_yng$PCA[nrow(cpi_yng$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_yng, "interactome PCA"))
  
rec_12_yng
rec_13_yng
rec_23_yng

```

```{r}

rec_12_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_old$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_old, "interactome PCA"))

rec_13_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_old$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_old, "interactome PCA"))
  
rec_23_old <- ggplot(cpi_old$PCA[1:(nrow(cpi_old$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_old$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_old$PCA[nrow(cpi_old$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(name_old, "interactome PCA"))
  
rec_12_old
rec_13_old
rec_23_old

```

### Merged object

```{r}

rec_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = cpi_merged$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(species, "interactome PCA"))

rec_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = cpi_merged$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(species, "interactome PCA"))
  
rec_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = cpi_merged$Celltypes$receiver))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("receiver", values = col_rec_red)+
  ggtitle(paste(species, "interactome PCA"))
  
rec_12
rec_13
rec_23

```

## Quality Metrics

### Nr of Interactions per cell type pair

```{r}

ints_ctp_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = ctpints_both$nr_ints))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Interactions/cell type pair", 
                         limits = c(0, max_ctpints))+
  ggtitle(paste(species, "interactome PCA"))

ints_ctp_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, 
                     colour = ctpints_both$nr_ints))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Interactions/cell type pair", 
                         limits = c(0, max_ctpints))+
  ggtitle(paste(species, "interactome PCA"))
  
ints_ctp_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, 
                     colour = ctpints_both$nr_ints))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Interactions/cell type pair", 
                         limits = c(0, max_ctpints))+
  ggtitle(paste(species, "interactome PCA"))
  
ints_ctp_12
ints_ctp_13
ints_ctp_23

```

### Nr of cells per emitter cell type

```{r}

nrc_ct_emi_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = ctpints_both$nr_cells_emi))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per emitter",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))

nrc_ct_emi_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = ctpints_both$nr_cells_emi))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per emitter",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))
  
nrc_ct_emi_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = ctpints_both$nr_cells_emi))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per emitter",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))
  
nrc_ct_emi_12
nrc_ct_emi_13
nrc_ct_emi_23

```

### Nr of cells per ligand cell type

```{r}

nrc_ct_rec_12 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, colour = ctpints_both$nr_cells_rec))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per receiver",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))

nrc_ct_rec_13 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.3, colour = ctpints_both$nr_cells_rec))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 1 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per receiver",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))
  
nrc_ct_rec_23 <- ggplot(cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),], 
                 aes(x = Dim.2, y = Dim.3, colour = ctpints_both$nr_cells_rec))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("Component 3 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 3], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("Component 2 [", round(cpi_merged$PCA[nrow(cpi_merged$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_continuous("Nr of cells per receiver",
                         limits = c(0, max_nrcells))+
  ggtitle(paste(species, "interactome PCA"))
  
nrc_ct_rec_12
nrc_ct_rec_13
nrc_ct_rec_23

```

## Distance

```{r}

# build a df to store the distance
dist_df <- ctpints_yng[[1]][,c(1, 3, 4)]
dist_df <- dist_df[order(dist_df$ct_pairs),]
pca_df <- cpi_merged$PCA[1:(nrow(cpi_merged$PCA)-1),]

dist_df$Distance_1 <- abs(
  cpi_merged$PCA$Dim.1[which(cpi_merged$Celltypes$Age == "young")] -
  cpi_merged$PCA$Dim.1[which(cpi_merged$Celltypes$Age == "old")])
dist_df$Distance_2 <- abs(
  cpi_merged$PCA$Dim.2[which(cpi_merged$Celltypes$Age == "young")] -
  cpi_merged$PCA$Dim.2[which(cpi_merged$Celltypes$Age == "old")])
dist_df$Distance_3 <- abs(
  cpi_merged$PCA$Dim.3[which(cpi_merged$Celltypes$Age == "young")] -
  cpi_merged$PCA$Dim.3[which(cpi_merged$Celltypes$Age == "old")])

```

```{r}

ggplot(dist_df, 
       aes(x = emitter, 
           y = Distance_1,
           fill = emitter))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC1 (yng)) - Coord(PC1 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Emitter", values = col_emi_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
 
ggplot(dist_df, 
       aes(x = receiver, 
           y = Distance_1,
           fill = receiver))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC1 (yng)) - Coord(PC1 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Receiver", values = col_rec_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
         
```

```{r}

ggplot(dist_df, 
       aes(x = emitter, 
           y = Distance_2,
           fill = emitter))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC2 (yng)) - Coord(PC2 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Emitter", values = col_emi_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
 
ggplot(dist_df, 
       aes(x = receiver, 
           y = Distance_2,
           fill = receiver))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC2 (yng)) - Coord(PC2 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Receiver", values = col_rec_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
         
```

```{r}

ggplot(dist_df, 
       aes(x = emitter, 
           y = Distance_3,
           fill = emitter))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC3 (yng)) - Coord(PC3 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Emitter", values = col_emi_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
 
ggplot(dist_df, 
       aes(x = receiver, 
           y = Distance_3,
           fill = receiver))+
  geom_boxplot()+
  theme_classic()+
  ylab("Abs(Coord(PC3 (yng)) - Coord(PC3 (old))")+
  xlab("Emitter")+
  scale_fill_manual("Receiver", values = col_rec_red)+
  theme(axis.text.x = element_text(angle = 90))+
  ylim(limits = c(0,50))+
  ggtitle(paste(species, "interactome PCA"))
         
```