---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script visualises important metrics for two cpi objects from YOUNG and OLD
datasets of THE SAME SPECIES.

Replace the file path to load objects from different species.

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)

#library(scran)
#library(ggpubr)
#library(scater)
#library(data.table)

```

## Load

### Code

```{r load_code, message = FALSE}

setwd("/home/l012t/Interspecies_BM")

source(file = "code/filepath.R")
source(file = "code/colors.R")

```

### Objects

Adjust the file paths to load objects from different species. 
After this, nothing needs to be changed.

```{r}

# merged and pre-processed SCE objects
sce_yng <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_ds_ctrm"))
sce_old <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_ds_ctrm"))

# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

name_yng <- "mmus_yng"
name_old <- "mmus_old"
species <- "mmus"

max_ctpints <- 500
max_ctints <- 1500
max_nrcells <- 10000

```

Merge overview dfs for direct comparion between age groups.

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctints_both <- rbind(ctints_yng[[1]], ctints_old[[1]])
ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))
ctints_both$celltypes <- factor(ctints_both$celltypes, 
                                levels = names(col_cts_red))
```

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))
```

# QC Analysis

## Cell type pair level

### Nr of interactions

Visualise distribution of nr of interactions per cell type pair.

```{r}

hist_ctpints_emi_yng <- ggplot(ctpints_yng[[1]], 
                               aes(x = reorder(ct_pairs, -nr_ints), 
                                   y = nr_ints, 
                                   fill = reorder(emitter, -nr_ints)))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0, max_ctpints))
  
hist_ctpints_rec_yng <- ggplot(ctpints_yng[[1]], 
                               aes(x = reorder(ct_pairs, -nr_ints), 
                                   y = nr_ints, 
                                   fill = reorder(receiver, -nr_ints)))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0, max_ctpints))

hist_ctpints_emi_yng
hist_ctpints_rec_yng

```

```{r}

hist_ctpints_emi_old <- ggplot(ctpints_old[[1]], 
                               aes(x = reorder(ct_pairs, -nr_ints), 
                                   y = nr_ints, 
                                   fill = reorder(emitter, -nr_ints)))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0, max_ctpints))
  
hist_ctpints_rec_old <- ggplot(ctpints_old[[1]], 
                               aes(x = reorder(ct_pairs, -nr_ints), 
                                   y = nr_ints, 
                                   fill = reorder(receiver, -nr_ints)))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0, max_ctpints))

hist_ctpints_emi_old
hist_ctpints_rec_old

```

Visualise per age group.

```{r}

bp_ctpints_age <- ggplot(ctpints_both, aes(x = age, y = nr_ints, fill = age))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of interactions per cell type pair")+
  xlab("Age")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_age_emi <- ggplot(ctpints_both, 
                             aes(x = emitter, y = nr_ints, fill = age))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of interactions per cell type pair")+
  xlab("Emitter partner")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_age_rec <- ggplot(ctpints_both, 
                             aes(x = receiver, y = nr_ints, fill = age))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of interactions per cell type pair")+
  xlab("Emitter partner")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_age
bp_ctpints_age_emi
bp_ctpints_age_rec

```

Visualise by partner cell types.

```{r}

bp_ctpints_emi <- ggplot(ctpints_both, 
                         aes(x = emitter, y = nr_ints, fill = emitter))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Emitter partner")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_emi_age <- ggplot(ctpints_both, 
                             aes(x = age, y = nr_ints, fill = emitter))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Age")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_rec <- ggplot(ctpints_both, 
                         aes(x = receiver, y = nr_ints, fill = receiver))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Receiver partner")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_rec_age <- ggplot(ctpints_both, 
                             aes(x = age, y = nr_ints, fill = receiver))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of interactions per cell type pair")+
  xlab("Age")+
  theme(axis.text.x = element_text(angle = 90))+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctpints))

bp_ctpints_emi
bp_ctpints_emi_age
bp_ctpints_rec
bp_ctpints_rec_age

```

### Nr of cells

Generically look at nr of cells per cell type first.
Histograms.

```{r}

hist_cts_yng <- ggplot(ctints_yng$overview, 
                       aes(x = reorder(celltypes, -nr_cells), y = nr_cells,
                           fill = annotation))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Cell type")+
  ylab("Number of cells per cell type")+
  scale_fill_manual("Annotation", values = col_ann)+
  scale_y_continuous(limits = c(0, max_nrcells))+
  ggtitle(paste(name_yng))

hist_cts_old <- ggplot(ctints_old$overview, 
                       aes(x = reorder(celltypes, -nr_cells), y = nr_cells,
                           fill = annotation))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Cell type")+
  ylab("Number of cells per cell type")+
  scale_fill_manual("Annotation", values = col_ann)+
  scale_y_continuous(limits = c(0, max_nrcells))+
  ggtitle(paste(name_old))

hist_cts_yng
hist_cts_old

```

Boxplots.

```{r}

bp_ct_yng_anno <- ggplot(ctints_yng$overview, 
                            aes(x = annotation, 
                                y = nr_cells, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of cells")+
  xlab("Annotation")+
  ggtitle(paste(name_yng))+
  ylim(limits = c(0, max_nrcells))

bp_ct_old_anno <- ggplot(ctints_old$overview, 
                            aes(x = annotation, 
                                y = nr_cells, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of cells")+
  xlab("Annotation")+
  ggtitle(paste(name_old))+
  ylim(limits = c(0, max_nrcells))

bp_ct_age <- ggplot(ctints_both, 
                    aes(x = age, 
                        y = nr_cells, fill = age))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of cells")+
  xlab("Age")+
  ggtitle(paste(name_old))+
  ylim(limits = c(0, max_nrcells))

bp_ct_yng_anno
bp_ct_old_anno
bp_ct_age

```


```{r}

pt_ctpints_nrc_yng <- ggplot(ctpints_yng$overview)+
  geom_point(aes(x = nr_cells_emi, y = nr_ints), 
             size = 1.2, color = col_ann['emitter'])+
  geom_point(aes(x = nr_cells_rec, y = nr_ints), 
             size = 1.2, color = col_ann['receiver'])+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of interactions per cell type pair")+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, max_ctpints))+
  ggtitle(paste(name_yng, "interactome"))

pt_ctpints_nrc_old <- ggplot(ctpints_old$overview)+
  geom_point(aes(x = nr_cells_emi, y = nr_ints), 
             size = 1.2, color = col_ann['emitter'])+
  geom_point(aes(x = nr_cells_rec, y = nr_ints), 
             size = 1.2, color = col_ann['receiver'])+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of interactions per cell type pair")+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, max_ctpints))+
  ggtitle(paste(name_old, "interactome"))

pt_ctpints_nrc_yng
pt_ctpints_nrc_old

```

```{r}

hist_nrc_ctp_emi_yng <- ggplot(ctpints_yng[[1]], 
                               aes(x = reorder(ct_pairs, -(nr_cells_emi+nr_cells_rec)),
                                   y = nr_cells_emi+nr_cells_rec, 
                                   fill = emitter))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of cells per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0, (max_nrcells*2)))

hist_nrc_ctp_rec_yng <- ggplot(ctpints_yng[[1]], 
                               aes(x = reorder(ct_pairs, -(nr_cells_emi+nr_cells_rec)),
                                   y = nr_cells_emi+nr_cells_rec, 
                                   fill = receiver))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of cells per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0, (max_nrcells*2)))

hist_nrc_ctp_emi_old <- ggplot(ctpints_old[[1]], 
                               aes(x = reorder(ct_pairs, -(nr_cells_emi+nr_cells_rec)),
                                   y = nr_cells_emi+nr_cells_rec, 
                                   fill = emitter))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Emitter partner", values = col_emi_red)+
  ylab("Number of cells per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0, (max_nrcells*2)))

hist_nrc_ctp_rec_old <- ggplot(ctpints_old[[1]], 
                               aes(x = reorder(ct_pairs, -(nr_cells_emi+nr_cells_rec)),
                                   y = nr_cells_emi+nr_cells_rec, 
                                   fill = receiver))+
  geom_col()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_manual("Receiver partner", values = col_rec_red)+
  ylab("Number of cells per cell type pair")+
  xlab("Cell type pairs")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0, (max_nrcells*2)))

hist_nrc_ctp_emi_yng
hist_nrc_ctp_rec_yng
hist_nrc_ctp_emi_old
hist_nrc_ctp_rec_old

```

### Scores

```{r}

ints_score_yng <- cpi_yng$Score
ints_score_old <- cpi_old$Score

ints_score_yng <- ints_score_yng %>%
  pivot_longer(cols = c(1:ncol(ints_score_yng)), 
               names_to = "ct_pair", values_to = "score")
ints_score_old <- ints_score_old %>%
  pivot_longer(cols = c(1:ncol(ints_score_old)), 
               names_to = "ct_pair", values_to = "score")

ints_score_yng <- ints_score_yng[which(!is.na(ints_score_yng$score)),]
ints_score_yng$nr_ints <- ctpints_yng[[1]]$nr_ints[match(
    ints_score_yng$ct_pair, ctpints_yng[[1]]$ct_pairs)]

ints_score_old <- ints_score_old[which(!is.na(ints_score_old$score)),]
ints_score_old$nr_ints <- ctpints_old[[1]]$nr_ints[match(
    ints_score_old$ct_pair, ctpints_old[[1]]$ct_pairs)]

bp_ctpints_sc_yng <- ggplot(ints_score_yng, 
                            aes(x = reorder(ct_pair, nr_ints), 
                                y = score, fill = nr_ints))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_continuous("Nr ints/ctp",  limits = c(0, max_ctpints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0,1))

bp_ctpints_sc_old <- ggplot(ints_score_old, 
                            aes(x = reorder(ct_pair, nr_ints), 
                                y = score, fill = nr_ints))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  scale_fill_continuous("Nr ints/ctp",  limits = c(0, max_ctpints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0,1))

bp_ctpints_sc_yng
bp_ctpints_sc_old

```

### Percentage of used interactions

Calculate how many of the possible interactions of cts are used in the 
specific ctps.
Requires info from both ctpints and ctints.

```{r}

# young
ints_frac_yng <- ctpints_yng$overview

ints_frac_yng$nr_ints_emitter <- vector(
  length = nrow(ints_frac_yng))
ints_frac_yng$nr_ints_receiver <- vector(
  length = nrow(ints_frac_yng))

ints_frac_yng$nr_ints_emitter <- ctints_yng$overview$nr_ints[
  match(ints_frac_yng$emitter, ctints_yng$overview$celltypes)]
ints_frac_yng$nr_ints_receiver <- ctints_yng$overview$nr_ints[
  match(ints_frac_yng$receiver, ctints_yng$overview$celltypes)]

ints_frac_yng$perc_ints_emi <- ints_frac_yng$nr_ints/ints_frac_yng$nr_ints_emitter
ints_frac_yng$perc_ints_rec <- ints_frac_yng$nr_ints/ints_frac_yng$nr_ints_receiver

# old
ints_frac_old <- ctpints_old$overview

ints_frac_old$nr_ints_emitter <- vector(
  length = nrow(ints_frac_old))
ints_frac_old$nr_ints_receiver <- vector(
  length = nrow(ints_frac_old))

ints_frac_old$nr_ints_emitter <- ctints_old$overview$nr_ints[
  match(ints_frac_old$emitter, ctints_old$overview$celltypes)]
ints_frac_old$nr_ints_receiver <- ctints_old$overview$nr_ints[
  match(ints_frac_old$receiver, ctints_old$overview$celltypes)]

ints_frac_old$perc_ints_emi <- ints_frac_old$nr_ints/ints_frac_old$nr_ints_emitter
ints_frac_old$perc_ints_rec <- ints_frac_old$nr_ints/ints_frac_old$nr_ints_receiver

```

Barplots.

```{r}

barp_intfrac_yng_emi <- ggplot(ints_frac_yng, 
                          aes(x = emitter, y = perc_ints_emi, fill = receiver))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Receivers", values = col_rec_red)+
  ylab("nr ints per ctp/nr possible ints per emitter")+
  xlab("Emitters")+
  ggtitle(paste("Interactions used per ctp [%]", name_yng, "interactome"))+
  ylim(limits = c(0, 1))

barp_intfrac_yng_rec <- ggplot(ints_frac_yng, 
                          aes(x = receiver, y = perc_ints_rec, fill = emitter))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylab("nr ints per ctp/nr possible ints per receiver")+
  xlab("Receivers")+
  ggtitle(paste("Interactions used per ctp [%]", name_yng, "interactome"))+
  ylim(limits = c(0, 1))

barp_intfrac_old_emi <- ggplot(ints_frac_old, 
                          aes(x = emitter, y = perc_ints_emi, fill = receiver))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Receivers", values = col_rec_red)+
  ylab("nr ints per ctp/nr possible ints per emitter")+
  xlab("Emitters")+
  ggtitle(paste("Interactions used per ctp [%]", name_old, "interactome"))+
  ylim(limits = c(0, 1))

barp_intfrac_old_rec <- ggplot(ints_frac_old, 
                          aes(x = receiver, y = perc_ints_rec, fill = emitter))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylab("nr ints per ctp/nr possible ints per receiver")+
  xlab("Receivers")+
  ggtitle(paste("Interactions used per ctp [%]", name_old, "interactome"))+
  ylim(limits = c(0, 1))

barp_intfrac_yng_emi
barp_intfrac_yng_rec
barp_intfrac_old_emi
barp_intfrac_old_rec  

```

Boxplots.

```{r}

bp_intfrac_yng_emi <- ggplot(ints_frac_yng, 
                             aes(x = emitter, 
                                 y = perc_ints_emi, 
                                 fill = emitter))+
  geom_boxplot(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylab("nr ints per ctp/nr possible ints per emitter")+
  xlab("Emitters")+
  ggtitle(paste("Interactions used per ctp [%]", name_yng, "interactome"))+
  ylim(limits = c(0, 1))

bp_intfrac_yng_rec <- ggplot(ints_frac_yng, 
                             aes(x = receiver, 
                                 y = perc_ints_emi, 
                                 fill = receiver))+
  geom_boxplot(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Receivers", values = col_rec_red)+
  ylab("nr ints per ctp/nr possible ints per receiver")+
  xlab("Receivers")+
  ggtitle(paste("Interactions used per ctp [%]", name_yng, "interactome"))+
  ylim(limits = c(0, 1))

bp_intfrac_old_emi <- ggplot(ints_frac_old, 
                             aes(x = emitter, 
                                 y = perc_ints_emi, 
                                 fill = emitter))+
  geom_boxplot(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylab("nr ints per ctp/nr possible ints per emitter")+
  xlab("Emitters")+
  ggtitle(paste("Interactions used per ctp [%]", name_old, "interactome"))+
  ylim(limits = c(0, 1))

bp_intfrac_old_rec <- ggplot(ints_frac_old, 
                             aes(x = receiver, 
                                 y = perc_ints_emi, 
                                 fill = receiver))+
  geom_boxplot(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Receivers", values = col_rec_red)+
  ylab("nr ints per ctp/nr possible ints per receiver")+
  xlab("Receivers")+
  ggtitle(paste("Interactions used per ctp [%]", name_old, "interactome"))+
  ylim(limits = c(0, 1))

bp_intfrac_yng_emi
bp_intfrac_yng_rec
bp_intfrac_old_emi
bp_intfrac_old_rec

```

## Cell type level

### Nr of interactions

Visualise per age group.
Histograms.

```{r}

hist_ctints_age <- ggplot(ctints_both, 
                          aes(x = reorder(celltypes, - nr_ints), 
                              y = nr_ints, fill = age))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ylim(limits = c(0,max_ctints))+
  ggtitle(paste(species, "interactome"))

hist_ctints_anno <- ggplot(ctints_both, 
                          aes(x = celltypes, 
                              y = nr_ints, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ylim(limits = c(0,max_ctints))+
  ggtitle(paste(species, "interactome"))

hist_ctints_anno_age <- ggplot(ctints_both, 
                          aes(x = celltypes, 
                              y = nr_ints, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ylim(limits = c(0,max_ctints))+
  ggtitle(paste(species, "interactome"))+
  facet_grid(cols = vars(age))

hist_ctints_yng_anno <- ggplot(ctints_yng[[1]], 
                          aes(x = reorder(celltypes, - nr_ints), 
                              y = nr_ints, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ylim(limits = c(0,max_ctints))+
  ggtitle(paste(name_yng, "interactome"))

hist_ctints_old_anno <- ggplot(ctints_old[[1]], 
                          aes(x = reorder(celltypes, - nr_ints), 
                              y = nr_ints, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ylim(limits = c(0,max_ctints))+
  ggtitle(paste(name_old, "interactome"))


hist_ctints_age
hist_ctints_anno
hist_ctints_anno_age
hist_ctints_yng_anno
hist_ctints_old_anno

```

Boxplots.

```{r}

bp_ctints_age <- ggplot(ctints_both, aes(x = age, y = nr_ints, fill = age))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))

bp_ctints_anno <- ggplot(ctints_both, 
                         aes(x = annotation, y = nr_ints, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of possible interactions per cell type")+
  xlab("Annotation")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))

bp_ctints_age_anno <- ggplot(ctints_both, 
                             aes(x = age, y = nr_ints, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of possible interactions per cell type")+
  xlab("Age")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))

bp_ctints_anno_age <- ggplot(ctints_both, 
                             aes(x = annotation, y = nr_ints, fill = age))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of possible interactions per cell type")+
  xlab("Annotation")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))


bp_ctints_age
bp_ctints_anno
bp_ctints_age_anno
bp_ctints_anno_age

```

Visualise per cell type.

```{r}

barp_ctints_ct <- ggplot(ctints_both, 
                         aes(x = celltypes, y = nr_ints, 
                              fill = celltypes))+
  geom_col()+
  theme_classic()+
  scale_fill_manual("Cell types", values = col_cts_red)+
  ylab("Number of possible interactions per cell type")+
  xlab("Cell types")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")

barp_ctints_ct_age <- ggplot(ctints_both, 
                         aes(x = celltypes, y = nr_ints, 
                              fill = celltypes))+
  geom_col()+
  theme_classic()+
  scale_fill_manual("Cell types", values = col_cts_red)+
  ylab("Number of possible interactions per cell type")+
  xlab("Cell types")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, max_ctints))+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  facet_grid(cols = vars(age))

barp_ctints_ct
barp_ctints_ct_age 

```

## Nr of Ligands/Receptors

```{r}

hist_nrlrs_age <- ggplot(nrlrs_both, 
                          aes(x = reorder(celltypes, - nr_lrs), 
                              y = nr_lrs, fill = age))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ylim(limits = c(0,800))+
  ggtitle(paste(species, "interactome"))

hist_nrlrs_anno <- ggplot(nrlrs_both, 
                          aes(x = celltypes, 
                              y = nr_lrs, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ylim(limits = c(0,800))+
  ggtitle(paste(species, "interactome"))

hist_nrlrs_anno_age <- ggplot(nrlrs_both, 
                          aes(x = celltypes, 
                              y = nr_lrs, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ylim(limits = c(0,800))+
  ggtitle(paste(species, "interactome"))+
  facet_grid(cols = vars(age))

hist_nrlrs_yng_anno <- ggplot(nrlrs_yng, 
                          aes(x = reorder(celltypes, - nr_lrs), 
                              y = nr_lrs, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ylim(limits = c(0,800))+
  ggtitle(paste(name_yng, "interactome"))

hist_nrlrs_old_anno <- ggplot(nrlrs_old, 
                          aes(x = reorder(celltypes, - nr_lrs), 
                              y = nr_lrs, fill = annotation))+
  geom_col(position = "dodge")+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ylim(limits = c(0,800))+
  ggtitle(paste(name_old, "interactome"))


hist_nrlrs_age
hist_nrlrs_anno
hist_nrlrs_anno_age
hist_nrlrs_yng_anno
hist_nrlrs_old_anno

```

Boxplots.

```{r}

bp_nrlrs_age <- ggplot(nrlrs_both, aes(x = age, y = nr_lrs, fill = age))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, 800))

bp_nrlrs_anno <- ggplot(nrlrs_both, 
                         aes(x = annotation, y = nr_lrs, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Annotation")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, 800))

bp_nrlrs_age_anno <- ggplot(nrlrs_both, 
                             aes(x = age, y = nr_lrs, fill = annotation))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Annotation", values = col_ann)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Age")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, 800))

bp_nrlrs_anno_age <- ggplot(nrlrs_both, 
                             aes(x = annotation, y = nr_lrs, fill = age))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_manual("Age", values = col_age)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Annotation")+
  ggtitle(paste(species, "interactome"))+
  ylim(limits = c(0, 800))


bp_nrlrs_age
bp_nrlrs_anno
bp_nrlrs_age_anno
bp_nrlrs_anno_age

```

Visualise per cell type.

```{r}

barp_nrlrs_ct <- ggplot(nrlrs_both, 
                         aes(x = celltypes, y = nr_lrs, 
                              fill = celltypes))+
  geom_col()+
  theme_classic()+
  scale_fill_manual("Cell types", values = col_cts_red)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Cell types")+
  ggtitle(paste(species, "interactome"))+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylim(limits = c(0, 800))

barp_nrlrs_ct_age <- ggplot(nrlrs_both, 
                         aes(x = celltypes, y = nr_lrs, 
                              fill = celltypes))+
  geom_col()+
  theme_classic()+
  scale_fill_manual("Cell types", values = col_cts_red)+
  ylab("Number of ligands/receptors per cell type")+
  xlab("Cell types")+
  ggtitle(paste(species, "interactome"))+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  facet_grid(cols = vars(age))+
  ylim(limits = c(0, 800))

barp_nrlrs_ct
barp_nrlrs_ct_age 

```

## Nr of cells

For interactions by cell type.

```{r}

pt_ctints_nrc_yng <- ggplot(ctints_yng$overview,
                             aes(x = nr_cells, y = nr_ints, color = annotation))+
  geom_point(size = 2)+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of possible interactions per cell type")+
  scale_color_manual("Annotation", values = col_ann)+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, max_ctints))+
  ggtitle(paste(name_yng, "interactome"))

pt_ctints_nrc_old <- ggplot(ctints_old$overview,
                             aes(x = nr_cells, y = nr_ints, color = annotation))+
  geom_point(size = 2)+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of possible interactions per cell type")+
  scale_color_manual("Annotation", values = col_ann)+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, max_ctints))+
  ggtitle(paste(name_old, "interactome"))

pt_ctints_nrc_yng
pt_ctints_nrc_old

```

For nr of ligands/receptors by cell type.

```{r}

pt_nrlrs_nrc_yng <- ggplot(nrlrs_yng,
                             aes(x = nr_cells, y = nr_lrs, color = annotation))+
  geom_point(size = 2)+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of ligands/receptors per cell type")+
  scale_color_manual("Annotation", values = col_ann)+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, 800))+
  ggtitle(paste(name_yng, "interactome"))

pt_nrlrs_nrc_old <- ggplot(nrlrs_old,
                             aes(x = nr_cells, y = nr_lrs, color = annotation))+
  geom_point(size = 2)+
  theme_classic()+
  xlab("Number of cells per cell type")+
  ylab("Number of per cell type pair")+
  scale_color_manual("Annotation", values = col_ann)+
  scale_x_continuous(limits = c(0, max_nrcells))+
  scale_y_continuous(limits = c(0, 800))+
  ggtitle(paste(name_old, "interactome"))

pt_nrlrs_nrc_yng
pt_nrlrs_nrc_old

```

## Score

### ctints

Reuse the ints_frac dataframes for convenience.

```{r}

pos_match_yng <- match(ints_score_yng$ct_pair, ints_frac_yng$ct_pairs)
pos_match_old <- match(ints_score_old$ct_pair, ints_frac_old$ct_pairs)

ints_score_yng$emitter <- ints_frac_yng$emitter[pos_match_yng]
ints_score_yng$receiver <- ints_frac_yng$receiver[pos_match_yng]
ints_score_yng$nr_ints_emitter <- ints_frac_yng$nr_ints_emitter[pos_match_yng]
ints_score_yng$nr_ints_receiver <- ints_frac_yng$nr_ints_receiver[pos_match_yng]

ints_score_yng$emitter <- factor(ints_score_yng$emitter, 
                                 levels = names(col_emi_red))
ints_score_yng$receiver <- factor(ints_score_yng$receiver, 
                                 levels = names(col_rec_red))

ints_score_old$emitter <- ints_frac_old$emitter[pos_match_old]
ints_score_old$receiver <- ints_frac_old$receiver[pos_match_old]
ints_score_old$nr_ints_emitter <- ints_frac_old$nr_ints_emitter[pos_match_old]
ints_score_old$nr_ints_receiver <-ints_frac_old$nr_ints_receiver[pos_match_old]

ints_score_old$emitter <- factor(ints_score_old$emitter, 
                                 levels = names(col_emi_red))
ints_score_old$receiver <- factor(ints_score_old$receiver, 
                                 levels = names(col_rec_red))
```

```{r}

ints_score_yng_emi <- ggplot(ints_score_yng, 
                             aes(x = emitter,
                                 y = score, fill = nr_ints_emitter))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr possible ints/ct", limits = c(0, max_ctints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0,1))

ints_score_yng_rec <- ggplot(ints_score_yng, 
                             aes(x = receiver, 
                                 y = score, fill = nr_ints_receiver))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr possible ints/ct", limits = c(0, max_ctints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0,1))

ints_score_old_emi <- ggplot(ints_score_old, 
                             aes(x = emitter,
                                 y = score, fill = nr_ints_emitter))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr possible ints/ct", limits = c(0, max_ctints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0,1))

ints_score_old_rec <- ggplot(ints_score_old, 
                             aes(x = receiver, 
                                 y = score, fill = nr_ints_receiver))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr possible ints/ct", limits = c(0, max_ctints))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0,1))


ints_score_yng_emi
ints_score_yng_rec
ints_score_old_emi
ints_score_old_rec

```

### nr of cells

```{r}

# young 
ints_score_yng$nr_cells_emitter <- ctints_yng$overview$nr_cells[match(
  ints_score_yng$emitter, ctints_yng$overview$celltypes)]
ints_score_yng$nr_cells_receiver <- ctints_yng$overview$nr_cells[match(
  ints_score_yng$receiver, ctints_yng$overview$celltypes)]

# old 
ints_score_old$nr_cells_emitter <- ctints_old$overview$nr_cells[match(
  ints_score_old$emitter, ctints_old$overview$celltypes)]
ints_score_old$nr_cells_receiver <- ctints_old$overview$nr_cells[match(
  ints_score_old$receiver, ctints_old$overview$celltypes)]

```

```{r}

nrc_score_yng_emi <- ggplot(ints_score_yng, 
                             aes(x = reorder(emitter, nr_cells_emitter),
                                 y = score, fill = nr_cells_emitter))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr of cells", limits = c(0, max_nrcells))+
  ylab("LRI Score")+
  xlab("Cell type")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0,1))

nrc_score_yng_rec <- ggplot(ints_score_yng, 
                             aes(x = reorder(receiver, nr_cells_receiver),
                                 y = score, fill = nr_cells_receiver))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr of cells", limits = c(0, max_nrcells))+
  ylab("LRI Score")+
  xlab("Cell type")+
  ggtitle(paste(name_yng, "interactome"))+
  ylim(limits = c(0,1))

nrc_score_old_emi <- ggplot(ints_score_old, 
                             aes(x = reorder(emitter, nr_cells_emitter),
                                 y = score, fill = nr_cells_emitter))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr of cells", limits = c(0, max_nrcells))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0,1))

nrc_score_old_rec <- ggplot(ints_score_old, 
                             aes(x = reorder(receiver, nr_cells_receiver),
                                 y = score, fill = nr_cells_receiver))+
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_continuous("Nr of cells", limits = c(0, max_nrcells))+
  ylab("LRI Score")+
  xlab("Cell type pair")+
  ggtitle(paste(name_old, "interactome"))+
  ylim(limits = c(0,1))

nrc_score_yng_emi
nrc_score_yng_rec
nrc_score_old_emi
nrc_score_old_rec

```

