---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"Global impact of ageing".

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(eulerr)
library(gridExtra)
library(cowplot)
library(scater)
library(ggbeeswarm)
library(ggpubr)

```

## Load

### Code

```{r load_code, message = FALSE}

source(file = "../../code/filepath.R")
source(file = "../../code/colors.R")

```

### Objects

```{r}

cpi_merged_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))

species <- "mmus"

```

# Plots

## A

PCA dimensions 1 and 2

```{r}

plot_a <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$Age))+
  geom_point(size = 1.5)

plot_a

```

## B

PCA of emitters

```{r}

plot_b <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$emitter))+
  geom_point(size = 1.5)

plot_b

```

# C 

PCA of receivers

```{r}

plot_c <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$receiver))+
  geom_point(size = 1.5)

plot_c

```

## D

Schematic of euclidian distances

## E

Direct EDs

Calculate euclidian distances first

```{r}

#scaling (and rename for convenience)
cpi_both_scaled <- scale(t(cpi_merged_pca$Score))

#euclidian distances
cpi_both_dist <- dist(cpi_both_scaled, method = 'euclidean')

# make a df for convenience
cpi_both_dist_mat <- as.matrix(cpi_both_dist)
cpi_both_dist_df <- as.data.frame(cpi_both_dist_mat)

```

Get the direct euclidian distances between ctps from young and ctps from old.

```{r}

dist_oy <- cpi_both_dist_df[grep("yng", rownames(cpi_both_dist_df)), 
                         grep("old", colnames(cpi_both_dist_df))]

dist_oy <- rownames_to_column(dist_oy, var = "ct_pair_yng")

dist_oy_direct <- dist_oy %>%
  pivot_longer(cols = c(2:ncol(dist_oy)),
               names_to = "ct_pair_old",
               names_ptypes = list("ct_pair_old" = character()),
               values_to = "distance",
               values_ptypes = list("euclidian_distance" = numeric())
  )

dist_oy_direct$ct_pair_yng <- gsub(paste0("_", species, "_", "yng"), "", dist_oy_direct$ct_pair_yng)
dist_oy_direct$ct_pair_old <- gsub(paste0("_", species, "_", "old"), "", dist_oy_direct$ct_pair_old)


dist_oy_direct$emitter_old <- gsub("[&][[:print:]]+", "", dist_oy_direct$ct_pair_old)
dist_oy_direct$receiver_old <- gsub("[[:print:]]+[&]", "", dist_oy_direct$ct_pair_old)

dist_oy_direct$emitter_yng <- gsub("[&][[:print:]]+", "", dist_oy_direct$ct_pair_yng)
dist_oy_direct$receiver_yng <- gsub("[[:print:]]+[&]", "", dist_oy_direct$ct_pair_yng)

dist_oy_direct$emitter_old <- factor(dist_oy_direct$emitter_old,
                                levels = names(col_emi_red))
dist_oy_direct$emitter_yng <- factor(dist_oy_direct$emitter_yng,
                                levels = names(col_emi_red))

dist_oy_direct$receiver_old <- factor(dist_oy_direct$receiver_old,
                                levels = names(col_rec_red))
dist_oy_direct$receiver_yng <- factor(dist_oy_direct$receiver_yng,
                                levels = names(col_rec_red))

dist_oy_direct_direct <- dist_oy_direct[dist_oy_direct$ct_pair_yng == dist_oy_direct$ct_pair_old,]

```

```{r}

plot_e1 <- ggplot(dist_oy_direct_direct, 
                  aes(x = emitter_old, y = distance, color = emitter_old))+
  geom_quasirandom()
  

plot_e2 <- ggplot(dist_oy_direct_direct,
                  aes(x = receiver_old, y = distance, color = receiver_old))+
  geom_quasirandom()

plot_e1
plot_e2

```

## F

Schematic of variability change.

## G

Euclidian distances within age groups.

Get all distances within young, then all distances within old. 
Then substract complete yng from complete old.

```{r}

cpi_both_dist_df_old <- cpi_both_dist_df[
  grep("old", colnames(cpi_both_dist_df)),
  grep("old", rownames(cpi_both_dist_df))]

cpi_both_dist_df_old <- cpi_both_dist_df_old[
  order(rownames(cpi_both_dist_df_old)),order(colnames(cpi_both_dist_df_old))]

cpi_both_dist_df_yng <- cpi_both_dist_df[
  grep("yng", colnames(cpi_both_dist_df)),
  grep("yng", rownames(cpi_both_dist_df))]

cpi_both_dist_df_yng <- cpi_both_dist_df_yng[
  order(rownames(cpi_both_dist_df_yng)),order(colnames(cpi_both_dist_df_yng))]

dist_df <- cpi_both_dist_df_old - cpi_both_dist_df_yng
dist_df <- dist_df[order(rownames(dist_df)),order(colnames(dist_df))]

```

```{r}

# change rownames and colnames to actual cell type names
rownames(dist_df) <- gsub(paste0("_", species, "_", "old"), "", rownames(dist_df))
colnames(dist_df) <- gsub(paste0("_", species, "_", "old"), "", colnames(dist_df))


dist_df <- rownames_to_column(dist_df, var = "ct_pair1")

dist_df_long <- dist_df %>%
  pivot_longer(cols = c(2:ncol(dist_df)),
               names_to = "ct_pair2",
               names_ptypes = list("ct_pair2" = character()),
               values_to = "distance",
               values_ptypes = list("euclidian_distance" = numeric())
  )


dist_df_long$emitter1 <- gsub("[&][[:print:]]+", "", dist_df_long$ct_pair1)
dist_df_long$receiver1 <- gsub("[[:print:]]+[&]", "", dist_df_long$ct_pair1)

dist_df_long$emitter2 <- gsub("[&][[:print:]]+", "", dist_df_long$ct_pair2)
dist_df_long$receiver2 <- gsub("[[:print:]]+[&]", "", dist_df_long$ct_pair2)

dist_df_long$emitter1 <- factor(dist_df_long$emitter1,
                                levels = names(col_emi_red))
dist_df_long$emitter2 <- factor(dist_df_long$emitter2,
                                levels = names(col_emi_red))

dist_df_long$receiver1 <- factor(dist_df_long$receiver1,
                                levels = names(col_rec_red))
dist_df_long$receiver2 <- factor(dist_df_long$receiver2,
                                levels = names(col_rec_red))
```

Stay within cell types

```{r}

dist_df_long_emi <- dist_df_long[
  dist_df_long$emitter1 == dist_df_long$emitter2,] 
dist_df_long_emi <- dist_df_long_emi[duplicated(dist_df_long_emi$distance),]

median_emi1_e <- dist_df_long_emi %>%
  group_by(emitter1) %>%
  summarise(median_val = median(distance))

plot_g1 <- ggplot(dist_df_long_emi,
                  aes(x = emitter1, y = distance, color = emitter1))+
  geom_quasirandom(size = 0.4)+
  geom_point(median_emi1_e, mapping = aes(y = median_val), color = "black", 
             fill = "white",  shape = 22, size = 3, stroke = 1)

dist_df_long_rec <- dist_df_long[
  dist_df_long$receiver1 == dist_df_long$receiver2,] 
dist_df_long_rec <- dist_df_long_rec[duplicated(dist_df_long_rec$distance),]


median_rec1_e <- dist_df_long_rec %>%
  group_by(receiver1) %>%
  summarise(median_val = median(distance))
  

plot_g2 <- ggplot(dist_df_long_rec, 
                  aes(x = receiver1, y = distance, color = receiver1))+
  geom_quasirandom(size = 0.4)+
  geom_point(median_rec1_e, mapping = aes(y = median_val), color = "black",
             fill = "white",  shape = 22, size = 3, stroke = 1)


plot_g1
plot_g2

median(dist_df_long_emi$distance)
median(dist_df_long_rec$distance)

```

# Uniform formatting

```{r}

plot_A <- plot_a+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Age", values = col_age)+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())

plot_a_legend <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$Age))+
  geom_point(size = 2.5)+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
 ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Age", values = col_age)

legend_a <- get_legend(plot_a_legend)

plot_A

```

```{r}

plot_B <- plot_b+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitters", values = col_emi_red)+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())


plot_b_legend <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$emitter))+
  geom_point(size = 2.5)+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Emitters", values = col_emi_red)

legend_b <- get_legend(plot_b_legend)

plot_B

```

```{r}

plot_C <- plot_c+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Receivers", values = col_rec_red)+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())


plot_c_legend <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = cpi_merged_pca$Celltypes$receiver))+
  geom_point(size = 2.5)+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_manual("Receivers", values = col_rec_red)

legend_c <- get_legend(plot_c_legend)

plot_C

```

```{r}

plot_E1 <- plot_e1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual("Emitters", values = col_emi_red)+
  xlab("CTPs (summarised)")+
  ylab(expression(atop("Direct EDs between",
                       paste("old and young CTPs"))))+
  ylim(limits = c(0, 125))

plot_E1

```

```{r}

plot_E2 <- plot_e2+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual("Receivers", values = col_rec_red)+
  xlab("CTPs (summarised)")+
  ylab(expression(atop("Direct EDs between",
                       paste("old and young CTPs"))))+
  ylim(limits = c(0, 125))

plot_E2

```

```{r}

plot_G1 <- plot_g1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual("Emitters", values = col_emi_red)+
  xlab("CTPs (summarised)")+
  ylab(expression(atop("EDs within old interactomes -",
                       paste("EDs within young interactomes"))))+
  ylim(limits = c(-40, 75))

plot_G1

```

```{r}

plot_G2 <- plot_g2+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual("Receivers", values = col_rec_red)+
  xlab("CTPs (summarised)")+
  ylab(expression(atop("EDs within old interactomes -",
                       paste("EDs within young interactomes"))))+
  ylim(limits = c(-40, 75))

plot_G2

```

# Assemble

```{r}

figure_5_abc <- ggarrange(
  
   ncol = 6,
    widths = c(3.9, 1, 3.9, 2, 3.9, 2.45) ,
  
  plot_A+theme(legend.position = "none"),
  legend_a,
  plot_B+theme(legend.position = "none"),
  legend_b,
  plot_C+theme(legend.position = "none"),
  legend_c
  
)

figure_5_abc

ggsave("images/figure_5_abc.png",
  figure_5_abc,
  width = 17*0.787402,
  height = 5*0.787402,
  units = c("in"),
  dpi = 300)

```

```{r}

figure_5_e <- ggarrange(
  
  plot_E1+theme(legend.position = "none")+
    ggtitle("Emitters"),
  plot_E2+theme(legend.position = "none")+
    ggtitle("Receivers")
 
)

figure_5_e


ggsave("images/figure_5_e.png",
  figure_5_e,
  width = 9*0.787402,
  height = 6*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_5_g <- ggarrange(
  
  plot_G1+theme(legend.position = "none")+
    ggtitle("Emitters"),
  plot_G2+theme(legend.position = "none")+
    ggtitle("Receivers")
 
)

figure_5_g

ggsave("images/figure_5_g.png",
  figure_5_g,
  width = 9*0.787402,
  height = 6*0.787402,
  units = c("in"),
  dpi = 150)

```
