---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"I optimized scRNAseq data for this method"

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(eulerr)
library(gridExtra)
library(cowplot)
library(scater)
library(ggbeeswarm)
library(ggpubr)

```

## Load

### Code

```{r load_code, message = FALSE}

source(file = "../../code/filepath.R")
source(file = "../../code/colors.R")
source(file = "../../interactome/functions/cpi_functions_calculation.R")

```

### Objects

```{r}

# merged and pre-processed SCE objects
sce_yng <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_ds_ctrm"))
sce_old <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_ds_ctrm"))

sce_yng_raw <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE"))
sce_old_raw <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE"))

sce_all <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_SCE"))

# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

cpi_yng_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi_pca"))
cpi_old_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi_pca"))

cpi_merged_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))

# corresponding RAW cpi objects
cpi_yng_raw <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi_raw_pca"))
cpi_old_raw <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi_raw_pca"))

cpi_merged_pca_raw <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_raw_pca"))


# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

# corresponding metrics objects RAW
ctpints_yng_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_raw_ctpints"))
ctints_yng_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_raw_ctints"))
nrlrs_yng_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_raw_nrlrs"))

ctpints_old_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_raw_ctpints"))
ctints_old_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_raw_ctints"))
nrlrs_old_raw <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_raw_nrlrs"))

# corresponding metrics objects NCT
ctpints_yng_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nct_ctpints"))
ctints_yng_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nct_ctints"))
nrlrs_yng_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nct_nrlrs"))

ctpints_old_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nct_ctpints"))
ctints_old_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nct_ctints"))
nrlrs_old_nct <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nct_nrlrs"))


```

```{r}

lrdb_part <- list.load(file = paste(
  filepath_lv1, "data/databases/lrdb_part.rds", sep = ""))

lrdb_comp <- list.load(file = paste(
  filepath_lv1, "data/databases/lrdb_comp.rds", sep = ""))

```

# Figure Parts

## A

This will be a schematic.

## B

LRDB Sources Euler plot.

```{r}

area_rnamagnet <- length(which(lrdb_comp$sources$RNA.Magnet_row != "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row == "NA" &
                                 lrdb_comp$sources$Mende.et.al_row == "NA"))

area_ccdb <- length(which(lrdb_comp$sources$RNA.Magnet_row == "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row != "NA" &
                                 lrdb_comp$sources$Mende.et.al_row == "NA"))

area_mende <- length(which(lrdb_comp$sources$RNA.Magnet_row == "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row == "NA" &
                                 lrdb_comp$sources$Mende.et.al_row != "NA"))

overlap_rnamagnet_ccdb <- length(which(lrdb_comp$sources$RNA.Magnet_row != "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row != "NA" &
                                 lrdb_comp$sources$Mende.et.al_row == "NA"))

overlap_ccdb_mende <-length(which(lrdb_comp$sources$RNA.Magnet_row != "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row == "NA" &
                                 lrdb_comp$sources$Mende.et.al_row != "NA"))

overlap_rnamagnet_mende <- length(which(lrdb_comp$sources$RNA.Magnet_row == "NA" &
                                 lrdb_comp$sources$CellChatDB.mouse_row != "NA" &
                                 lrdb_comp$sources$Mende.et.al_row != "NA"))

overlap_all <- length(which(lrdb_comp$sources$RNA.Magnet_row != "NA" &
                              lrdb_comp$sources$CellChatDB.mouse_row != "NA" &
                              lrdb_comp$sources$Mende.et.al_row != "NA" ))


fit <- euler(c("A" = area_rnamagnet, 
               "B" = area_ccdb, 
               "C" = area_mende,
               "A&B" = overlap_rnamagnet_ccdb,
               "A&C" = overlap_ccdb_mende,
               "B&C" = overlap_rnamagnet_mende,
               "A&B&C" = overlap_all))

plot_b <- plot(fit, 
     labels = c("", "", ""),
     fills = c("grey80", "orange", "white"),
     quantities = list(type = "percent", cex = 1))

grid.arrange(
  grobs = plot_b[[5]]
)

plot_b

```

## C

LRDB Interactions.

```{r}

# info from lrdb
interactions_all <- as.data.frame(table(lrdb_comp$interactions$interaction_type))
colnames(interactions_all)[1] <- "Interaction_type" 

# info from yng and old cpis
interactions_yng <- as.data.frame(table(cpi_yng$Interactions$interaction_type[
  is.nan(rowMeans(cpi_yng$Score, na.rm = TRUE)) == FALSE]))
interactions_old <- as.data.frame(table(cpi_old$Interactions$interaction_type[
  is.nan(rowMeans(cpi_old$Score, na.rm = TRUE)) == FALSE]))

interactions_all$mmus_young[match(interactions_yng$Var1, interactions_all[,1])] <- interactions_yng$Freq
interactions_all$mmus_old[match(interactions_old$Var1, interactions_all[,1])] <- interactions_old$Freq


colnames(interactions_all)[2] <- "LRDB"

interactions_all <- pivot_longer(interactions_all, 
                                 cols = c(2:4),
                                 names_to = "Sample")

interactions_all$Interaction_type <- factor(interactions_all$Interaction_type,
                                            levels = names(col_itp))

interactions_all$Sample[interactions_all$Sample == "mmus_young"] <- "young"
interactions_all$Sample[interactions_all$Sample == "mmus_old"] <- "old"

interactions_all$Sample <- factor(interactions_all$Sample,
                                  levels = c("LRDB", "young", "old"))

interactions_all$value[is.na(interactions_all$value)] <- 0

plot_c <- ggplot(interactions_all,  aes(x = Sample,
                              y = value,
                              fill = Interaction_type))+
  geom_col(position = "stack")+
  ylab("Number of interactions")+
  scale_fill_manual("LRI functional annotation", values = col_itp)
  
plot_c

```

# D

UMAP with discarded cells.

```{r}

hem_cts <- c("LMPPs", "Small pre-BCs", "Large pre-BCs", "Pro-BCs",
             "Mature B cells", "T cells", "NK cells", "Gran/Mono prog.",
             "Monocyte prog.", "Neutrophil prog.", "Eo/Baso prog.",
             "Monocytes", "Neutrophils", "Dendritic cells", "Ery/Mk prog.",
             "Megakaryocyte prog.", "Erythrocyte prog.", "Erythroid",
             "Baso/Eo/Mast prog.", "T cells/NK cells", "Monocyte-primed prog.",
             "Dendritic-primed prog.", "LT-HSCs", "Common myeloid prog.",
             "Gran/Mono prog."
             )

hem_pos <- intersect(which(sce_all$Fraction == "stromal"),
                       which(sce_all$Identity %in% hem_cts))
  
sce_all$Discard <- rep("FALSE", length(ncol(sce_all)))
sce_all$Discard[hem_pos] <- "TRUE"
  
# cell type vector of cell types to remove from all fractions
remove_cts <- c("Schwann cells", "Mature B cells", "T cells/NK cells", 
                "Pro-BCs", "Dendritic cells", "Monocytes", "Neutrophils", 
                "Erythroid", "Small pre-BCs", "Large pre-BCs", 
                "Immature B cells",  "Chondrocytes", "Myofibroblasts", 
                "Gran/Mono prog.")

remove_pos <- which(sce_all$Identity %in% remove_cts)
sce_all$Discard[remove_pos] <- "TRUE"


plot_d <- plotUMAP(sce_all,  colour_by = "Discard", point_size = 0.1, 
                       point_alpha = 1)+
  scale_color_manual("Removed cells", values = c("TRUE" = "orange", 
                                                 "FALSE" = "grey20"))

plot_d_leg <- plotUMAP(sce_all,  colour_by = "Identity", point_size = 2.5, 
                       point_alpha = 1)+
  scale_color_manual("Removed cells", values = c("TRUE" = "orange", 
                                                 "FALSE" = "grey20"))

plot_d

length(sce_all$Discard)
length(which(sce_all$Discard == TRUE))

```

## E und F

Downsampling.

```{r}

qc_df_yng_df <- perCellQCMetrics(sce_yng, assay.type = "downsampled")
qc_df_old_df <- perCellQCMetrics(sce_old, assay.type = "downsampled")

qc_df_yng_raw_df <- perCellQCMetrics(sce_yng)
qc_df_old_raw_df <- perCellQCMetrics(sce_old)

qc_df_yng_df$Age <- sce_yng$Age
qc_df_old_df$Age <- sce_old$Age
qc_df_yng_raw_df$Age <- sce_yng$Age
qc_df_old_raw_df$Age <- sce_old$Age

qc_df_yng_df$Identity <- sce_yng$Identity
qc_df_old_df$Identity <- sce_old$Identity
qc_df_yng_raw_df$Identity <- sce_yng$Identity
qc_df_old_raw_df$Identity <- sce_old$Identity

qc_df_yng_df$condition <- "After"
qc_df_old_df$condition <- "After"
qc_df_yng_raw_df$condition <- "Before"
qc_df_old_raw_df$condition <- "Before"

qc_df_all_df <- rbind(qc_df_yng_df,
                      qc_df_old_df,
                      qc_df_yng_raw_df,
                      qc_df_old_raw_df)

qc_df_all_df$condition <- factor(qc_df_all_df$condition, 
                                 levels = c("Before",
                                            "After"))

qc_df_all_df$Age <- factor(qc_df_all_df$Age, 
                                 levels = c("young",
                                            "old"))

qc_df_all_df$Identity <- factor(qc_df_all_df$Identity, 
                                 levels = c(
                                   names(col_emi_red),
                                   names(col_rec_red)
                                 ))

```

```{r}

plot_e <- ggplot(as.data.frame(qc_df_all_df), 
                  aes(x = Age, y = detected, color = Age))+
  geom_quasirandom(size = 0.1)+
  facet_grid(cols = vars(condition))+
  scale_color_manual("Age", values = col_age)

plot_f <- ggplot(as.data.frame(qc_df_all_df[qc_df_all_df$condition == "After",]),
                  aes(x = Age, y = detected, color = Age))+
  geom_quasirandom(size = 0.1)+
  facet_grid(cols = vars(Identity), switch = "x")+
  scale_color_manual("Age", values = col_age)+
  ggtitle("After")

  
plot_e  
plot_f
  
```

```{r}

med_yng <- median(qc_df_all_df$detected[
  intersect(which(qc_df_all_df$Age == "young"),
            which(qc_df_all_df$condition == "before downsampling"))])
med_old <- median(qc_df_all_df$detected[
  intersect(which(qc_df_all_df$Age == "old"),
            which(qc_df_all_df$condition == "before downsampling"))])

med_yng
med_old

2818/1661

```

## G

```{r}

ctints_both <- rbind(ctints_yng[[1]],
                    ctints_old[[1]])
ctints_raw_both <- rbind(
                    ctints_yng_raw[[1]],
                    ctints_old_raw[[1]])

ctints_yng[[1]]$condition <- "none"
ctints_old[[1]]$condition <- "none"

ctints_all <- rbind(ctints_yng[[1]],
                    ctints_old[[1]],
                    ctints_yng_raw[[1]],
                    ctints_old_raw[[1]])

ctints_all$condition[ctints_all$condition == "none"] <- "After pre-processing"
ctints_all$condition[ctints_all$condition == "no pre-processing steps"] <- "Before pre-processing"

ctints_all$condition <- factor(ctints_all$condition, 
                               levels = c("Before pre-processing", "After pre-processing"))

```

```{r}

plot_g <- ggplot(ctints_all)+
  geom_point(aes(x = nr_cells,  y = nr_ints, 
                color = age))+
  theme_classic()+
  scale_color_manual("Age", values = col_age)+
  facet_grid(rows = vars(age), cols = vars(condition))

plot_g

```

## H

PCA of nr of interactions per cell type pair

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctpints_both_raw <- rbind(ctpints_yng_raw[[1]], ctpints_old_raw[[1]])
ctpints_both_raw$age <- factor(ctpints_both_raw$age, levels = c("young", "old"))
ctpints_both_raw$emitter <- factor(ctpints_both_raw$emitter, 
                               levels = names(col_emi_red))
ctpints_both_raw$receiver <- factor(ctpints_both_raw$receiver, 
                               levels = names(col_rec_red))
```


```{r}

# must reorder the ctpints object to fit the rownames of the cpi_pca objects
ctpints_both_test <- ctpints_both
ctpints_both_test$ct_pairs <- paste(ctpints_both_test$ct_pairs, 
                                    ctpints_both_test$species, 
                                    ctpints_both_test$age, sep = "_")
ctpints_both_test$ct_pairs[
  grep("young", 
       ctpints_both_test$ct_pairs)] <- gsub("young", 
                                            "yng", 
                                            ctpints_both_test$ct_pairs)

ctpints_both_raw_test <- ctpints_both_raw
ctpints_both_raw_test$ct_pairs <- paste(ctpints_both_raw_test$ct_pairs, 
                                    ctpints_both_raw_test$species, 
                                    ctpints_both_raw_test$age, 
                                    "raw", sep = "_")

ctpints_both_raw_test$ct_pairs <- gsub("young", 
                                            "yng", 
                                            ctpints_both_raw_test$ct_pairs)

ctpints_both_test <- ctpints_both_test[
  match(rownames(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),]),
                                             ctpints_both_test$ct_pairs),]
ctpints_both_raw_test <- ctpints_both_raw_test[
  match(rownames(cpi_merged_pca_raw$PCA[1:(nrow(cpi_merged_pca_raw$PCA)-1),]),
                                             ctpints_both_raw_test$ct_pairs),]

plot_h1 <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = ctpints_both_test$nr_ints))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))



plot_h2 <- ggplot(cpi_merged_pca_raw$PCA[1:(nrow(cpi_merged_pca_raw$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = ctpints_both_raw_test$nr_ints))+
  geom_point(size = 1.5)+
  theme_classic()+
  ylab(paste("PC2 [", round(cpi_merged_pca_raw$PCA[
    nrow(cpi_merged_pca_raw$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca_raw$PCA[
    nrow(cpi_merged_pca_raw$PCA), 1], 
                                    digits = 2), "%]", sep = ""))

plot_h1
plot_h2

```

## I&J

Repertoires: which genes are expressed in over 5% of cells?
This takes very long to recalculate.

```{r}

sce_old_lig <- sce_old[!is.na(match(rowData(sce_old)$ID,
                                unique(lrdb_comp$interactions$ligand_ensembl_id))),]
sce_yng_lig <- sce_yng[!is.na(match(rowData(sce_yng)$ID,
                                unique(lrdb_comp$interactions$ligand_ensembl_id))),]

sce_old_rec <- sce_old[!is.na(match(rowData(sce_old)$ID,
                                unique(lrdb_comp$interactions$receptor_ensembl_id))),]
sce_yng_rec <- sce_yng[!is.na(match(rowData(sce_yng)$ID,
                                unique(lrdb_comp$interactions$receptor_ensembl_id))),]

```

```{r}

# remove all cell types that were not detected to avoid dividing by 0 
sce_old_lig_pec <- expr_cells_perc(
  assay = "downsampled",
  sce = sce_old_lig,
  cts = levels(colData(sce_old)$Identity)[
    which(levels(colData(sce_old)$Identity) %in% 
            unique(colData(sce_old)$Identity))],
  cts_list = as.list(levels(colData(sce_old)$Identity)[
    which(levels(colData(sce_old_lig)$Identity) %in% 
            unique(colData(sce_old_lig)$Identity))]))

sce_yng_lig_pec <- expr_cells_perc(
  assay = "downsampled",  sce_yng_lig,
  cts = levels(colData(sce_yng)$Identity)[
    which(levels(colData(sce_yng)$Identity) %in% 
            unique(colData(sce_yng)$Identity))],
  cts_list = as.list(levels(colData(sce_yng)$Identity)[
    which(levels(colData(sce_yng)$Identity) %in% 
            unique(colData(sce_yng)$Identity))]))


sce_old_rec_pec <- expr_cells_perc(
  assay = "downsampled",  sce_old_rec,
  cts = levels(colData(sce_old)$Identity)[
    which(levels(colData(sce_old)$Identity) %in% 
            unique(colData(sce_old)$Identity))],
  cts_list = as.list(levels(colData(sce_old_lig)$Identity)[
    which(levels(colData(sce_old_lig)$Identity) %in% 
            unique(colData(sce_old_lig)$Identity))]))

sce_yng_rec_pec <- expr_cells_perc(
  assay = "downsampled",  sce_yng_rec,
  cts = levels(colData(sce_yng)$Identity)[
    which(levels(colData(sce_yng)$Identity) %in% 
            unique(colData(sce_yng)$Identity))],
  cts_list = as.list(levels(colData(sce_yng)$Identity)[
    which(levels(colData(sce_yng)$Identity) %in% 
            unique(colData(sce_yng)$Identity))]))

```

Prepare data for ggplot visualisation.

```{r}

sce_old_pec_lig_subs <- sce_old_lig_pec[,which(colnames(sce_old_lig_pec) 
                                         %in% names(col_emi_red))]
sce_yng_pec_lig_subs <- sce_yng_lig_pec[,which(colnames(sce_yng_lig_pec) 
                                         %in% names(col_emi_red))]

sce_old_pec_rec_subs <- sce_old_rec_pec[,which(colnames(sce_old_rec_pec) 
                                         %in% names(col_rec_red))]
sce_yng_pec_rec_subs <- sce_yng_rec_pec[,which(colnames(sce_yng_rec_pec) 
                                         %in% names(col_rec_red))]

sce_old_pec_lig_gg <- sce_old_pec_lig_subs %>%
  gather(colnames(sce_old_pec_lig_subs), key = "celltype", value = "percentage")
sce_yng_pec_lig_gg <- sce_yng_pec_lig_subs %>%
  gather(colnames(sce_yng_pec_lig_subs), key = "celltype", value = "percentage")

sce_old_pec_rec_gg <- sce_old_pec_rec_subs %>%
  gather(colnames(sce_old_pec_rec_subs), key = "celltype", value = "percentage")
sce_yng_pec_rec_gg <- sce_yng_pec_rec_subs %>%
  gather(colnames(sce_yng_pec_rec_subs), key = "celltype", value = "percentage")

sce_old_pec_lig_gg$percentage <- sce_old_pec_lig_gg$percentage *100
sce_yng_pec_lig_gg$percentage <- sce_yng_pec_lig_gg$percentage *100

sce_old_pec_rec_gg$percentage <- sce_old_pec_rec_gg$percentage *100
sce_yng_pec_rec_gg$percentage <- sce_yng_pec_rec_gg$percentage *100

sce_old_pec_lig_gg$celltype <- factor(sce_old_pec_lig_gg$celltype, levels = 
                                     names(col_emi_red))
sce_yng_pec_lig_gg$celltype <- factor(sce_yng_pec_lig_gg$celltype, levels = 
                                     names(col_emi_red))

sce_old_pec_rec_gg$celltype <- factor(sce_old_pec_rec_gg$celltype, levels = 
                                     names(col_rec_red))
sce_yng_pec_rec_gg$celltype <- factor(sce_yng_pec_rec_gg$celltype, levels = 
                                     names(col_rec_red))

```

```{r}

sce_yng_pec_lig_gg$annotation <- "Ligand"
sce_yng_pec_rec_gg$annotation <- "Receptor"

gg_df_g_y <- rbind(sce_yng_pec_lig_gg, sce_yng_pec_rec_gg)

plot_i <- ggplot(gg_df_g_y, aes(x = celltype, y = percentage, color = annotation))+
  geom_quasirandom(size = 0.3)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Fraction of cells expressing L/R genes [%]")+
  xlab("Cell type")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, slope = 0, linetype = "dotted", size = 0.8)

plot_i_legend <- ggplot(gg_df_g_y, aes(x = celltype, y = percentage, color = annotation))+
  geom_quasirandom(size = 2.5)+
  theme_classic()
  


legend_i <- get_legend(plot_i_legend)
plot_i

```

```{r}

sce_old_pec_lig_gg$annotation <- "Ligand"
sce_old_pec_rec_gg$annotation <- "Receptor"

gg_df_o <- rbind(sce_old_pec_lig_gg, sce_old_pec_rec_gg)

plot_j <- ggplot(gg_df_o, aes(x = celltype, y = percentage, color = annotation))+
  geom_quasirandom(size = 0.3)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  ylab("Fraction of cells expressing L/R genes [%]")+
  xlab("Cell type")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, slope = 0, linetype = "dotted", size = 0.8)

plot_j

```

## K

The same plot but by Annotation.
Young.

```{r}

plot_k1 <- ggplot(gg_df_g_y, aes(x = annotation, y = percentage, color = annotation))+
  geom_boxplot(outlier.size = 0.7)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylab("Fraction of cells expressing L/R genes [%]")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, linetype = 3, slope = 0, size = 0.8)

legend_k1 <- get_legend(plot_k1)
plot_k1

```

Old.

```{r}

plot_k2 <- ggplot(gg_df_o, aes(x = annotation, y = percentage, color = annotation))+
  geom_boxplot(outlier.size = 0.7)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylab("Fraction of cells expressing L/R genes [%]")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, linetype = 3, slope = 0, size = 0.8)

plot_k2

```

Both.

```{r}

gg_df_g_y$age <- "Young"
gg_df_o$age <- "Old"

gg_df_both <- rbind(gg_df_g_y, gg_df_o)

gg_df_both$age <- factor(gg_df_both$age, levels = c("Young", "Old"))

plot_k3 <- ggplot(gg_df_both, aes(x = annotation, y = percentage, color = annotation))+
  geom_boxplot(outlier.size = 0.7)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")+
  ylab(expression(atop("Cells expressing",
                       paste("L/R genes [%]"))))+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, linetype = 3, slope = 0, size = 0.8)+
  facet_grid(cols = vars(age))

plot_k3

```

## M

Nr of ligands/receptors after cutoff.

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))

nrlrs_both$condition <- "all pre-processing steps"
nrlrs_both$species <- "mmus"
```

```{r}

nrlrs_both_nct <- rbind(nrlrs_yng_nct, nrlrs_old_nct)


nrlrs_both_nct$age <- factor(nrlrs_both_nct$age, levels = c("young", "old"))
nrlrs_both_nct$celltypes <- factor(nrlrs_both_nct$celltypes, 
                               levels = names(col_cts_red))

nrlrs_both_nct$condition <- "no cut-off"

```

```{r}

gg_df2 <- rbind(nrlrs_both_nct,
               nrlrs_both)

gg_df2$condition <- factor(gg_df2$condition,
                          levels = c("no cut-off", "all pre-processing steps"))

gg_df2$age <- unfactor(gg_df2$age)
gg_df2$age[gg_df2$age == "young"] <- "Young"
gg_df2$age[gg_df2$age == "old"] <- "Old"

gg_df2$age <- factor(gg_df2$age,
                          levels = c("Young", "Old"))
gg_df2$annotation <- factor(gg_df2$annotation,
                            levels = c("emitter", "receiver"))

```

```{r}

plot_m <- ggplot(gg_df2[gg_df2$condition == "all pre-processing steps",], 
                  aes(x = annotation, y = nr_lrs, color = annotation))+
  geom_boxplot()+
  scale_color_manual("Gene classification", values = col_ann)+
  ylab(expression(atop("Number of ligands or",
                       paste("receptors per cell type"))))+
  facet_grid(cols = vars(age))
  
plot_m
  
```

# Assemble

```{r}

# not much I can do about plot()
plot_B <- plot_b
plot_B

```

```{r}

plot_C <- plot_c+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 90))

legend_c <- get_legend(plot_C)

plot_C

```

```{r}

plot_D <- plot_d+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())

plot_D_legend <- plot_d_leg+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())

legend_D <- get_legend(plot_D_legend)

plot_D

```

```{r}


plot_E <- plot_e+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # indidivual additions
  theme(strip.text.y = element_blank(),
        strip.text.x = element_text(size = 13, face = "bold"),
        strip.background.x = element_blank(),
        strip.background.y = element_blank()
        )+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())+
  ylab("Gene counts per cell type")+
  ggtitle("Downsampling")
              

plot_F <- plot_f+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # indidivual additions
  theme(strip.text.y = element_blank(),
        strip.text.x = element_text(size = 11, angle = 90),
        strip.background.x = element_blank(),
        strip.background.y = element_blank(),
        strip.placement = "outside"
        )+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())+
  ylab("Gene counts per cell")
 
plot_E             
plot_F

```

```{r}

plot_G <- plot_g+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # indidivual additions
  theme(strip.text.y = element_blank(),
        strip.text.x = element_text(size = 13, face = "bold"),
          strip.background.x = element_blank(),
        strip.background.y = element_blank()
        )+
  scale_y_continuous(limits = c(0, 2500), breaks = c(0, 1000, 2000))+
  scale_x_continuous(limits = c(0, 8000), breaks = c(0, 2500, 5000, 7500))+
  ylab("Number of interactions per cell type")+
  xlab("Number of cells per cell type")
                     
plot_G

legend_G <- get_legend(plot_G)

```

```{r}

plot_H_legend <- plot_h1+ # base theme
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_gradientn("Interactions/cell type pair", 
                         colors = c("black", "darkorange3", "gold"),
                         limits = c(0, 1600))

legend_H <- get_legend(plot_H_legend)

plot_H <- ggarrange(
  
  plot_h2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13, face = "bold"),
          strip.background.x = element_blank(),
        strip.background.y = element_blank())+
    scale_color_gradientn("Interactions/cell type pair", 
                         colors = c("black", "darkorange3", "gold"),
                         limits = c(0, 1600))+
    ggtitle("Before pre-processing")+
    theme(plot.title = element_text(hjust = 0.45, size = 13, face = "bold"))
  
  ,

  plot_h1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
   theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13, face = "bold",),
          strip.background.x = element_blank(),
        strip.background.y = element_blank())+
    scale_color_gradientn("Interactions/cell type pair", 
                         colors = c("black", "darkorange3", "gold"),
                         limits = c(0, 1600))+
    ggtitle("After pre-processing")+
    theme(plot.title = element_text(hjust = 0.45, size = 13, face = "bold"))
  
  

)

legend_h <- get_legend(plot_H_legend)

plot_H

```

```{r}

plot_I <- plot_i+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Cell type")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, slope = 0, linetype = "dotted", size = 0.8)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.45))+
  ggtitle("Young repertoires")+
 ylab(expression(atop("Cells expressing",
                       paste("L/R genes [%]"))))

plot_J <- plot_j+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Cell type")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, slope = 0, linetype = "dotted", size = 0.8)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.45))+
  ggtitle("Old repertoires")+
  ylab(expression(atop("Cells expressing",
                       paste("L/R genes [%]"))))


plot_J_legend <- plot_j+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Cell type")+
  scale_color_manual("Gene annotation", values = c("Ligand" = col_ann[[1]], 
                                                   "Receptor" = col_ann[[2]]))+
  geom_abline(intercept = 5, slope = 0, linetype = "dotted", size = 0.8)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.45))+
  ggtitle("Old repertoires")+
  ylab(expression(atop("Cells expressing",
                       paste("L/R genes [%]"))))

legend_J <- get_legend(plot_J_legend)

plot_I
plot_J

```

```{r}

plot_K <- plot_k3+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())+
  theme(strip.text.x = element_text(size = 13, face = "bold"),
          strip.background.x = element_blank(),
        strip.background.y = element_blank())

plot_k_legend <- get_legend(plot_K)
  
plot_K

```

```{r}

plot_M <- plot_m+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+
  theme(strip.text.x = element_text(size = 13, face = "bold"),
          strip.background.x = element_blank(),
        strip.background.y = element_blank())+
  ylim(limits = c(0, 200))

plot_M

```

```{r}

plot_B
plot_C
plot_D
plot_E
plot_F
plot_G
plot_H
plot_I
plot_J
plot_K
plot_M

```

```{r, fig.width = 4.72, fig.height = 1.57}

#12

legend_bcd <-  ggarrange(
  ncol = 1, 
  heights = c(2, 1),
  legend_c, 
  legend_D
            )

figure_1_bcd <- ggarrange(
  ncol = 4,
  widths = c(3, 3, 3, 3),
  
  plot_B,
  plot_C+theme(legend.position = "none"),
  legend_bcd,
  plot_D+theme(legend.position = "none")
)

figure_1_bcd

ggsave("images/figure_1_bcd.png",
  figure_1_bcd,
  width = 12*0.787402,
  height = 4.3*0.787402,
  units = c("in"),
  dpi = 300)

```

```{r}

figure_1_ef <- ggarrange(
  ncol = 2,
  widths = c(5, 7.5),
  
  plot_E+theme(legend.position = "none"),
  plot_F+theme(legend.position = "none")
)

figure_1_ef

ggsave("images/figure_1_ef.png",
  figure_1_ef,
  width = 12*0.787402,
  height = 4.5*0.787402,
  units = c("in"),
  dpi = 300)


```


```{r}

#12
figure_1_gh <- ggarrange(
  
  ncol = 2,
  #widths = c(6.5, 7),
  plot_G+theme(legend.position = "none"),
  ggarrange(
    ncol = 1,
    heights = c(2,4),
    ggarrange(
      ncol = 2,
      widths = c(2,2),
      legend_G,
      legend_H),
      plot_H+theme(legend.position = "none")
    )
)
figure_1_gh

ggsave("images/figure_1_gh.png",
  figure_1_gh,
  width = 12*0.787402,
  height = 6*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}


# 12
figure_1_ijkm <- ggarrange(
  
  ncol = 2,
  widths = c(13, 4),
  
  ggarrange(
    ncol = 1,
    heights = c(5, 2),
  ggarrange(
     ncol = 2,
      plot_I+theme(legend.position = "none"),
      plot_J+theme(legend.position = "none")),
  ggarrange(
     ncol = 2,
     widths = c(1, 1),
    plot_k_legend)),
  
  ggarrange(
    ncol = 1,
    heights = c(2, 2),
    plot_K+theme(legend.position = "none"),
    plot_M+theme(legend.position = "none")
  )
)
figure_1_ijkm

ggsave("images/figure_1_ijkm.png",
  figure_1_ijkm,
  width = 12*0.787402,
  height = 7*0.787402,
  units = c("in"),
  dpi = 150)

```
