---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"This method can capture important interactions"

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(eulerr)
library(gridExtra)
library(cowplot)
library(scater)
library(ggbeeswarm)
library(ggpubr)

```

## Load

### Code

```{r load_code, message = FALSE}

source(file = "../../code/filepath.R")
source(file = "../../code/colors.R")

```

### Objects

```{r}

mmus_yng_sce_ds <- readRDS(file = paste0(
    filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_ds"))
mmus_old_sce_ds <- readRDS(file = paste0(
    filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_ds"))

score_df_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_ctpints_score_df"))

score_df_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_ctpints_score_df"))

```

```{r}

score_df_yng$Age <- "Young"
score_df_old$Age <- "Old"

score_df_both <- rbind(score_df_yng, score_df_old)

```

```{r}

sce_all <- cbind(mmus_yng_sce_ds, mmus_old_sce_ds)
assays(sce_all)$logcounts <- assays(sce_all)$downsampled

```


# Figure Parts

## A, B, G, H
 
Umaps corresponding to the histograms

```{r}

plot_a <- plotUMAP(sce_all,  colour_by = "Kitl", point_size = 0.5,
                       point_alpha = 1)+
  scale_color_gradientn("Kitlg ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_b <- plotUMAP(sce_all,  colour_by = "Kit", point_size = 0.5, 
                       point_alpha = 1)+
  scale_color_gradientn("Kit  ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_g <- plotUMAP(sce_all,  colour_by = "Cxcl12", point_size = 0.5, 
                       point_alpha = 1)+
  scale_color_gradientn("Cxcl12", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_h <- plotUMAP(sce_all,  colour_by = "Cxcr4", point_size = 0.5, 
                       point_alpha = 1)+
  scale_color_gradientn("Cxcr4 ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_a
plot_b
plot_g
plot_h

```

## C-F1

Histogram of top % of interactions detected per cell type.
This requires cpi_interactions_Yng_vs_old to be loaded.

Kitl&Kit

```{r}

plot_c1 <- ggplot(score_df_yng[score_df_yng$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, fill = emitter))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_d1 <- ggplot(score_df_yng[score_df_yng$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, fill = receiver))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_e1 <- ggplot(score_df_old[score_df_old$interaction == "Kitl&Kit",],
                  aes(x = score_percentile, fill = emitter))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_f1 <- ggplot(score_df_old[score_df_old$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, fill = receiver))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_c1
plot_d1
plot_e1
plot_f1

```

## I-M1

Cxcl12&Cxcr4

```{r}

plot_i1 <- ggplot(score_df_yng[score_df_yng$interaction == "Cxcl12&Cxcr4",],
                  aes(x = score_percentile, fill = emitter))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_j1 <- ggplot(score_df_yng[score_df_yng$interaction == "Cxcl12&Cxcr4",],
                  aes(x = score_percentile, fill = receiver))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_k1 <- ggplot(score_df_old[score_df_old$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, fill = emitter))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)

plot_m1 <- ggplot(score_df_old[score_df_old$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, fill = receiver))+
  geom_histogram(color = "grey20", size = 0.2, binwidth = 5, boundary = 0)


plot_i1
plot_j1
plot_k1
plot_m1

```

## C-F2

Score distributions for all cell types Kitl&Kit

```{r}

plot_c2 <- ggplot(score_df_yng[score_df_yng$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, 
                      color = emitter, y = fct_rev(emitter)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)

plot_d2 <- ggplot(score_df_yng[score_df_yng$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, 
                      color = receiver, y = fct_rev(receiver)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)

plot_e2 <- ggplot(score_df_old[score_df_old$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, 
                      color = emitter, y = fct_rev(emitter)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)

plot_f2 <- ggplot(score_df_old[score_df_old$interaction == "Kitl&Kit",], 
                  aes(x = score_percentile, 
                      color = receiver, y = fct_rev(receiver)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)


plot_c2
plot_d2
plot_e2
plot_f2

```

## I-M2

Score distributions for all cell types Cxcl12&Cxcr4

```{r}

plot_i2 <- ggplot(score_df_yng[score_df_yng$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, 
                      color = emitter, y = fct_rev(emitter)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)

plot_j2 <- ggplot(score_df_yng[score_df_yng$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, 
                      color = receiver, y = fct_rev(receiver)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)


plot_k2 <- ggplot(score_df_old[score_df_old$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, 
                      color = emitter, y = fct_rev(emitter)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)

plot_m2 <- ggplot(score_df_old[score_df_old$interaction == "Cxcl12&Cxcr4",], 
                  aes(x = score_percentile, 
                      color = receiver, y = fct_rev(receiver)))+
  geom_boxplot()+ 
  scale_y_discrete(drop=FALSE)



plot_i2
plot_j2
plot_k2
plot_m2

```





# Uniform Formatting

```{r}

plot_A <- plot_a+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"),
        plot.title = element_text(size = 14, face = "bold.italic") )+
  ggtitle("Kitlg&Kit")

plot_B <- plot_b+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_G <- plot_g+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"),
        plot.title = element_text(size = 14, face = "bold.italic") )+
  ggtitle("Cxcl12&Cxcr4")

plot_H <- plot_h+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_A
plot_B
plot_G
plot_H

```

```{r}

plot_C1 <- plot_c1+
# base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Kitlg&Kit"), " score percentile")))+
  ggtitle("Young")

plot_C_leg1 <- plot_c1+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_emi_red)


legend_C1 <- get_legend(plot_C_leg1)

plot_C1+ theme(legend.position = "none")

```

```{r}

plot_D1 <- plot_d1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Receivers", values = col_rec_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Kitlg&Kit"), " score percentile")))

plot_D1_leg <- plot_D1+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Receivers", values = col_rec_red)


legend_D1 <- get_legend(plot_D1_leg)

plot_D1+ theme(legend.position = "none")


```

```{r}

plot_E1 <- plot_e1+
# base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Kitlg&Kit"), " score percentile")))+
  ggtitle("Old")

plot_E1+ theme(legend.position = "none")

```

```{r}

plot_F1 <- plot_f1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_rec_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Kitlg&Kit"), " score percentile")))

plot_F1+theme(legend.position = "none")

```




```{r}

plot_I1 <- plot_i1+
# base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Cxcl12&Cxcr4"), " score percentile")))+
  ggtitle("Young")

plot_I1+ theme(legend.position = "none")

```

```{r}

plot_J1 <- plot_j1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_rec_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Cxcl12&Cxcr4"), " score percentile")))

plot_J1+ theme(legend.position = "none")

```

```{r}

plot_K1 <- plot_k1+
# base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_emi_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Cxcl12&Cxcr4"), " score percentile")))+
  ggtitle("Old")

plot_K1+ theme(legend.position = "none")

```

```{r}

plot_M1 <- plot_m1+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_fill_manual("Emitters", values = col_rec_red)+
  ylim(c(0, 60))+
  xlim(0, 100)+
  ylab("Number of CTPs")+
  xlab(expression(paste(italic("Cxcl12&Cxcr4"), " score percentile")))

plot_M1+theme(legend.position = "none")

```

```{r}

plot_C2 <- plot_c2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Emitters", values = col_emi_red)+
  xlim(0, 100)+ 
  ylab("Emitters")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)))+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_C2 + theme(legend.position = "none")
  
```

```{r}

plot_D2 <- plot_d2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Receivers", values = col_rec_red)+
  xlim(0, 100)+
  ylab("Receivers")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_D2 + theme(legend.position = "none")

```

```{r}

plot_E2 <- plot_e2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Emitters", values = col_emi_red)+
  xlim(0, 100)+ 
  ylab("Emitters")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_E2 + theme(legend.position = "none")
  
```

```{r}

plot_F2 <- plot_f2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Receivers", values = col_rec_red)+
  xlim(0, 100)+
  ylab("Receivers")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_F2 + theme(legend.position = "none")

```


```{r}

plot_I2 <- plot_i2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Emitters", values = col_emi_red)+
  xlim(0, 100)+ 
  ylab("Emitters")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_I2 + theme(legend.position = "none")
  
```

```{r}

plot_J2 <- plot_j2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Receivers", values = col_rec_red)+
  xlim(0, 100)+
  ylab("Receivers")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_J2 + theme(legend.position = "none")

```

```{r}

plot_K2 <- plot_k2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Emitters", values = col_emi_red)+
  xlim(0, 100)+ 
  ylab("Emitters")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
plot_K2 + theme(legend.position = "none")
  
```

```{r}

plot_M2 <- plot_m2+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # indidivual additions
  scale_color_manual("Receivers", values = col_rec_red)+
  xlim(0, 100)+
  ylab("Receivers")+
  xlab("Kitl&Kit score percentile")+
  scale_y_discrete(labels = c(rep("     ", 11)), drop = FALSE)+
  theme(axis.ticks.y = element_blank(),
        axis.title.x = element_blank())
  
  
plot_M2 + theme(legend.position = "none")


```

```{r}

plot_A
plot_B
plot_C1
plot_C2
plot_D1
plot_D2
plot_E1
plot_E2
plot_F1
plot_F2

plot_G
plot_H
plot_I1
plot_I2
plot_J1
plot_J2
plot_K1
plot_K2
plot_M1
plot_M2

```

# Assemble

```{r}

figure_2_abcdef <- ggarrange(
  
  ncol = 2,
  
  
  ggarrange(
    ncol = 1,
    heights = c(1, 0.05, 2.6),
    plot_A,
    NULL,
    ggarrange(
      ncol = 1,
      heights = c(1, 0.05, 1),
      ggarrange(
        ncol = 1,
        heights = c(2, 1.1),
        plot_C1+theme(legend.position = "none"),
        plot_C2+theme(legend.position = "none")),
      NULL,
      ggarrange(
        ncol = 1,
        heights = c(2, 1.1),
        plot_E1+theme(legend.position = "none"),
        plot_E2+theme(legend.position = "none"))
    )
  ),
  
  ggarrange(
    ncol = 1,
    heights = c(1, 0.05 ,2.6),
    plot_B+ggtitle(""),
    NULL,
    ggarrange(
      ncol = 1,
      heights = c(1, 0.05, 1),
      ggarrange(
        ncol = 1,
         heights = c(2, 1.1),
        plot_D1+theme(legend.position = "none")+
          ggtitle(""),
        plot_D2+theme(legend.position = "none")),
      NULL,
      ggarrange(
        ncol = 1,
         heights = c(2, 1.1),
        plot_F1+theme(legend.position = "none")+
          ggtitle(""),
        plot_F2+theme(legend.position = "none"))
    )
  )
  
)

figure_2_abcdef

ggsave("images/figure_2_abcdef.png",
  figure_2_abcdef,
  width = 7*0.787402,
  height = 15*0.787402,
  units = c("in"),
  dpi = 150)

```



```{r}

figure_2_ghijkm <- ggarrange(
  
  ncol = 2,
  
  
  ggarrange(
    ncol = 1,
    heights = c(1, 0.05, 2.6),
    plot_G,
    NULL,
    ggarrange(
      ncol = 1,
      heights = c(1, 0.05, 1),
      ggarrange(
        ncol = 1,
        heights = c(2, 1.1),
        plot_I1+theme(legend.position = "none")+
          theme(axis.title.x = element_text(hjust = 1)),
        plot_I2+theme(legend.position = "none")),
      NULL,
      ggarrange(
        ncol = 1,
        heights = c(2, 1.1),
        plot_K1+theme(legend.position = "none")+
          theme(axis.title.x = element_text(hjust = 1)),
        plot_K2+theme(legend.position = "none"))
    )
  ),
  
  ggarrange(
    ncol = 1,
    heights = c(1, 0.05 ,2.6),
    plot_H+ggtitle(""),
    NULL,
    ggarrange(
      ncol = 1,
      heights = c(1, 0.05, 1),
      ggarrange(
        ncol = 1,
         heights = c(2, 1.1),
        plot_J1+theme(legend.position = "none")+
          ggtitle("")+
          theme(axis.title.x = element_text(hjust = 1)),
        plot_J2+theme(legend.position = "none")),
      NULL,
      ggarrange(
        ncol = 1,
         heights = c(2, 1.1),
        plot_M1+theme(legend.position = "none")+
          ggtitle("")+
          theme(axis.title.x = element_text(hjust = 1)),
        plot_M2+theme(legend.position = "none"))
    )
  )
  
)

figure_2_ghijkm

ggsave("images/figure_2_ghijkm.png",
  figure_2_ghijkm,
  width = 7*0.787402,
  height = 15*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_2_legends1 <- ggarrange(
  legend_C1
)

figure_2_legends1

ggsave("images/figure_2_legends1.png",
  figure_2_legends1,
  width = 2.5*0.787402,
  height = 4*0.787402,
  units = c("in"),
  dpi = 150)

figure_2_legends2 <- ggarrange(
  legend_D1
)

figure_2_legends2

ggsave("images/figure_2_legends2.png",
  figure_2_legends2,
  width = 2.5*0.787402,
  height = 4*0.787402,
  units = c("in"),
  dpi = 150)

```
