---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"Age-specific ligand, receptor, and interaction sets"

This script also requires cpi_interactions_yng_vs_old_mmus_cpi

# Preparation

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(eulerr)
library(gridExtra)
library(cowplot)
library(scater)
library(ggbeeswarm)
library(ggpubr)
library(ggnewscale)
library(ComplexUpset)

```

## Load

### Code

```{r load_code, message = FALSE}

source(file = "../../code/filepath.R")
source(file = "../../code/colors.R")
source(file = "../../interactome/functions/cpi_functions_calculation.R")
source(file = "../../interactome/functions/cpi_functions_analysis.R")

```

### Objects

```{r}

#  cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

cpi_yng_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi_pca"))
cpi_old_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi_pca"))

cpi_merged_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))

# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

max_ctints <- 420
max_ctpints <- 300
```


Merge overview dfs for direct comparion between age groups.

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctints_both <- rbind(ctints_yng[[1]], ctints_old[[1]])
ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))
ctints_both$celltypes <- factor(ctints_both$celltypes, 
                                levels = names(col_cts_red))
ctints_both$annotation <- factor(ctints_both$annotation,
                                 levels = names(col_ann))
```

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))
```


# Figure Parts

## A

Overlap young old cell type level ligands

For better convenience, skip uniform font size step here.

```{r}

ggdf1 <- sigmols_shared_young
ggdf2 <- sigmols_shared_old

ggdf1$sample <- unfactor(ggdf1$sample)
ggdf2$sample <- unfactor(ggdf2$sample)

ggdf1$sample[ggdf1$sample == "shared"] <- "conserved"
ggdf2$sample[ggdf2$sample == "shared"] <- "conserved"

ggdf1$sample <- factor(ggdf1$sample, levels = c(
  "exclusively young", "exclusively old", "conserved"))
ggdf2$sample <- factor(ggdf2$sample, levels = c(
  "exclusively young", "exclusively old", "conserved"))

legend_plot_a1 <- ggplot(ggdf1, 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))

legend_a1 <- get_legend(legend_plot_a1)
    
plot_a1 <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.65),

  ggplot(ggdf1[ggdf1$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-220, 0),
                       breaks = c(-200, -100, 0),
                       labels = c(200, 100, 0))+
    ylab("")+
     xlab(expression(atop("Ligands/",
                       paste("emitter"))))+
    theme(legend.position = "none"),
 
  
   ggplot(ggdf2[ggdf2$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_text(size = 11, hjust = 0.5,
                                     margin = margin(0, -6, 0, -9, unit = "pt")),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, 220),
                       breaks = c(0, 100, 200),
                       labels = c(0, 100, 200))+
    ylab("Cell type pairs")+
    xlab(expression(atop("Ligands/",
                       paste("emitter"))))+
    theme(legend.position = "none")
)

plot_a1

```

Overlap young old cell type level receptors

Requires loaded cpi_interactions_yng_vs_old

```{r}
    
plot_a2 <- ggarrange(
  
  ncol = 2,
  widths = c(1, 1.75),

  ggplot(ggdf1[ggdf1$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-220, 0),
                       breaks = c(-200, -100, 0),
                       labels = c(200, 100, 0))+
    ylab("")+
     xlab(expression(atop("Receptors/",
                       paste("receiver"))))+
    theme(legend.position = "none"),
 
  
   ggplot(ggdf2[ggdf2$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_text(size = 11, hjust = 0.5,
                                     margin = margin(0, -8, 0, -9, unit = "pt")),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, 220),
                       breaks = c(0, 100, 200),
                       labels = c(0, 100, 200))+
    ylab("Cell type pairs")+
      xlab(expression(atop("Receptors/",
                       paste("receiver"))))+
    theme(legend.position = "none")
  
)

plot_a2

```

## B 

Percentage of conserved ligands/receptors.

```{r}

plot_b <- plot_emirec_unique
plot_b

median(sigmols_shared_age_long$unique_percent[
  intersect(which(sigmols_shared_age_long$annotation == "Receivers"),
            which(sigmols_shared_age_long$age == "old"))
])

sigmols_shared_age_long[sigmols_shared_age_long$celltypes == "Stromal fibros",]
sigmols_shared_age_long[sigmols_shared_age_long$celltypes == "Dendritic-primed progs",]

```

## C

Overlap interactions cell type level emitters

```{r}

ggdf3 <- ctints_shared_young
ggdf4 <- ctints_shared_old

ggdf3$sample <- unfactor(ggdf3$sample)
ggdf4$sample <- unfactor(ggdf4$sample)

ggdf3$sample[ggdf3$sample == "shared"] <- "conserved"
ggdf4$sample[ggdf4$sample == "shared"] <- "conserved"

ggdf3$sample <- factor(ggdf3$sample, levels = c(
  "exclusively young", "exclusively old", "conserved"))
ggdf4$sample <- factor(ggdf4$sample, levels = c(
  "exclusively young", "exclusively old", "conserved"))


plot_c1 <- ggarrange(
  
  ncol = 2,
  widths = c(1, 1.5),

  ggplot(ggdf3[ggdf3$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45),
          legend.position = "none")+
    scale_x_continuous(limits = c(-max_ctints, 0),
                       breaks = c(-400, -200, 0),
                       labels = c(0, 200, 400))+
    ylab("")+
   xlab(expression(atop("Number of LRIs/",
                       paste("emitter")))),
 
  
   ggplot(ggdf4[ggdf4$annotation == "emitter",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_text(size = 11, hjust = 0.5,
                                     margin = margin(0, -6, 0, -9, unit = "pt")),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45),
          legend.position = "none")+
    scale_x_continuous(limits = c(0, max_ctints),
                       breaks = c(0, 200, 400),
                       labels = c(0, 200, 400))+
     xlab(expression(atop("Number of LRIs/",
                       paste("emitter"))))
)

plot_c1

```

Overlap interactions cell type level receivers

```{r}

plot_c2 <- ggarrange(
  
  ncol = 3,
  widths = c(1, 1.65),

  ggplot(ggdf3[ggdf3$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_ctints, 0),
                       breaks = c(-400, -200, 0),
                       labels = c(400, 200, 0))+
    ylab("")+
    xlab(expression(atop("Number of LRIs/",
                       paste("receiver"))))+
    theme(legend.position = "none"),
 
  
   ggplot(ggdf4[ggdf4$annotation == "receiver",], 
         aes(y = reorder(celltypes, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    conserved = "orange"))+
    theme(axis.text.y = element_text(size = 11, hjust = 0.5,
                                     margin = margin(0, -8, 0, -9, unit = "pt")),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_ctints),
                       breaks = c(0, 200, 400),
                       labels = c(0, 200, 400))+
    ylab("Cell type pairs")+
    xlab(expression(atop("Number of LRIs/",
                       paste("receiver"))))+
    theme(legend.position = "none")
)

plot_c2

```

## D 

Uniquely young and old ints/cell type

```{r}

plot_d <- plot_emirec_unique_ints
plot_d

ctints_shared_age_long[ctints_shared_age_long$celltypes == "Stromal fibros",]
ctints_shared_age_long[ctints_shared_age_long$celltypes == "Dendritic-primed progs",]


median(ctints_shared_age_long$unique_percent[
  intersect(which(ctints_shared_age_long$annotation == "Emitters"),
            which(ctints_shared_age_long$age == "old"))
])

```

## E

OVerlap young vs old cell type pair level

```{r}

plot_e1 <- ggarrange(
  
  ncol = 2,

  ggplot(ctpints_shared_young, 
         aes(y = reorder(ct_pair, order), x = -value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("exclusively young" = col_age[[1]], 
                                     "exclusively old" = col_age[[2]],
                                    shared = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(-max_ctpints, 0),
                       breaks = c(-max_ctpints, (-max_ctpints* 0.5), 0),
                       labels = c(max_ctpints, (max_ctpints* 0.5), 0))+
    ylab("")+
     xlab(expression(atop("Number of",
                       paste("LRIs/CTP"))))+
    theme(legend.position = "none"),
 
  
   ggplot(ctpints_shared_old, 
         aes(y = reorder(ct_pair, order), x = value, fill = sample))+
    geom_col(position = "stack")+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
    scale_fill_manual("", values = c("old" = col_age[[2]], 
                                     "young" = col_age[[1]], 
                                    shared = "orange"))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.line.y = element_blank(),
          plot.title = element_text(hjust = 0.45))+
    scale_x_continuous(limits = c(0, max_ctpints),
                       breaks = c(0, (max_ctpints*0.5), max_ctpints),
                       labels = c(0, (max_ctpints*0.5), max_ctpints))+
    ylab("Cell type pairs")+
     xlab(expression(atop("Number of",
                       paste("LRIs/CTP"))))+
    theme(legend.position = "none")
    
)

plot_e1

```

## F

Percent of unique interactions for each ct

```{r}

ctpints_shared_age$emitter <- factor(ctpints_shared_age$emitter,
                                      levels = names(col_emi_red))

ctpints_shared_age_long <- ctpints_shared_age %>%
  pivot_longer(col = c(10,11), values_to = "perc_unique", names_to = "age")


ctpints_shared_age_long$age[
  ctpints_shared_age_long$age == "perc_unique_old"] <- "old"
ctpints_shared_age_long$age[
  ctpints_shared_age_long$age == "perc_unique_yng"] <- "young"
ctpints_shared_age_long$age <- factor(ctpints_shared_age_long$age,
                                      levels = c("young", "old"))

plot_f1 <- ggplot(ctpints_shared_age_long, 
                  aes(x = age, color = age, y = perc_unique))+
  geom_boxplot()+
  facet_grid(cols = vars(emitter), switch = "x")

plot_f1

```

```{r}

ctpints_shared_age_long$receiver <- factor(ctpints_shared_age_long$receiver,
                                      levels = names(col_rec_red))

plot_f2 <- ggplot(ctpints_shared_age_long, aes(x = age, color = age, y = perc_unique))+
  geom_boxplot()+
  facet_grid(cols = vars(receiver), switch = "x")

plot_f2

```

# Uniform Formatting


```{r}

plot_B <- plot_b +
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
  scale_color_manual("Age", values = col_age)+
  ylim(limits = c(0, 100))+
ylab(expression(atop("Unique ligands or receptors",
                       paste("[% of total ligands or receptors]"))))+
  theme(axis.title.x = element_blank())+
  stat_compare_means(method = "anova",
                     label = "p.signif",
                     inherit.aes = TRUE,
                     label.y = 47, size = 3.5)

plot_B

```

```{r}

plot_D <- plot_d+
 #  base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
  scale_color_manual("Age", values = col_age)+
  ylim(limits = c(0, 100))+
ylab(expression(atop("Unique LRIs",
                       paste("[% of total LRIs/cell type]"))))+
  theme(axis.title.x = element_blank())+
  stat_compare_means(method = "anova",
                     label = "p.signif",
                     inherit.aes = TRUE,
                     label.y = 47, size = 3.5)

plot_D

```


```{r}

plot_E <- plot_e1

plot_E

```

```{r}


plot_F1 <- plot_f1+
 #  base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
  scale_color_manual("Age", values = col_age)+
ylab(expression(atop("Unique LRIs",
                       paste("[% of total LRIs/CTP]"))))+
  xlab("CTPs (summarized)")+
  ylim(limits = c(0, 100))+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_text(angle = 90, size = 11),
        strip.placement = "outside")

plot_F1

legend_age <- get_legend(plot_F1)

```

```{r}

plot_F2 <- plot_f2+
 #  base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
    # individual additions
  scale_color_manual("Age", values = col_age)+
 ylab(expression(atop("Unique LRIs",
                       paste("[% of total LRIs/CTP]"))))+
  xlab("CTPs (summarized)")+
  ylim(limits = c(0, 100))+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_text(angle = 90, size = 11),
        strip.placement = "outside")

plot_F2

```

# Assemble

```{r}

plot_A1 <- annotate_figure(plot_a1,
               top = text_grob("Emitters", face = "bold", size = 14,
                               hjust = 1.5))

plot_A2 <-annotate_figure(plot_a2,
               top = text_grob("Receivers", face = "bold", size = 14,
                               hjust = 0.4))

plot_A1
plot_A2


ggsave("images/figure_4_a1.png",
  plot_A1,
  width = 7.5*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

ggsave("images/figure_4_a2.png",
  plot_A2,
  width = 6*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

figure_4_b <- ggarrange(
  ncol = 1,
  plot_B+theme(legend.position = "none"),
  heights = c(3,1),
  ggarrange(
    legend_a1,
    legend_age,
      widths = c(3,2)
  )
)

figure_4_b

ggsave("images/figure_4_b.png",
  figure_4_b,
  width = 3.5*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

plot_C1 <- annotate_figure(plot_c1,
               top = text_grob("Emitters", face = "bold", size = 14,
                               hjust = 0.3))

plot_C2 <-annotate_figure(plot_c2,
               top = text_grob("Receivers", face = "bold", size = 14,
                               hjust = 1.25))

plot_C1
plot_C2


ggsave("images/figure_4_c1.png",
  plot_C1,
  width = 5.5*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

ggsave("images/figure_4_c2.png",
  plot_C2,
  width = 8*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

figure_4_d <- ggarrange(
  ncol = 1,
  plot_D+theme(legend.position = "none"),
  heights = c(3,1),
  NULL
  
)

figure_4_d

ggsave("images/figure_4_d.png",
  figure_4_d,
  width = 3.5*0.787402,
  height = 5.2*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_4_ef <- ggarrange(
  
  ncol = 3,
  widths = c(5, 2, 2),
  plot_E,
  plot_F1+theme(legend.position = "none"),
  plot_F2+theme(legend.position = "none")
)

figure_4_ef

ggsave("images/figure_4_ef.png",
  figure_4_ef,
  width = 17*0.787402,
  height = 6.3*0.787402,
  units = c("in"),
  dpi = 150)

```
