---
author: "lea wölbert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"Take a closer look into LT-HSCs"

## Libraries

```{r libraries, message = FALSE}

library(SingleCellExperiment)
library(rlist)
library(tidyverse)
library(eulerr)
library(gridExtra)
library(cowplot)
library(scater)
library(ggbeeswarm)
library(ggpubr)
library(scran)
library("factoextra")

```

## Load

### Code

```{r load_code, message = FALSE}

source(file = "../../code/filepath.R")
source(file = "../../code/colors.R")
source(file = "../../interactome/functions/cpi_functions_calculation.R")
source(file = "../../interactome/functions/cpi_functions_analysis.R")

```

### Objects

```{r}

sce_all <- readRDS(file = paste0(
  filepath_lv1, "data/sce_objects/mmus/mmus_SCE"))

mmus_yng_sce_ds <- readRDS(file = paste0(
    filepath_lv1, "data/sce_objects/mmus/mmus_young_SCE_ds"))
mmus_old_sce_ds <- readRDS(file = paste0(
    filepath_lv1, "data/sce_objects/mmus/mmus_old_SCE_ds"))

sce_all <- cbind(mmus_yng_sce_ds, mmus_old_sce_ds)
assays(sce_all)$logcounts <- assays(sce_all)$downsampled


# corresponding cpi objects
cpi_yng <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi"))
cpi_old <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi"))

cpi_yng_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_yng_cpi_pca"))
cpi_old_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_old_cpi_pca"))

cpi_merged_pca <- readRDS(file = paste0(
  filepath_lv1, "data/cci_files/mmus_cpi_pca"))


# corresponding metrics objects
ctpints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctpints"))
ctints_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_ctints"))
nrlrs_yng <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_yng_cpi_nrlrs"))

ctpints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctpints"))
ctints_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_ctints"))
nrlrs_old <- readRDS(file = paste0(
    filepath_lv1, "data/cci_files/mmus_old_cpi_nrlrs"))

species <- "mmus"
cpi_both <- cpi_merged_pca

```


Merge overview dfs for direct comparion between age groups.

```{r}

ctpints_both <- rbind(ctpints_yng[[1]], ctpints_old[[1]])
ctpints_both$age <- factor(ctpints_both$age, levels = c("young", "old"))
ctpints_both$emitter <- factor(ctpints_both$emitter, 
                               levels = names(col_emi_red))
ctpints_both$receiver <- factor(ctpints_both$receiver, 
                               levels = names(col_rec_red))
```

```{r}

ctints_both <- rbind(ctints_yng[[1]], ctints_old[[1]])
ctints_both$age <- factor(ctints_both$age, levels = c("young", "old"))
ctints_both$celltypes <- factor(ctints_both$celltypes, 
                                levels = names(col_cts_red))
ctints_both$annotation <- factor(ctints_both$annotation,
                                 levels = names(col_ann))
```

```{r}

nrlrs_both <- rbind(nrlrs_yng, nrlrs_old)
nrlrs_both$age <- factor(nrlrs_both$age, levels = c("young", "old"))
nrlrs_both$celltypes <- factor(nrlrs_both$celltypes, 
                               levels = names(col_cts_red))
```


# Figure Parts

## A-C

Umap of HSCs and various genes

```{r}

plot_a <- plotUMAP(sce_all[,sce_all$Fraction == "hsc"],  colour_by = "Cd34",
                   point_size = 0.4, 
                  point_alpha = 1)+
  scale_color_gradientn("Cd34 ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_b <- plotUMAP(sce_all[,sce_all$Fraction == "hsc"],  colour_by = "Flt3",
                   point_size = 0.4, 
                  point_alpha = 1)+
  scale_color_gradientn("Flt3 ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_c <- plotUMAP(sce_all[,sce_all$Fraction == "hsc"],  colour_by = "Procr",
                   point_size = 0.4,  point_alpha = 1)+
  scale_color_gradientn("Procr ", colors = c("black", "darkorange3", "orange", "lightgoldenrod"))

plot_a
plot_b
plot_c

```

## D

Overlap receptors

Requires some objects from loaded cpi_interactions_yng_vs_old

```{r}

hsc_ct_list <- ctints_shared_age_list[grep("LT-HSCs", names(ctints_shared_age_list))]

hsc_ctp_list <- ctpints_shared_age_list[grep("LT-HSCs", names(ctpints_shared_age_list))]

hsc_rec_yng <- ctlrs_yng[["LT-HSCs"]]
hsc_rec_old <- ctlrs_old[["LT-HSCs"]]

```

```{r}

shared_recs <- intersect(hsc_rec_yng$sigmols, hsc_rec_old$sigmols)
unique_yng_recs <- hsc_rec_yng$sigmols[-which(hsc_rec_yng$sigmols %in% shared_recs)]
unique_old_recs <- hsc_rec_old$sigmols[-which(hsc_rec_old$sigmols %in% shared_recs)]

```


```{r}

fit1 <- euler(c("A" = length(unique_yng_recs), 
               "B" = length(unique_old_recs), 
               "A&B" = length(shared_recs)))

plot_d <- plot(fit1, 
     labels = c("", ""),
     fills = c("orange", "grey80"),
     quantities = list(type = "counts", cex = 1))

plot_d

```

## H (similar to D)

```{r}

length_old <- vector()
length_shared <- vector()
length_young <- vector()

for(i in 1:length(hsc_ctp_list)){
  length_old <- c(length_old, length(hsc_ctp_list[[i]]$unique_old_intsctp))
  length_shared <- c(length_shared, length(hsc_ctp_list[[i]]$shared_intsctp))
  length_young <- c(length_young, length(hsc_ctp_list[[i]]$unique_yng_intsctp))
}

fit3 <- euler(c("A" = median(length_young), 
               "B" = median(length_old), 
               "A&B" = median(length_shared)))

plot_h <- plot(fit3, 
     labels = c("", ""),
     fills = c("orange", "grey80"),
     quantities = list(type = "counts", cex = 1))

plot_h

```

## E & F

Try to track how many interactions each receptor has and if they are
conserved.

```{r}

hsc_ctints_yng <- ctints_yng[[2]][["LT-HSCs"]]
hsc_ctints_old <- ctints_old[[2]][["LT-HSCs"]]

```

```{r}

hsc_rec_yng$nr_ints_per_recep <- vector(length = nrow(hsc_rec_yng))

for(i in 1:nrow(hsc_rec_yng)){
  
  hsc_rec_yng$nr_ints_per_recep[i] <- length(grep(hsc_rec_yng$sigmols[i], hsc_ctints_yng$interactions))
}

hsc_rec_old$nr_ints_per_recep <- vector(length = nrow(hsc_rec_old))

for(i in 1:nrow(hsc_rec_old)){
  
  hsc_rec_old$nr_ints_per_recep[i] <- length(grep(hsc_rec_old$sigmols[i], hsc_ctints_old$interactions))
}

hsc_rec_yng$age <- "young"
hsc_rec_old$age <- "old"

lths_rec <- rbind(hsc_rec_yng, hsc_rec_old)
lths_rec$age <- factor(lths_rec$age, levels = c("young", "old"))

lths_rec_shared <- intersect(lths_rec$sigmols[lths_rec$age == "young"],
                             lths_rec$sigmols[lths_rec$age == "old"])
setequal(lths_rec_shared, shared_recs)


hsc_rec_shared_yng <- hsc_rec_yng[hsc_rec_yng$sigmols %in% lths_rec_shared,]
hsc_rec_shared_old <- hsc_rec_old[hsc_rec_old$sigmols %in% lths_rec_shared,]

match_pos <- match(hsc_rec_shared_yng$sigmols, hsc_rec_shared_old$sigmols)

hsc_rec_shared_old <- hsc_rec_shared_old[match_pos,]

# add the range_nr between yng and old numbers into yng df
hsc_rec_shared_yng$range_nr <- hsc_rec_shared_old$nr_ints_per_recep - hsc_rec_shared_yng$nr_ints_per_recep
  
hsc_ctints_yng$ligand <- gsub("[&][[:print:]]+", "", hsc_ctints_yng$interactions)
hsc_ctints_yng$receptor <- gsub("[[:print:]]+[&]", "", hsc_ctints_yng$interactions)

hsc_ctints_old$ligand <- gsub("[&][[:print:]]+", "", hsc_ctints_old$interactions)
hsc_ctints_old$receptor <- gsub("[[:print:]]+[&]", "", hsc_ctints_old$interactions)

hsc_ctints_yng_df_shared <- hsc_ctints_yng[hsc_ctints_yng$receptor %in% lths_rec_shared,]
hsc_ctints_old_df_shared <- hsc_ctints_old[hsc_ctints_old$receptor %in% lths_rec_shared,]

for(i in 1:nrow(hsc_rec_shared_yng)){
  
  yng_ints <- vector()
  old_ints <- vector()
  
  yng_ints <- hsc_ctints_yng_df_shared$interactions[grep(hsc_rec_shared_yng$sigmols[i],
                                               hsc_ctints_yng_df_shared$receptor)]
  old_ints <- hsc_ctints_old_df_shared$interactions[grep(hsc_rec_shared_old$sigmols[i],
                                               hsc_ctints_old_df_shared$receptor)]
  
  if(length(grep("TRUE", is.na(match(old_ints, yng_ints)))) != 0){
    id <- FALSE
  }else if(length(grep("TRUE", is.na(match(yng_ints, old_ints)))) != 0){
    id <- FALSE
  }else if(hsc_rec_shared_yng$range_nr[i] != 0){
    id <- FALSE
  }else{
    id <- TRUE
  }
  
  hsc_rec_shared_yng$identical_interactions[i] <- id
  
}

lths_rec$identical_interactions <- vector(length = nrow(lths_rec))

lths_rec$identical_interactions <- hsc_rec_shared_yng$identical_interactions[
  match(lths_rec$sigmols, hsc_rec_shared_yng$sigmols)]
lths_rec$identical_interactions[is.na(lths_rec$identical_interactions)] <- FALSE

i <- 41

length(grep(hsc_rec_old$sigmols[hsc_rec_old$sigmols == "Icam1"], hsc_ctints_old$interactions))

```

```{r}

plot_e <- ggplot(lths_rec, aes(y = nr_ints_per_recep, x = age, 
                                color = identical_interactions))+
  geom_quasirandom()

plot_f <- ggplot(hsc_rec_shared_yng, aes(x = range_nr))+
  geom_bar()

plot_e
plot_f

```

## G

compare ranks between young and old

```{r}

# add ranks to the rec dataframe
hsc_rec_shared_yng$rank <- hsc_ctints_yng$rank[match(hsc_rec_shared_yng$sigmols, 
                                              hsc_ctints_yng$receptor)]
hsc_rec_shared_old$rank <- hsc_ctints_old$rank[match(hsc_rec_shared_old$sigmols, 
                                              hsc_ctints_old$receptor)]


hsc_rec_shared_yng$range_rank <- hsc_rec_shared_old$rank[match(hsc_rec_shared_yng$sigmols,
                                            hsc_rec_shared_old$sigmols)] - hsc_rec_shared_yng$rank


table(is.na(match(hsc_rec_shared_yng$sigmols,hsc_rec_shared_old$sigmols)))
table(is.na(match(hsc_rec_shared_old$sigmols, hsc_rec_shared_yng$sigmols)))

```

```{r}

plot_g <- ggplot(hsc_rec_shared_yng, aes(y = range_rank, x = celltypes))+
  geom_quasirandom()

plot_g

```

## J

Score percentile changes.

```{r}

score_df_yng_hsc <- score_df_yng[score_df_yng$receiver == "LT-HSCs",]
score_df_old_hsc <- score_df_old[score_df_old$receiver == "LT-HSCs",]

matched_combis <- intersect(
  paste0(score_df_old_hsc$ct_pair, score_df_old_hsc$interaction), 
  paste0(score_df_yng_hsc$ct_pair, score_df_yng_hsc$interaction))


score_df_yng_hsc <- score_df_yng_hsc[
  !is.na(match(paste0(score_df_yng_hsc$ct_pair, score_df_yng_hsc$interaction), 
               matched_combis)),]
score_df_old_hsc <- score_df_old_hsc[
  !is.na(match(paste0(score_df_old_hsc$ct_pair, 
                      score_df_old_hsc$interaction), matched_combis)),]

score_df_yng_hsc <- score_df_yng_hsc[match(
  paste0(score_df_old_hsc$ct_pair, score_df_old_hsc$interaction),
  paste0(score_df_yng_hsc$ct_pair, score_df_yng_hsc$interaction)),]

score_df_yng_hsc$range_perc <- score_df_old_hsc$score_percentile - score_df_yng_hsc$score_percentile
score_df_yng_hsc$range_score <- score_df_old_hsc$score - score_df_yng_hsc$score

```

```{r}

plot_j <- ggplot(score_df_yng_hsc, 
                 aes(x = ct_pair, y = range_perc, 
                     color = c(score_df_yng_hsc$range_perc > 33) | score_df_yng_hsc$range_perc < (-33)))+
  geom_quasirandom()

plot_j

```

## I

Types of interaction.

This plot requires plot J thats why it's last

```{r}

# unique old
uni_old <- vector()
for(i in 1:length(hsc_ctp_list)){
  uni_old <- c(uni_old, hsc_ctp_list[[i]]$unique_old_intsctp)
}

uni_old <- unique(uni_old)
uni_old

uni_yng <- vector()
for(i in 1:length(hsc_ctp_list)){
  uni_yng <- c(uni_yng, hsc_ctp_list[[i]]$unique_yng_intsctp)
}

uni_yng <- unique(uni_yng)
uni_yng

interactions_all <- as.data.frame(
  table(cpi_yng$Interactions$interaction_type[
    cpi_yng$Interactions$interaction_pair %in% uni_old]))
colnames(interactions_all)[1] <- "Interaction_type" 
interactions_all$age <- "old"

# all old
interactions_old <- as.data.frame(table(cpi_old$Interactions$interaction_type[
  is.nan(rowMeans(cpi_old$Score, na.rm = TRUE)) == FALSE]))

interactions_all$mmus_old[match(interactions_old$Var1, interactions_all[,1])] <- interactions_old$Freq

# 33 percentile change
over33_Change <- score_df_yng_hsc$interaction[c(
  which(score_df_yng_hsc$range_perc > 33),
  which(score_df_yng_hsc$range_perc < -33))]
over33_Change <- unique(over33_Change)

interactions_change <- as.data.frame(
  table(cpi_yng$Interactions$interaction_type[
    cpi_yng$Interactions$interaction_pair %in% over33_Change]))

interactions_all$change_old[
  match(interactions_change$Var1, 
        interactions_all[,1])] <- interactions_change$Freq


interactions_all <- pivot_longer(interactions_all, 
                                 cols = c(2,4, 5),
                                 names_to = "Sample")
interactions_all$value[is.na(interactions_all$value)] <- 0

interactions_all$Sample[
  interactions_all$Sample == "mmus_old"] <- "all old"
interactions_all$Sample[
  interactions_all$Sample == "Freq"] <- "uniquely old"
interactions_all$Sample[
  interactions_all$Sample == "change_old"] <- "differentially scored"

interactions_all$Sample <- factor(interactions_all$Sample, levels = c(
  "all old", "uniquely old", "differentially scored"
))

plot_i <-  ggplot(interactions_all,  aes(x = Sample,
                              y = value,
                              fill = Interaction_type))+
  geom_col(position = "fill")+
  ylab("Number of interactions")+
  scale_fill_manual("LRI functional annotation", values = col_itp)
  
plot_i

```

## K & M

1st and 3rd most important PCs

```{r}

# perform PCA again so I can extract the attributes

df_pca <- get_pca(cpi_both)

vars <- get_pca_var(df_pca)

vars$contrib <- vars$contrib[order(vars$contrib[,2], decreasing = TRUE),]
top_contrib <- rownames(vars$contrib)[1:50]
top_contrib <- gsub("[.]", "&", top_contrib)

plot_k <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = unlist(c(cpi_merged_pca$Score[
                       rownames(cpi_merged_pca$Score) == top_contrib[1],]))))+
geom_point(size = 1.5)


plot_m <- ggplot(cpi_merged_pca$PCA[1:(nrow(cpi_merged_pca$PCA)-1),], 
                 aes(x = Dim.1, y = Dim.2, 
                     colour = unlist(c(cpi_merged_pca$Score[
                       rownames(cpi_merged_pca$Score) == top_contrib[3],]))))+
geom_point(size = 1.5)

plot_k
plot_m

```


## Extract some important lists of genes

LRI that are scored higher in old LT-HSC.

```{r}

unique_old_recs

```

```{r}

unique_yng_recs

```

```{r}

score_perc_higher <- score_df_yng_hsc$interaction[
  score_df_yng_hsc$range_perc > 33]
score_perc_higher <- unique(score_perc_higher)

score_perc_higher

```

```{r}

score_perc_lower <- score_df_yng_hsc$interaction[
  score_df_yng_hsc$range_perc < -33]
score_perc_lower <- unique(score_perc_lower)

score_perc_lower

```

```{r}

over33_Change <- unique(c(score_perc_lower, score_perc_higher))

diff_33_ligands <- gsub("[&][[:print:]]+", "", over33_Change)
table(diff_33_ligands)
diff_33_ligands <- unique(diff_33_ligands)

diff_33_receptors <- gsub("[[:print:]]+[&]", "", over33_Change)
table(diff_33_receptors)
diff_33_receptors <- unique(diff_33_receptors)

diff_33_ligands
diff_33_receptors

```

PCs

reuse the PC vars from before.

```{r}

top_contrib

table(top_contrib %in% over33_Change)
table(top_contrib %in% uni_old)
table(top_contrib %in% uni_yng)

```

# Uniform formatting

```{r}

plot_A <- plot_a+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_A

```

```{r}

plot_B <- plot_b+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_B

```

```{r}

plot_C <- plot_c+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_C

```

```{r}

plot_D <-  as.ggplot(plot_d)
plot_D

```

```{r}

plot_E <- plot_e+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  scale_color_manual(values = c("TRUE" = "orange", "FALSE" = "black"))+
  labs(color="Identical\ninteractions\n")+
  theme(axis.text.x = element_text(angle = 90))+
  ylab(expression(atop("Number of interactions",
                       paste("each receptor engages in"))))+
  xlab("Age")+
  ggtitle("Interaction sets of LT-HSC receptors")

plot_E

```

```{r}

plot_F <- plot_f+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab("Number of receptors")+
  xlab(expression(atop("Number of interactions",
                       paste("added per receptor during ageing"))))+
  ggtitle("")

plot_F

```

```{r}

plot_G <- plot_g+
    # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(expression(atop("Receptor rank old-",
                       paste("receptor rank young"))))+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())

plot_G

```

```{r}

plot_H <-  as.ggplot(plot_h)
plot_H

```

```{r}

plot_I <- plot_i+
 # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 90))

legend_i <- get_legend(plot_I)

plot_I

```

```{r}

plot_J <- plot_j+
  # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual(values = c("TRUE" = "orange", "FALSE" = "black"))+
  labs(color=">33 percentile\nchange")+
  xlab("CTPs")+
  ylab(expression(atop("Score percentile old-",
                       paste("Score percentile young"))))+
  ggtitle("LT-HSC scores")


plot_J

legend_j <- get_legend(plot_J)

```

```{r}

plot_K <- plot_k+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_gradientn(top_contrib[1], 
                        colors = c("black", "darkorange3", "lightgoldenrod"), 
                        limits = c(0,1))+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_K

```

```{r}

plot_M <- plot_m+
   # base theme
    theme_classic()+
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          legend.title = element_text(size = 12, face = "bold"),
          legend.text = element_text(size = 11),
          plot.title = element_text(size = 14, face = "bold"))+
  theme(plot.background = element_blank(),
        panel.background = element_blank(),
        legend.background = element_blank())+
  # individual additions
  ylab(paste("PC2 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 2], 
                                    digits = 2), "%]", sep = ""))+
  xlab(paste("PC1 [", round(cpi_merged_pca$PCA[nrow(cpi_merged_pca$PCA), 1], 
                                    digits = 2), "%]", sep = ""))+
  scale_color_gradientn(top_contrib[3], 
                        colors = c("black", "darkorange3", "lightgoldenrod"), 
                        limits = c(0,1))+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(size = 12, face = "bold.italic"))

plot_M

```

# Assemble

```{r}

figure_6_abc <- ggarrange(
  ncol = 3,
  plot_A+ggtitle("LT-HSC marker gene expression"),
  plot_B+ggtitle(""),
  plot_C+ggtitle("")
)

figure_6_abc

ggsave("images/figure_6_abc.png",
  figure_6_abc,
  width = 17*0.787402,
  height = 4.5*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_6_d <- ggarrange(
  plot_D
)

figure_6_d

ggsave("images/figure_6_d.png",
  figure_6_d,
  width = 3*0.787402,
  height = 3*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_6_efg <- ggarrange(
  ncol = 3,
  widths = c(3.5, 2, 3),
  plot_E,
  plot_F,
  plot_G+
    ggtitle("Ranks of LT-HSC receptors")
)

figure_6_efg

ggsave("images/figure_6_efg.png",
  figure_6_efg,
  width = 14*0.787402,
  height = 4*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_6_h <- ggarrange(
  plot_H
)

figure_6_h

ggsave("images/figure_6_h.png",
  figure_6_h,
  width = 3*0.787402,
  height = 3*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_6_ij <- ggarrange(
  ncol = 3,
  widths = c(3,2,3),
  
  plot_I+theme(legend.position = "none"),
  ggarrange(
    ncol = 1,
    legend_i,
    legend_j
  ),
  plot_J+theme(legend.position = "none")
  
)

figure_6_ij

ggsave("images/figure_6_ij.png",
  figure_6_ij,
  width = 14*0.787402,
  height = 6*0.787402,
  units = c("in"),
  dpi = 150)

```

```{r}

figure_6_km <- ggarrange(
 
  plot_K,
  plot_M
  
)

figure_6_km

ggsave("images/figure_6_km.png",
  figure_6_km,
  width = 10*0.787402,
  height = 4*0.787402,
  units = c("in"),
  dpi = 150)

```
